### 2022-03-11 Elliptic Curves/submission.tex
Initial commit

\documentclass{scrartcl}

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{xparse}
\usepackage{geometry}
\usepackage{enumerate}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage[style=english]{csquotes}
\usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}

\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\usetikzlibrary{babel, positioning, shapes.geometric, arrows, arrows.meta}
\addbibresource{bibliography.bib}

\title{Miniproject - Elliptic Curves}
\author{Simon Pohmann}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\p}{\mathfrak{p}}
\newcommand{\Set}{\mathrm{\textbf{Set}}}
\newcommand{\Aff}{\mathrm{\textbf{Aff}}}
\newcommand{\Sch}{\mathrm{\textbf{Sch}}}
\newcommand{\Ring}{\mathrm{\textbf{Ring}}}
\newcommand{\Ab}{\mathrm{\textbf{Ab}}}
\newcommand{\Top}{\mathrm{Top}}
\newcommand{\Spec}{\mathrm{Spec}}
\newcommand{\Quot}{\mathrm{Quot}}
\newcommand{\im}{\mathrm{im}}
\renewcommand{\O}{\mathcal{O}}
\DeclareMathOperator*{\colim}{colim}

\newcommand\restr[2]{{
    \left.\kern-\nulldelimiterspace
    #1
    \vphantom{\big|}
    \right|_{#2}
}}

\newtheorem{prop}{Proposition}
\newtheorem{theorem}[prop]{Theorem}
\newtheorem{lemma}[prop]{Lemma}
\newtheorem{corollary}[prop]{Corollary}

\theoremstyle{definition}
\newtheorem{problem}[prop]{Problem}
\newtheorem{alg}[prop]{Algorithm}
\newtheorem{definition}[prop]{Definition}
\newtheorem{example}[prop]{Example}
\newtheorem{remark}[prop]{Remark}

\begin{document}
\maketitle

\printbibliography
\end{document}

### 2022-03-12 Elliptic Curves/submission.tex
Continued on Ex 1 Elliptic Curves

@@
 \DeclareMathOperator*{\colim}{colim}
+\newcommand{\notdivides}{\ \nmid \ }
+\newcommand{\divides}{\ \mid \ }
 
@@
 
+\section{Question 1}
+
+\begin{example}[1(i)]
+    Have
+    \begin{equation*}
+        |162^2 + 6|_5 = |26250|_5 = |5^4 \cdot 7 \cdot 2 \cdot 3|_5 = 5^{-4} < 5^{-3}
+    \end{equation*}
+\end{example}
+
+\begin{example}[1(ii)]
+    Let
+    \begin{equation*}
+        \alpha = 5^{-1} + 2 \cdot 5^0 + 5 (1 + 4 \cdot 5) \sum_{n \geq 0} 5^{2n} \in \Q_5
+    \end{equation*}
+    Note that in $\Q_5$ we have
+    \begin{equation*}
+        \sum_{n \geq 0} 5^{2n} = \sum_{n \geq 0} 25^n = \frac 1 {1 - 25} = -\frac 1 {24}
+    \end{equation*}
+    So
+    \begin{equation*}
+        \alpha = \frac 1 5 + 2 + 5 (21) \frac 1 {24} = \frac {263} {40}
+    \end{equation*}
+\end{example}
+For the next exercises, we will slightly abuse notation and write
+\begin{equation*}
+    E(R) := \{ (x, y) \in E \ | \ x, y \in R \}
+\end{equation*}
+for an Elliptic Curve $E$ defined over $k$ and any ring $R$ contained in some extension field of $k$.
+\begin{prop}[1(iii)]
+    Consider the Elliptic Curve $E: y^2 = x^3 + 2x + 2$ defined over $\Z$.
+    Then $E(\Z) = \{ \O \}$ and
+    \begin{equation*}
+        E(\Z_p) \neq \{ \O \} \ \Leftrightarrow \ p \neq 3
+    \end{equation*}
+\end{prop}
+\begin{proof}
+    First show that there exists some $(x, y) \in \tilde{E}(\F_p)$ with $y \neq 0$ for all primes $p \neq 3$.
+
+    If $p \equiv 1, 5 \mod 8$, then $-1$ is a square in $\F_p$, thus there is $\alpha \in \F_p$ with $\alpha^2 = -1$ and so $(-1, \alpha) \in \tilde{E}(\F_p)$.
+    If $p \equiv 7 \mod 8$, then (by Quadratic Reciprocity) it follows that $2$ is a square in $\F_p$.
+    Thus there is $\alpha \in \F_p$ with $\alpha^2 = 2$ and so $(0, \alpha) \in \tilde{E}(\F_p)$.
+
+    Hence, consider now the case $p \equiv 3 \mod 8$.
+    Note that
+    \begin{equation*}
+        \Delta(E) = 4 \cdot 2^3 + 27 \cdot 2^2 = 140 = 2^2 \cdot 5 \cdot 7
+    \end{equation*}
+    Hence we see that $p \notdivides \Delta(E)$ and so $\tilde{E}$ is an Elliptic Curve defined over $\F_p$.
+    Now the Hasse bound shows that
+    \begin{equation*}
+        \#\tilde{E}(\F_p) \in [p + 1 - 2\sqrt{p}, p + 1 + 2\sqrt{p}]
+    \end{equation*}
+    Note that for $p > 9$ have $\sqrt{p} < p/3$ and thus
+    \begin{equation*}
+        p + 1 - 2\sqrt{p} > 4
+    \end{equation*}
+    Thus $\tilde{E}(\F_p) \geq 5$ and so there must be $(x, y) \in \tilde{E}(\F_p)$ with $y \neq 0$, as there are at most four points on $\tilde{E}(\F_p)$ that do not satisfy this ($\O$ and possibly $(\alpha_i, 0)$ with $\alpha_i$ a root of $x^3 + 2x + 2$).
+
+    Now consider any prime $p \neq 2, 3$ and $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_p), x, y \in \Z$.
+    Let $f(t) := t^2 - x^3 - 2x - 2$.
+    Then
+    \begin{equation*}
+        |f(y)|_p \leq p^{-1} \quad \text{and} \quad |f'(y)|_p = |y|_p = 1
+    \end{equation*}
+    Thus $|f(y)|_p < |f'(y)|_p^2$ and Hensel's Lemma yields a root $\gamma \in \Z_p$ with $(x, \gamma) \in E(\Z_p)$.
+
+    In the case $p = 2$, note that $f(t) := t^2 - 5^3 - 2 \cdot 5 - 2 = t^2 - 137$ satisfies
+    \begin{equation*}
+        |f(1)|_2 = |-136|_2 = |-17 \cdot 2^3|_2 = 2^{-3} < \left( 2^{-1} \right)^2 = |2|_2^2 = |f'(1)|_2^2
+    \end{equation*}
+    and so Hensel's Lemma yields a point $(5, \gamma) \in E(\Z_2)$.
+
+    The only remaining case is $p = 3$, and a trying all 9 points in $\F_3^2$ shows that $\tilde{E}(\F_3) = \{\O\}$.
+    This clearly shows that $E(\Z_3) = \{ \O \}$ and so $E(\Z) = \{\O\}$.
+\end{proof}
+For the next exercise, we first summarize the techniques we have used above.
+\begin{prop}
+    \label{prop:p_adic_points_techniques}
+    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $\Z$.
+    Let $p$ be a prime.
+    Then
+    \begin{itemize}
+        \item If $E(\Z_p) \neq \{\O\}$ then $\tilde{E}(\F_p) \neq \{\O\}$.
+        \item Suppose $p \neq 2$. There is $(x, y) \in \tilde{E}(\F_p)$ with $y \neq 0$ if and only if there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$.
+        \item Suppose $p \neq 2$. If $\#\tilde{E}(\F_p) \geq 5$ then there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$.
+        \item Suppose $p \geq 11$ and $p \notdivides \Delta(E)$. Then there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$.
+    \end{itemize}
+\end{prop}
+\begin{proof}
+    The first part is trivial and follows from the fact that any $(x, y) \in E(\Z_p)$ yields $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_p)$.
+
+    For the second part, note that by assumption, there is $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_p), x, y \in \Z$ with $|y|_p = 1$ and so
+    \begin{equation*}
+        |y^2 - x^3 - a_2 x^2 - a_4 x - a_6|_p \leq p^{-1} < 1 = 1^2 = |2y|_p
+    \end{equation*}
+    Hensel's Lemma now shows that there is $\gamma \in \Z_p$ such that $\gamma^2 = x^3 + a_2 x^2 + a_4 x + a_6$ and so $(x, \gamma) \in E(\Z_p)$.
+    Since $|y|_p = 1$ clearly also $|\gamma|_p = 1$.
+    The other direction is obvious and follows directly by taking the reduction modulo $p$.
+
+    For the third part, notice that there are at most three different points $(x, y) \in \tilde{E}(\F_p)$ with $y = 0$, as in this case $x$ is a root of the cubic $t^3 + a_2 t^2 + a_4 t + a_6$.
+    Thus, if $\#\tilde{E}(\F_p) \geq 5$, there must be $(x, y) \in \tilde{E}(\F_p)$ with $y \neq 0$ and so the claim follows by the second part.
+
+    For the fourth part, note that as above, $p > 9$ implies $\sqrt{p} < p/3$ and so the Hasse bound yields (since $\tilde{E}$ is an Elliptic Curve by assumption, as $p \notdivides \Delta(E)$)
+    \begin{equation*}
+        \#\tilde{E}(\F_p) \geq p + 1 - 2\sqrt{p} > 4
+    \end{equation*}
+    thus $\#\tilde{E}(\F_p) \geq 5$. 
+    The claim now follows by the third part.
+\end{proof}
+This already shows that we do not have to worry to much about the condition $E(\Z_p) \neq \{\O\}$ for $p \neq 2, 3, 5, 7$ prime, as we expect that it is fulfilled quite often.
+This gives the following condition.
+\begin{prop}
+    Let $f_0, f_1, f_2 \in \Z$ and consider the Elliptic Curve $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$.
+    Let $p \in \{3, 5, 7\}$.
+    Then there is no $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ if and only if
+    \begin{align*}
+        p = 3 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 2 \mod 3 \\
+        p = 5 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 2, 3 \mod 5 \\
+        p = 7 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 3, 5, 6 \mod 7
+    \end{align*}
+    for all $n \in \Z$.
+
+    In particular, this is necessary for $E$ to satisfy the desired properties, i.e. there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ if and only if $p \neq 3, 5, 7$
+    \footnote{I understood the task here to be ``if and only if''. As mentioned later, this interpretation is probably wrong, and I will discuss the other case next.}.
+\end{prop}
+\begin{proof}
+    Let $p \in \{3, 5, 7\}$.
+    Assume there is some $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_p), x, y \in \Z$ with $\tilde{y} \neq 0$.
+    Then have
+    \begin{equation*}
+        y^2 \equiv x^3 + f_2 x^2 + f_1 x + f_0 \mod p
+    \end{equation*}
+    and so $x^3 + f_2 x^2 + f_1 x + f_0$ is a quadratic residue modulo $p$.
+
+    By checking all elements in $\F_3$, $\F_5$ and $\F_7$, one finds
+    \begin{align*}
+        \text{$n$ quadratic residue modulo $3$} \ &\Leftrightarrow \ n \equiv 0, 1 \mod 3 \\
+        \text{$n$ quadratic residue modulo $5$} \ &\Leftrightarrow \ n \equiv 0, 1, 4 \mod 5 \\
+        \text{$n$ quadratic residue modulo $7$} \ &\Leftrightarrow \ n \equiv 0, 1, 4, 2 \mod 7
+    \end{align*}
+    These cases have been excluded by assumption.
+
+    The other direction follows by reversing the above computation.
+    The claim now follows from Proposition~\ref{prop:p_adic_points_techniques}.
+\end{proof}
+However, there is one problem here.
+Using a computer, it is easy to see that the linear equations
+\begin{equation*}
+    \forall n \in \F_7: \ f_0 + f_1 n + f_2 n^2 + n^3 \equiv 3, 5, 6 \mod 7
+\end{equation*}
+This seems to indicate that I have indeed misunderstood the task, and we only look for Elliptic Curves $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$ such that there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ for every $p \neq 3, 5, 7$, and do not require further properties for $E(\Z_3), E(\Z_5)$ and $E(\Z_7)$.
+
+So instead consider a strengthening of Proposition~\ref{prop:p_adic_points_techniques} part four.
+\begin{prop}
+    Let $p \geq 5$ be a prime and $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$ an Elliptic Curve with $f_0, f_1, f_2 \in \Z$.
+    Then there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$.
+\end{prop}
+\begin{proof}
+    If $p \geq 11$ and $p \notdivides \Delta(E)$ then $\tilde{E}$ is an Elliptic Curve over $\F_p$ and the claim follows from Proposition~\ref{prop:p_adic_points_techniques}.
+    Using a computer, it is easy to check that the claim holds for $p = 5$ and $p = 7$ (there are only $5^5$ resp. $7^7$ different combinations of $f_0, f_1, f_2, x, y \in \F_5$ resp. $\F_7$).
+
+    So assume now that $p \divides \Delta(E)$, hence $x^3 + f_2 x^2 + f_1 x + f_0$ factors as
+    \begin{equation*}
+        x^3 + f_2 x^2 + f_1 x + f_0 \equiv (x - \alpha)^2(x - \beta) \mod p
+    \end{equation*}
+    Now note that for $t \in \F_p$ have
+    \begin{equation*}
+        \left( t^2 + \beta, \ t (t^2 + \beta - \alpha) \right) \in \tilde{E}
+    \end{equation*}
+    Hence, we find a function
+    \begin{equation*}
+        \phi: \F_p \to \tilde{E}(\F_p) \setminus \{\O\}, \quad t \mapsto \left( t^2 + \beta, \ t (t^2 + \beta - \alpha) \right)
+    \end{equation*}
+    If there is $\gamma \in \F_p$ with $\gamma^2 = \alpha - \beta$, then 
+    \begin{equation*}
+        \restr{\phi}{\F_p \setminus \{-\gamma\}}
+    \end{equation*}
+    is injective, otherwise $\phi$ is injective.
+    Hence, we see that $\#(\tilde{E}(\F_p) \setminus \{\O\}) \geq \#\F_p - 1 \geq 4$ and so $\#\tilde{E}(\F_p) \geq 5$.
+    It follows that there is $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_p)$ with $\tilde{y} \neq 0$.
+    By a Hensel-lifting argument as in Proposition~\ref{prop:p_adic_points_techniques}, we now see that there is $\gamma \in \Z_p$ with $(x, \gamma) \in E(\Z_p)$ and $|\gamma|_p = 1$.
+\end{proof}
+
 \printbibliography

### 2022-03-12 Elliptic Curves/submission.tex
Answered question 1

@@
     \begin{align*}
-        p = 3 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 2 \mod 3 \\
-        p = 5 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 2, 3 \mod 5 \\
-        p = 7 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 3, 5, 6 \mod 7
+        p = 3 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 0, 2 \mod 3 \\
+        p = 5 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 0, 2, 3 \mod 5 \\
+        p = 7 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 0, 3, 5, 6 \mod 7
     \end{align*}
@@
     \end{align*}
-    These cases have been excluded by assumption.
+    Except for $n \equiv 0 \mod p$, these cases have been excluded by assumption.
+    However we assumed that $y \not\equiv 0 \mod p$, so $y^2 \not\equiv 0 \mod p$ and the claim follows.
 
@@
 However, there is one problem here.
-Using a computer, it is easy to see that the linear equations
-\begin{equation*}
-    \forall n \in \F_7: \ f_0 + f_1 n + f_2 n^2 + n^3 \equiv 3, 5, 6 \mod 7
-\end{equation*}
+Using a computer, one can easily find (e.g. by trying all possibilities) that there are no $f_0, f_1, f_2 \in \Z$ such that the above conditions are (simultaneously) fulfilled for $3$, $5$ and $7$.
 This seems to indicate that I have indeed misunderstood the task, and we only look for Elliptic Curves $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$ such that there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ for every $p \neq 3, 5, 7$, and do not require further properties for $E(\Z_3), E(\Z_5)$ and $E(\Z_7)$.
 
-So instead consider a strengthening of Proposition~\ref{prop:p_adic_points_techniques} part four.
+So instead consider a strengthening of the last part of Proposition~\ref{prop:p_adic_points_techniques}.
 \begin{prop}
-    Let $p \geq 5$ be a prime and $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$ an Elliptic Curve with $f_0, f_1, f_2 \in \Z$.
+    \label{prop:points_in_EZp}
+    Let $p \geq 11$ be a prime and $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$ an Elliptic Curve with $f_0, f_1, f_2 \in \Z$.
     Then there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$.
@@
     If $p \geq 11$ and $p \notdivides \Delta(E)$ then $\tilde{E}$ is an Elliptic Curve over $\F_p$ and the claim follows from Proposition~\ref{prop:p_adic_points_techniques}.
-    Using a computer, it is easy to check that the claim holds for $p = 5$ and $p = 7$ (there are only $5^5$ resp. $7^7$ different combinations of $f_0, f_1, f_2, x, y \in \F_5$ resp. $\F_7$).
 
@@
     \begin{equation*}
-        x^3 + f_2 x^2 + f_1 x + f_0 \equiv (x - \alpha)^2(x - \beta) \mod p
+        x^3 + \tilde{f}_2 x^2 + \tilde{f}_1 x + \tilde{f}_0 \equiv (x - \alpha)^2(x - \beta)
     \end{equation*}
+    with $\alpha, \beta \in \bar{\F}_p$.
+    However, note that $\F_p$ is perfect, so $(x - \alpha)^2(x - \beta)$ cannot be irreducible over $\F_p$, otherwise $\F_p[x] / \langle(x - \alpha)^2(x - \beta)\rangle$ would be a non-separable field extension of $\F_p$.
+    Thus, either $\alpha \in \F_p$ or $\beta \in \F_p$.
+    If $\alpha \in \F_p$, then clearly also $\beta = -2\alpha - \tilde{f}_2 \in \F_p$.
+    If $\beta \in \F_p$, then also $(x - \alpha)^2 \in \F_p[x]$ and again by perfectness of $\F_p$, note that $\alpha \in \F_p$.
+    So $\alpha, \beta \in \F_p$.
+
     Now note that for $t \in \F_p$ have
@@
     \begin{equation*}
-        \restr{\phi}{\F_p \setminus \{-\gamma\}}
+        \restr{\phi}{\F_p \setminus \{-\gamma\}}: \F_p \setminus \{-\gamma\} \to \tilde{E}(\F_p)
     \end{equation*}
@@
 \end{proof}
+The above proposition shows that constructing Elliptic Curves $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$ such that there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ for all primes $p \neq 3, 5, 7$ is indeed quite simple, as almost all curves satisfy this.
+This only case that can fail is $p = 2$, but here, the condition is fulfilled quite often, so we can just try different choices.
+\begin{example}
+    Let
+    \begin{align*}
+        E_1: \ &y^2 = x^3 + 2 x \\
+        E_2: \ &y^2 = x^3 + 2 x^2 + 6 x + 5\\
+        E_3: \ &y^2 = x^3 + 6x + 1
+    \end{align*}
+    Note that
+    \begin{align*}
+        1^2 &\equiv 3^3 + 2 \cdot 3 = 33 \mod 8 \\
+        1^2 &\equiv 2^3 + 2 \cdot 2^2 + 6 \cdot 2 + 5 = 33 \mod 8 \\
+        1^2 &\equiv 4^3 + 6 \cdot 4 + 1 = 89 \mod 8
+    \end{align*}
+    so Hensel's Lemma yields points $(x, y) \in E_i(\Z_2)$ with $|y|_2 = 1$ for $i \in \{1, 2, 3\}$.
+    By Proposition~\ref{prop:points_in_EZp}, we have points $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ for all $p \geq 11$.
 
+    Finally, note that trying all points shows
+    \begin{align*}
+        \tilde{E}_1(\F_3) &= \{ (0, 0), (1, 0), (2, 0), \O \} \\
+        \tilde{E}_1(\F_5) &= \{ (0, 0), \O \} \\
+        \tilde{E}_2(\F_7) &= \{ (1, 0), (5, 0), (6, 0), \O \}
+    \end{align*}
+    so there is no point $(x, y) \in E_i(\Z_p)$ with $|y|_p = 1$ for $p \in \{3, 5, 7\}$ and a suitable $i$. 
+\end{example}
 \printbibliography

### 2022-03-13 Elliptic Curves/submission.tex
Solved 2(i)

@@
 \end{example}
+
+\section{Question 2}
+\begin{example}[2(i)]
+    Consider the Elliptic Curve $E: y^2 = x(x + 1)(x + 4)$ defined over $\Q$.
+    Have
+    \begin{equation*}
+        x(x + 1)(x + 4) = x^3 + 5x^2 + 4x = \left( x + \frac 5 3 \right)^3 - \frac {13} 3 \left( x + \frac 5 3 \right) + \frac {70} {27}
+    \end{equation*}
+    So $E$ is isomorphic to $E': y^2 = x^3 - \frac {13} 3 x + \frac {70} {27}$ via
+    \begin{equation*}
+        \psi: E \to E', \quad (x, y) \mapsto \left( x + \frac 5 3, y \right)
+    \end{equation*}
+    This isomorphism preserves the group structure\footnote{It is a general result that all isogenies are group homomorphisms, but in this case, it is also directly obvious as the isomorphism is linear, hence maps lines to lines.}, and so $E'_{\mathrm{tors}} \cong E_{\mathrm{tors}}$.
+    Have
+    \begin{equation*}
+        \Delta(E') = 4 \left( -\frac {13} 3 \right)^3 + 27 \left( \frac {70} {27} \right)^2 = -144 = \Delta(E)
+    \end{equation*}
+    Consider now any prime $p \neq 2, 3$.
+    Then the isomorphism $\psi: E \to E'$ induces an isomorphism $\tilde{\psi}: \tilde{E} \to \tilde{E}'$ between the reductions modulo $p$.
+    Note that $\tilde{E}, \tilde{E}'$ are still Elliptic Curves.
+
+    Hence, we can use results from the lecture on the reduction modulo $p \neq 2, 3$ for the curve $E$, even though it is not given by an equation of the form $y^2 = x^3 + Ax + B$, as all these statements are preserved under isomorphism.
+    In particular, we see that the kernel of reduction $E_1(\Q_5)$ has no torsion and so there is an embedding
+    \begin{equation*}
+        E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_5)
+    \end{equation*}
+    Note that
+    \begin{equation*}
+        \tilde{E}(\F_5) = \{ (0, 0), (1, 0), (2, 1), (2, 4), (3, 2), (3, 3), (4, 0), \O \}
+    \end{equation*}
+    has order 8.
+    Clearly
+    \begin{equation*}
+        (0, 0), (-1, 0), (-4, 0), \O \in E_{\mathrm{tors}}(\Q)
+    \end{equation*}
+    So the only remaining question is whether this is all the torsion (i.e. $\#E_{\mathrm{tors}}(\Q) = 4$) or there are more points (i.e. $\#E_{\mathrm{tors}}(\Q) = 8$).
+
+    Consider now $P = (-2, 2) \in E$.
+    The tangent at $P$ is given by $y = -x$ and the third point of intersection with $E$ is thus $(0, 0)$.
+    Hence $P + P = (0, 0)$ and so $[4]P = \O$.
+    It follows that $\#E_{\mathrm{tors}}(\Q) = 8$ and furthermore that 
+    \begin{equation*}
+        E_{\mathrm{tors}}(E) = \langle P, (-1, 0) \rangle \cong \Z/4\Z \oplus \Z/2\Z
+    \end{equation*}
+\end{example}
+
 \printbibliography

### 2022-03-13 Elliptic Curves/submission.tex
Done part of 2(ii)

@@
 \begin{equation*}
-    E(R) := \{ (x, y) \in E \ | \ x, y \in R \}
+    E(R) := \{ (x, y) \in E(\bar{k}) \ | \ x, y \in R \} \cup \{\O\}
 \end{equation*}
-for an Elliptic Curve $E$ defined over $k$ and any ring $R$ contained in some extension field of $k$.
+for an Elliptic Curve $E$ defined over $k$ and any ring $R$ contained in the algebraic closure $\bar{k}$.
+Note that this is usually not a group anymore, and does not have a lot of nice structure.
 \begin{prop}[1(iii)]
@@
 \end{example}
+\begin{example}
+    Consider the Elliptic Curve $E: y^2 = x(x + 1)(x - 8)$.
+    Note that we have an isomorphism
+    \begin{equation*}
+        \psi: E \to E', \quad (x, y) \mapsto \left( x - \frac 7 3, y \right)
+    \end{equation*}
+    to the Elliptic Curve $E': y^2 = x^3 - \frac {73} 3 x - \frac {1190} {27}$ defined over $\Q$.
+    Have that
+    \begin{equation*}
+        \Delta(E) = -72^2 = -5184 = \Delta(E')
+    \end{equation*}
+    Note that this has only the prime factors $2$ and $3$.
+    As before, this shows that all the results from the lecture on the reduction modulo $p \neq 2, 3$ are also valid for the curve $E$, even though it is not defined by an equation of the form $y^2 = x^3 + Ax + B$.
+    We see that
+    \begin{equation*}
+        \tilde{E}(\F_7) = \{ (0, 0), (1, 0), (4, 2), (4, 5), (5, 1), (5, 6), (6, 0), \O \}
+    \end{equation*}
+    and thus has order 8.
+    As before, we this only leaves two possible cases, either the obvious 2-torsion points are all torsion points (i.e.
+$\#E_{\mathrm{tors}}(\Q) = 4$) or each of the points $\tilde{E}(\F_5)$ lifts to a torsion point (i.e.
+$\#E_{\mathrm{tors}}(\Q) = 8$).
 
-\printbibliography
+    Unlike the previous example however, this time the former is the case.
+    To see this, we use the Nagell-Lutz theorem.
+    Assume $(x, y) \in E_{\mathrm{tors}}(\Q)$ with $y \neq 0$.
+    Then it yields that $y^2 \divides \Delta(E) = -72^2$ and so $y \divides 72$.
+    So
+    \begin{equation*}
+        y \in \{ \pm 1, \pm 2, \pm 4, \pm 8, \pm 3 \pm 6, \pm 12, \pm 24, \pm 9, \pm 18, \pm 36, \pm 72 \}
+    \end{equation*}
+    Furthermore $y \not\equiv 0 \mod 7$ and since $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_7)$, it follows that
+    \begin{equation*}
+        (\tilde{x}, \tilde{y}) \in \{ (4, \pm 2), (5, \pm 1) \} \ \Rightarrow \ \tilde{y} \in \{ \pm 1, \pm 2 \}
+    \end{equation*}
+    Thus we only have the possibilities
+    \begin{equation*}
+        y \in \{ \pm 1, \pm 2, \pm 8, \pm 6, \pm 12, \pm 9, \pm 36, \pm 72 \}
+    \end{equation*}
+    Furthermore, observe that
+    \begin{equation*}
+        \tilde{E}(\F_{11}) = \{ (0, 0), (5, 3), (5, 8), (6, 2), (6, 9), (8, 0), (10, 0), \O \}
+    \end{equation*}
+    and so it follows by the same argument that
+    \begin{equation*}
+        \tilde{y} \in \{ \pm 2, \pm 3 \}
+    \end{equation*}
+    This further restricts the possibilities to
+    \begin{equation*}
+        y \in \{ \pm 2, \pm 8, \pm 12, \pm 9 \}
+    \end{equation*}
+    Finally, observe that none of the equations
+    \begin{align*}
+        4 &= x^3 - 7x^2 - 8x \\
+        64 &= x^3 - 7x^2 - 8x \\
+        144 &= x^3 - 7x^2 - 8x \\
+        81 &= x^3 - 7x^2 - 8x
+    \end{align*}
+    has a solution in $\Q$.
+    To see this, use e.g. the rational root theorem and some computation:
+
+    The only factors of $4$ are $\pm 1, \pm 2, \pm 4$ and none solves $4 = x^3 + 7x^2 - 8x$.
+    The only factors of $64$ are $\pm 1, \pm 2, \pm 4, \pm 8, \pm 16, \pm 32, \pm 64$ and none solves $64 = x^3 - 7x^2 - 8x$.
+    The only factors of $144$ are $\pm 1, \pm 2, \pm 4, \pm 8, \pm 16, \pm 3, \pm 6, \pm 12, \pm 24, \pm 48, \pm 9, \pm 18, \pm 36, \pm 72, \pm 144$ and none solves $144 = x^3 - 7x^2 - 8x$.
+    The only factors of $81$ are $\pm 1, \pm 3, \pm 9, \pm 27, \pm 81$ and none solves $81 = x^3 - 7x^2 - 8x$.
+\end{example}
 \end{document}

### 2022-03-13 Elliptic Curves/submission.tex
proved for 2(ii) that Z4 x Z2 embeds into any E(Fp)

@@
 \end{example}
+\begin{prop}
+    \label{prop:duplication_formula}
+    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve over a field $k$.
+    For a point $P \in E$ with $P \neq \O$ denote by $x(P)$ its (affine) $x$-coordinate.
+    Then have for all $P \in E$ with $P \neq -P$ that
+    \begin{equation*}
+        x([2]P) = \frac {x(P)^4 - 2a_4 x(P)^2 - 8a_6x(P) + a_4^2 - 4a_2a_6} {4(x(P)^3 + a_2 x(P)^2 + a_4 x(P) + a_6)}
+    \end{equation*}  
+\end{prop}
+\begin{prop}
+    Let $E: y^2 = x(x + 1)(x - 8)$ be the Elliptic Curve from the previous example.
+    The for each prime $p \geq 5$, have that $\Z/4\Z \oplus \Z/2\Z$ is a subgroup of $\tilde{E}(\F_p)$.
+\end{prop}
+\begin{proof}
+    First of all, note that the duplication formula from Proposition~\ref{prop:duplication_formula} has the form
+    \begin{equation*}
+        x([2]P) = \frac {x(P)^4 + 16 x(P) + 64} {4 x(P)^3 - 28 x(P)^2 - 32 x(P)}
+    \end{equation*}
+    Consider any prime $p \geq 5$.
+    Clearly there are the 2-torsion points
+    \begin{equation*}
+        (0, 0), (-1, 0), (8, 0) \in \tilde{E}(\F_p)
+    \end{equation*}
+
+    \paragraph{Case 1} If $-1$ is a quadratic residue modulo $p$, then there is $\beta \in \F_p$ with $\beta^2 = -36$.
+    Have then that $(2, \beta) \in \tilde{E}(\F_p)$ and
+    \begin{equation*}
+        x([2](2, \beta)) = \frac {2^4 + 16 \cdot 2^2 + 64} {4 \cdot 2^3 - 28 \cdot 2^2 - 32 \cdot 2} = \frac {144} {-144} = -1
+    \end{equation*}
+    and so $[2](2, \beta) = (-1, 0)$ is a 2-torsion point.
+    Thus $(2, \beta)$ has order $4$ and we see that
+    \begin{equation*}
+        \langle (2, \beta), (0, 0) \rangle \cong \Z/4\Z \oplus \Z/2\Z
+    \end{equation*}
+
+    \paragraph{Case 2} If $-2$ is a quadratic residue modulo $p$, then there is $\alpha \in \F_p$ with $\alpha^2 = -8$.
+    Then
+    \begin{equation*}
+        (\alpha - 8)^2 = (\alpha^2 + \alpha)(\alpha - 8) = \alpha(\alpha + 1)(\alpha - 8)
+    \end{equation*}
+    With $\beta := \alpha - 8$ we now find $(\alpha, \beta) \in \tilde{E}(\F_p)$ and
+    \begin{equation*}
+        x([2](\alpha, \beta)) = \frac {\alpha^4 + 16 \alpha^2 + 64} {4 \alpha^3 - 28 \alpha^2 - 32 \alpha} = \frac {(\alpha^2 + 8)^2} {4 \alpha^3 - 28 \alpha^2 - 32 \alpha} = 0
+    \end{equation*}
+    and so $[2](\alpha, \beta) = (0, 0)$ is a 2-torsion point.
+    Hence, $(\alpha, \beta)$ has order $4$ and thus
+    \begin{equation*}
+        \langle (\alpha, \beta), (-1, 0) \rangle \cong \Z/4\Z \oplus \Z/2\Z
+    \end{equation*}
+
+    \paragraph{Case 3} If $2$ is a quadratic residue modulo $p$, then there is $\alpha' \in \F_p$ with $(\alpha')^2 = 72$ and so there is $\alpha = \alpha' + 8$ with $\alpha^2 - 16\alpha - 8 = 0$.
+    Note that $\alpha^2 = 16\alpha + 8$ and thus
+    \begin{equation*}
+        (9\alpha - 24)^2 = 81 \cdot 16 \alpha + 81 \cdot 8 - 432 \alpha + 576 = 1224 + 864\alpha = \alpha^3 - 7\alpha^2 - 8\alpha= \alpha (\alpha + 1) (\alpha - 8)
+    \end{equation*}
+    With $\beta := 9\alpha - 24$ we now find $(\alpha, \beta) \in \tilde{E}(\F_p)$ and
+    \begin{align*}
+        x([2](\alpha, \beta)) =& \frac {\alpha^4 + 16 \alpha^2 + 64} {4\alpha^3 - 28\alpha^2 - 32\alpha} = \frac {(\alpha^2 + 8)^2} {4\alpha(\alpha + 1)(\alpha - 8)} \\
+        =& \frac {16^2(\alpha + 1)^2} {4\alpha(\alpha + 1)(\alpha - 8)} = \frac {64 (\alpha + 1)} {(\alpha^2 - 8\alpha)} = \frac {64 (\alpha + 1)} {16\alpha + 8 - 8\alpha} = 8
+    \end{align*}
+    and so $[2](\alpha, \beta) = (8, 0)$ is a 2-torsion point.
+    Hence $(\alpha, \beta)$ has order $4$ and thus
+    \begin{equation*}
+        \langle (\alpha, \beta), (0, 0) \rangle \cong \Z/4\Z \oplus \Z/2\Z
+    \end{equation*}
+
+    Since the Legendre symbol is multiplicative and $(-2)(-1) = 2$, these cases are exhaustive.
+\end{proof}
 \end{document}

### 2022-03-13 Elliptic Curves/submission.tex
Worked more on 2(ii)

@@
 \end{example}
-\begin{example}
+\begin{example}[2(ii)]
+    \label{ex:2ii}
     Consider the Elliptic Curve $E: y^2 = x(x + 1)(x - 8)$.
@@
     The only factors of $81$ are $\pm 1, \pm 3, \pm 9, \pm 27, \pm 81$ and none solves $81 = x^3 - 7x^2 - 8x$.
+
+    Note that the usual approach to bound the size of $E_{\mathrm{tors}}(\Q)$ is use to the theorem that this embeds into $\tilde{E}(\F_p)$ whenever $\tilde{E}$ is an Elliptic Curve.
+    However, for this example, this was not sufficient, as we could not find a prime such that the group $\Z/4\Z \oplus \Z/2\Z$ does not embed into $\tilde{E}(\F_p)$.
+    In the next part, we want to study this phenomenon more carefully and indeed see that there is no such prime, i.e.
+just considering reduction modulo $p$ is not sufficient to compute the torsion group of $E$.
 \end{example}
+First, it is convenient to have a closed formula for the $x$-coordinate of $[2]P$ for a point $P$ on an Elliptic Curve.
 \begin{prop}
@@
     Consider any prime $p \geq 5$.
-    Clearly there are the 2-torsion points
-    \begin{equation*}
-        (0, 0), (-1, 0), (8, 0) \in \tilde{E}(\F_p)
-    \end{equation*}
 

### 2022-03-14 Elliptic Curves/submission.tex
Found partial solution for 2(ii)

@@
     In the next part, we want to study this phenomenon more carefully and indeed see that there is no such prime, i.e.
-just considering reduction modulo $p$ is not sufficient to compute the torsion group of $E$.
+it is impossible to show that $\#E_{\mathrm{tors}}(\Q) \neq 8$ by just considering the reductions modulo $p$.
 \end{example}
@@
 \end{proof}
+To find more examples, it might be a good idea to use the structure from the previous theorem, but take another set of exhaustive cases.
+So consider an Elliptic Curve
+\begin{equation*}
+    E: y^2 = x(x - \alpha)(x - \beta) = x^3 - (\alpha + \beta)x^2 + \alpha \beta x
+\end{equation*}
+with 3 nontrivial torsion points $(\alpha, 0), (\beta, 0), (0, 0)$ over $\Q$.
+We study in which cases there is some $P \in \tilde{E}(\F_p)$ of order 4.
+\begin{lemma}
+    Let $E: y^2 = x(x - \alpha)(x - \beta)$ be an Elliptic Curve over a field $k$ of characteristic $\neq 2$.
+    Then there exists $P \in E(k)$ of order 4 if and only if $k$ has a root of
+    \begin{equation*}
+        \left(\mu^4 + 2(\alpha + \beta)\mu^2 + (\alpha - \beta)^2\right)\left(\mu^4 + (2\beta - 4\alpha)\mu^2 + \beta^2\right)\left(\mu^4 + (2\alpha - 4\beta)\mu^2 + \alpha^2\right)
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    The duplication formula for $E$ gives with $x = x(P)$ that
+    \begin{equation*}
+        x([2]P) = d(x) := \frac {x^4 - 2 \alpha \beta x^2 + \alpha^2 \beta^2} {4x^3 - 4(\alpha + \beta) x^2 + 4 \alpha \beta x}
+    \end{equation*}
+
+    \paragraph{Case 1} If there is $\mu \in \F_p$ with $\mu^4 + 2(\alpha + \beta)\mu^2 + (\alpha - \beta)^2 = 0$.
+
+    Then note that there is $\gamma := \frac 1 2 (\mu^2 - \alpha - \beta)$ such that $\gamma^2 = \alpha\beta$.
+    Thus
+    \begin{equation*}
+        d(\gamma) = \frac {\gamma^4 - 2\alpha\beta\gamma^2 + \alpha^2\beta^2} {4\gamma^3 - 4(\alpha + \beta) \gamma^2 + 4 \alpha \beta \gamma} = \frac 0 {4\gamma^3 - 4(\alpha + \beta) \gamma^2 + 4 \alpha \beta \gamma} = 0
+    \end{equation*}
+    Note further that
+    \begin{equation*}
+        \gamma^3 - (\alpha + \beta)\gamma^2 + \alpha\beta\gamma = 2\alpha\beta\gamma - \alpha\beta(\alpha + \beta) = \alpha\beta(2\gamma - \alpha - \beta) = \gamma^2 \mu^2
+    \end{equation*}
+    since $\mu^2 = 2\gamma - \alpha - \beta$.
+    So there is a point $(\gamma, \gamma\mu) \in E(k)$ with $[2](\gamma, \mu) = (0, 0)$.
+
+    \paragraph{Case 2} If there is $\mu \in k$ with $\mu^4 + (2\beta - 4\alpha)\mu^2 + \beta^2 = 0$.
+
+    Then note that there is $\gamma := \frac 1 2 (\mu^2 + \beta)$ such that $\gamma^2 - 2\alpha\gamma + \alpha\beta = 0$.
+    Thus
+    \begin{align*}
+        &\gamma^4 - 2 \alpha \beta \gamma^2 + \alpha^2 \beta^2 = 4\alpha \gamma^3 - 4\alpha(\alpha + \beta) \gamma^2 + 4 \alpha^2 \beta \gamma \\
+        =& \gamma^4 - 4\alpha \gamma^3 + (4\alpha^2 + 4\alpha\beta - 2\alpha\beta)\gamma^2 - 4\alpha^2\beta \gamma + \alpha^2\beta^2 \\
+        =& \gamma^4 - 4\alpha \gamma^3 + 2\alpha(2\alpha + \beta)\gamma^2 - 4\alpha^2\beta \gamma + \alpha^2\beta^2 \\
+        =& (\gamma^2 - 2\alpha \gamma + \alpha \beta)^2 = 0^2 = 0
+    \end{align*}
+    and so
+    \begin{equation*}
+        \gamma^4 - 2 \alpha \beta \gamma^2 + \alpha^2 \beta^2 = \alpha(4\gamma^3 - 4(\alpha + \beta) \gamma^2 + 4 \alpha \beta \gamma)
+    \end{equation*}
+    It follows that
+    \begin{equation*}
+        d(\gamma) = \frac {\gamma^4 - 2 \alpha \beta \gamma^2 + \alpha^2 \beta^2} {4\gamma^3 - 4(\alpha + \beta) \gamma^2 + 4 \alpha \beta \gamma} = \alpha
+    \end{equation*}
+    Furthermore note that
+    \begin{align*}
+        \gamma^3 - (\alpha + \beta)\gamma^2 + \alpha\beta\gamma =& \gamma(2\alpha\gamma - \alpha\beta) - (2\alpha\gamma - \alpha\beta)(\alpha + \beta) + \alpha\beta\gamma \\
+        =& 2\alpha(2\alpha\gamma - \alpha\beta) - 2\alpha^2\gamma - 2\alpha\beta\gamma + \alpha^2\beta + \alpha\beta^2 \\
+        =& \gamma(4\alpha^2 - 2\alpha^2 - 2\alpha\beta) + \alpha^2\beta + \alpha\beta^2 - 2\alpha^2\beta \\
+        =& 2\alpha\gamma(\alpha - \beta) + \alpha\beta(\beta - \alpha) = \alpha(\alpha - \beta)(2\gamma - \beta) = (\gamma - \alpha)^2\mu^2
+    \end{align*}
+    as $\mu^2 = 2\gamma - \beta$ and $(\gamma - \alpha)^2 = 2\alpha\gamma - \alpha\beta - 2\gamma\alpha + \alpha^2 = \alpha(\alpha - \beta)$.
+    So there is a point $(\gamma, (\gamma - \alpha)\mu) \in E(k)$ with $[2](\gamma, (\gamma - \alpha)\mu) = (\alpha, 0)$.
+
+    \paragraph{Case 3} Similarly, if there is $\mu \in k$ with $\mu^4 + (2\alpha - 4\beta)\mu^2 + \alpha^2 = 0$, then there is a point $P \in E(k)$ with $[2]P = (\beta, 0)$
+\end{proof}
 \end{document}

### 2022-03-16 Elliptic Curves/submission.tex
Worked more on 3(i)

@@
     Let $E: y^2 = x(x - \alpha)(x - \beta)$ be an Elliptic Curve over a field $k$ of characteristic $\neq 2$.
-    Then there exists $P \in E(k)$ of order 4 if and only if $k$ has a root of
+    Then there exists $P \in E(k)$ of order 4 if and only if $k$ has a root of the polynomial $F(T)$ given by
     \begin{equation*}
-        \left(\mu^4 + 2(\alpha + \beta)\mu^2 + (\alpha - \beta)^2\right)\left(\mu^4 + (2\beta - 4\alpha)\mu^2 + \beta^2\right)\left(\mu^4 + (2\alpha - 4\beta)\mu^2 + \alpha^2\right)
+        \left(T^4 + 2(\alpha + \beta)T^2 + (\alpha - \beta)^2\right)\left(T^4 + (2\beta - 4\alpha)T^2 + \beta^2\right)\left(T^4 + (2\alpha - 4\beta)T^2 + \alpha^2\right)
     \end{equation*}
@@
         =& \gamma(4\alpha^2 - 2\alpha^2 - 2\alpha\beta) + \alpha^2\beta + \alpha\beta^2 - 2\alpha^2\beta \\
-        =& 2\alpha\gamma(\alpha - \beta) + \alpha\beta(\beta - \alpha) = \alpha(\alpha - \beta)(2\gamma - \beta) = (\gamma - \alpha)^2\mu^2
+        =& 2\alpha\gamma(\alpha - \beta) + \alpha\beta(\beta - \alpha) \\
+        =& \alpha(\alpha - \beta)(2\gamma - \beta) \\
+        =& (\gamma - \alpha)^2\mu^2
     \end{align*}
@@
 \end{proof}
+Hence, we just have to find $\alpha, \beta \in \Q$ such that the polynomial $F$ has no root in $\Q$ and a root in every $\F_p$ (where $p$ is a prime of good reduction).
+First, note that $F(T) = G(T^2)$ where
+\begin{equation*}
+    G(T) = \left( T^2 + 2(\alpha + \beta)T + (\alpha - \beta)^2 \right)\left( T^2 + (2\beta - 4\alpha)T + \beta^2 \right)\left( T^2 + (2\alpha - \beta)T + \alpha^2 \right)
+\end{equation*}
+Since the cases where this has a root in $\Q$ are clearly a Zariski-closed condition on $(\alpha, \beta)$, we see that ``most'' value of $\alpha, \beta$ will result in no root of $F(T)$.
+Hence, we focus on finding $\alpha, \beta \in \Z$ such that $F(T)$ has a root modulo any prime $p$ (of good reduction).
+A necessary condition for that is that $G(T)$ has a root modulo any prime $p$, which in turn is equivalent that any of the discriminants (scaled by squares)
+\begin{equation*}
+    \alpha\beta, \ (\alpha - 3\beta)(\alpha - \beta), \ (\beta - 3\alpha)(\beta - \alpha)
+\end{equation*}
+is a quadratic residue modulo $p$, for any prime $p$.
+
+\section*{Question 3}
+\begin{prop}
+    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve with $a_2, a_4, a_6 \in \Z$ and $P = (\alpha, \beta) \in E$ a point of order 5 with $\alpha = 0$.
+\end{prop}
+\begin{proof}
+    Let $(\alpha_2, \beta_2) = [2]P$.
+    First note that by assumption have
+    \begin{align*}
+        [3]P = (\alpha_2, -\beta_2), \quad [4]P = (0, -\beta), \quad [5]P = \O
+    \end{align*}
+    Further, by the Nagell-Lutz theorem, we know that $\beta, \alpha_2, \beta_2 \in \Z$.
+    Applying the duplication formula shows
+    \begin{equation*}
+        \alpha_2 = \frac {a_4^2} {4a_6} - a_2 \in \Z
+    \end{equation*}
+    and so $2\beta \divides a_4$.
+    Now apply the duplication formula twice, and see that
+    \begin{align*}
+        x([4]P) = \frac {f(x)x} {g(x)} + \frac 1 {g(x)} \Bigl( &a_4^8 - 16a_2a_4^6a_6 + 96a_2^2a_4^4a_6^2 - 256a_2^3a_4^2a_6^3 + 256a_2^4a_6^4 - 32a_4^5a_6^2 \\
+        &+ 256a_2a_4^3a_6^3 - 512a_2^2a_4a_6^4 - 256a_4^2a_6^4 + 1024a_2a_6^5 \Bigr)
+    \end{align*}
+    with polynomials $f, g \in k[x]$.
+    Since $[4]P = -P = (0, -\beta)$ by assumption, we see that
+    \begin{align*}
+        0 = &a_4^8 - 16a_2a_4^6a_6 + 96a_2^2a_4^4a_6^2 - 256a_2^3a_4^2a_6^3 + 256a_2^4a_6^4 - 32a_4^5a_6^2 \\
+        &+ 256a_2a_4^3a_6^3 - 512a_2^2a_4a_6^4 - 256a_4^2a_6^4 + 1024a_2a_6^5 := F
+    \end{align*}
+    Note that $F$ factors as
+    \begin{align*}
+        F =& (-a_4^2 + 4a_2a_6) \cdot \\
+        &(\underbrace{-a_4^6 + 12a_2a_4^4a_6 - 48a_2^2a_4^2a_6^2 + 64a_2^3a_6^3 + 32a_4^3a_6^2 - 128a_2a_4a_6^3 + 256a_6^4}_{=: G})
+    \end{align*}
+    \paragraph{If $4a_2a_6 = a_4^2$} As $\alpha_2 = \frac 1 4 a_4^2/a_6 - a_2$ it follows that $\alpha_2 = 0$, a contradiction ($\alpha_2 = 0$ would imply $[2]P = P$ or $[2]P = -P$, both contradicting the assumption that $\mathrm{ord}(P) = 5$).
+    \paragraph{If $G = 0$} Have for any prime $p \divides a_4$
+\end{proof}
+\begin{prop}
+    Let $E: y^2 + (v + 1) x y + v y = x^3 + v x^2$ be an Elliptic Curve and $P = (x_1, y_1), Q = (x_2, y_2) \in E$ with $x_1 \neq x_2$.
+    Then
+    \begin{equation*}
+        x(P + Q) = -x_1 - x_2 + m^2 + m(v + 1) - v
+    \end{equation*}
+    where
+    \begin{equation*}
+        m = \frac {y_2 - y_1} {x_2 - x_1}
+    \end{equation*}
+\end{prop}
+\begin{prop}
+    Let
+    \begin{equation*}
+        E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2 + a_4 x + a_6    
+    \end{equation*}
+    and
+    \begin{equation*}
+        E': y^2 + a'_1 x y + a'_3 y = x^3 + a'_2 x^2 + a'_4 x + a'_6    
+    \end{equation*}
+    be Elliptic Curves.
+    If there are five distinct points $P_1, ..., P_5 \in E \cap E'$ in ``sufficiently independent position'', then $E = E'$ (meaning $a_i = a'_i$).
+
+    To be completely precise, there is a fixed 1-dimensional algebraic curve $C \subseteq \mathbb{A}^{10}$ (that does not depend on $E$, $E'$ or $P_1, ..., P_5$) of degree $6$ such that if there are five points $P_1 = (x_1, y_1), ..., P_5 = (x_5, y_5) \in E \cap E'$ with
+    \begin{equation*}
+        (x_1, ..., x_5, y_1, ..., y_5) \notin C
+    \end{equation*}
+    then $E = E'$.
+\end{prop}
+\begin{proof}
+    Consider the matrix $A = (a_{ij}) \in k[x_1, ..., x_5, y_1, ..., y_5]^{5 \times 5}$ given by
+    \begin{equation*}
+        a_{ij} = \begin{cases}
+            x_i^{j - 1} & \text{if $j \leq 3$} \\
+            -x_iy_i & \text{if $j = 4$} \\
+            -y_i & \text{if $j = 5$}
+        \end{cases}
+    \end{equation*}
+    Let $C = \V(\det(A))$ and assume there are five points $P_1 = (x_1, y_1), ..., P_5(x_5, y_5) \in E \cap E'$.
+    Then the matrix $A_P := A(x_1, ..., x_5, y_1, ..., y_5) \in k^{5 \times 5}$ is regular.
+    Since $P_1, ..., P_5 \in E \cap E'$, see that
+    \begin{equation*}
+        A_P (a_6 \ \ a_4 \ \ a_2 \ \ a_1 \ \ a_3)^T = (y_1^2 x_1^3 \ \ ... \ \ y_5^2 x_5^3)^T
+    \end{equation*}
+    and
+    \begin{equation*}
+        A_P (a'_6 \ \ a'_4 \ \ a'_2 \ \ a'_1 \ \ a'_3)^T = (y_1^2 x_1^3 \ \ ... \ \ y_5^2 x_5^3)^T
+    \end{equation*}
+    Thus by linear algebra, find that $E = E'$.
+\end{proof}
+\begin{prop}[3(i)]
+    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$ and $P = (\alpha_1, \beta_1) \in E(k)$ a (nontrivial) 5-torsion point.
+    wlog $\alpha_1 = 0$.
+    Let further $[2]P = (\alpha_2, \beta_2)$ and note that $\alpha_1 = 0 \neq \alpha_2$.
+    Then there exists a birational equivalence $E \to E'$ where $E': y^2 + (1 + v) x y + v y = x^3 + v x^2$ given by
+    \begin{equation*}
+        \psi: E \to E', \quad (x, y) \mapsto (u^2 x, u^3 y + u^2 s x + t)
+    \end{equation*}
+    where
+    \begin{equation*}
+        v = \frac {\beta_2} {\beta}, \quad t = -\frac {\beta_2} {2\beta}, \quad u^3 = \frac {\beta_2} {2\beta^2}, \quad s = \frac {u} {\alpha_2} ( \beta_2 + \beta )
+    \end{equation*}
+\end{prop}
+\begin{proof}
+    Clearly $\psi$ maps $E$ to an Elliptic Curve $E''$.
+    Note that by assumption, we have
+    \begin{align*}
+        &[1](0, \beta) = (0, \beta), \quad [2](0, \beta) = (\alpha_2, \beta_2), \\
+        &[3](0, \beta) = -[2](0, \beta) = (\alpha_2, -\beta_2), \quad [4](0, \beta) = -[1](0, \beta) = (0, -\beta)
+    \end{align*}
+    Assume for now that $u^2 \alpha_2 = -v$.
+    Under $\psi$, we see that
+    \begin{equation*}
+        (0, \beta) \mapsto (0, u^3 \beta + t) = \left( 0, \frac {\beta} {2\beta_2} - \frac {\beta} {2\beta_2} \right) = (0, 0) \in E'
+    \end{equation*}
+    and
+    \begin{align*}
+        (\alpha_2, \beta_2) \mapsto (u^2 \alpha_2, u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(-v, \frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
+        &= \left( -v, \frac {\beta_2^2} {\beta^2} \right) = (-v, v^2) \in E'
+    \end{align*}
+    and
+    \begin{align*}
+        (\alpha_2, \beta_2) \mapsto (u^2 \alpha_2, -u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(-v, -\frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
+        &= (-v, 0) \in E'
+    \end{align*}
+    and
+    \begin{align*}
+        (0, -\beta) \mapsto (0, -u^3 \beta + t) = \left( 0, -\frac {\beta_2} {2\beta} - \frac {\beta_2} {2\beta} \right) = (0, -v) \in E'
+    \end{align*}
+    and of course $\O \mapsto \O$.
+    Hence we have $\#(E' \cap E'') \geq 5$ and by the previous proposition we see that $E' = E''$.
+
+    So it is left to show that $\beta/(2\beta^2)$ has a third root in $\Q$ and that $u^2 \alpha_2 = -v$.
+\end{proof}
 \end{document}

### 2022-03-16 Elliptic Curves/submission.tex
Almost done with 3(i)

@@
 
-    So it is left to show that $\beta/(2\beta^2)$ has a third root in $\Q$ and that $u^2 \alpha_2 = -v$.
+    So it is left to show that $\beta_2/(2\beta^2)$ has a third root in $\Q$ and that $u^2 \alpha_2 = -v$.
+    First, note that $u^2 \alpha_2 = -v$ is equivalent to $u^6 \alpha_2 = -v^3$ (since there is only one cubic root in $\Q$).
+    Have
+    \begin{equation*}
+        u^4 \alpha_2 = -v^3 \ \Leftrightarrow \ \frac {\beta_2^2} {4\beta^4} \alpha_2^3 = -\frac {\beta_2^3} {\beta^3} \ \Leftrightarrow \ \alpha_2^3 = -4 \beta \beta_2
+    \end{equation*}
+    Consider the following SAGE script:
+    \lstinputlisting[language = python]{./3i_algebra.sage}
+    The output shows that $\alpha_2^3 = -4 \beta \beta_2$ already follows from the facts
+    \begin{align*}
+        &(0, \beta) \in E, \\
+        &(\alpha_2, \beta_2) \in E, \\
+        &[2](0, \beta) = (\alpha_2, \beta_2), \\
+        &[2](\alpha_2, \beta_2) = (0, -\beta)
+    \end{align*}
+    Hence it suffices to show that $\beta_2/(2\beta^2)$ has a third root in $\Q$.
 \end{proof}

### 2022-03-16 Elliptic Curves/submission.tex
Solve 3i

--- 2022-03-16 Elliptic Curves/submission.tex
@@
 \section*{Question 3}
-\begin{prop}
-    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve with $a_2, a_4, a_6 \in \Z$ and $P = (\alpha, \beta) \in E$ a point of order 5 with $\alpha = 0$.
-\end{prop}
-\begin{proof}
-    Let $(\alpha_2, \beta_2) = [2]P$.
-    First note that by assumption have
-    \begin{align*}
-        [3]P = (\alpha_2, -\beta_2), \quad [4]P = (0, -\beta), \quad [5]P = \O
-    \end{align*}
-    Further, by the Nagell-Lutz theorem, we know that $\beta, \alpha_2, \beta_2 \in \Z$.
-    Applying the duplication formula shows
-    \begin{equation*}
-        \alpha_2 = \frac {a_4^2} {4a_6} - a_2 \in \Z
-    \end{equation*}
-    and so $2\beta \divides a_4$.
-    Now apply the duplication formula twice, and see that
-    \begin{align*}
-        x([4]P) = \frac {f(x)x} {g(x)} + \frac 1 {g(x)} \Bigl( &a_4^8 - 16a_2a_4^6a_6 + 96a_2^2a_4^4a_6^2 - 256a_2^3a_4^2a_6^3 + 256a_2^4a_6^4 - 32a_4^5a_6^2 \\
-        &+ 256a_2a_4^3a_6^3 - 512a_2^2a_4a_6^4 - 256a_4^2a_6^4 + 1024a_2a_6^5 \Bigr)
-    \end{align*}
-    with polynomials $f, g \in k[x]$.
-    Since $[4]P = -P = (0, -\beta)$ by assumption, we see that
-    \begin{align*}
-        0 = &a_4^8 - 16a_2a_4^6a_6 + 96a_2^2a_4^4a_6^2 - 256a_2^3a_4^2a_6^3 + 256a_2^4a_6^4 - 32a_4^5a_6^2 \\
-        &+ 256a_2a_4^3a_6^3 - 512a_2^2a_4a_6^4 - 256a_4^2a_6^4 + 1024a_2a_6^5 := F
-    \end{align*}
-    Note that $F$ factors as
-    \begin{align*}
-        F =& (-a_4^2 + 4a_2a_6) \cdot \\
-        &(\underbrace{-a_4^6 + 12a_2a_4^4a_6 - 48a_2^2a_4^2a_6^2 + 64a_2^3a_6^3 + 32a_4^3a_6^2 - 128a_2a_4a_6^3 + 256a_6^4}_{=: G})
-    \end{align*}
-    \paragraph{If $4a_2a_6 = a_4^2$} As $\alpha_2 = \frac 1 4 a_4^2/a_6 - a_2$ it follows that $\alpha_2 = 0$, a contradiction ($\alpha_2 = 0$ would imply $[2]P = P$ or $[2]P = -P$, both contradicting the assumption that $\mathrm{ord}(P) = 5$).
-    \paragraph{If $G = 0$} Have for any prime $p \divides a_4$
-\end{proof}
-\begin{prop}
-    Let $E: y^2 + (v + 1) x y + v y = x^3 + v x^2$ be an Elliptic Curve and $P = (x_1, y_1), Q = (x_2, y_2) \in E$ with $x_1 \neq x_2$.
+\begin{lemma}
+    \label{prop:relation_y_uv}
+    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
+    Suppose that $E$ has a nontrivial 5-torsion point $P = (\alpha_1, \beta_1) \in E(k)$.
+    wlog $\alpha_1 = 0$.
+    Let further $(\alpha_2, \beta_2) = [2](0, \beta)$.
     Then
     \begin{equation*}
-        x(P + Q) = -x_1 - x_2 + m^2 + m(v + 1) - v
+        \alpha_2^3 = -4\beta\beta_2
     \end{equation*}
-    where
-    \begin{equation*}
-        m = \frac {y_2 - y_1} {x_2 - x_1}
-    \end{equation*}
-\end{prop}
+\end{lemma}
+\begin{proof}
+    Consider the following SAGE script:
+    \lstinputlisting[language = python]{./3i_algebra.sage}
+    The output shows that $\alpha_2^3 = -4 \beta \beta_2$ already follows from the facts
+    \begin{align*}
+        &(0, \beta) \in E, \\
+        &(\alpha_2, \beta_2) \in E, \\
+        &[2](0, \beta) = (\alpha_2, \beta_2), \\
+        &[2](\alpha_2, \beta_2) = (0, -\beta)
+    \end{align*}
+    which hold by assumption that $(0, \beta)$ has order $5$.
+    The claim follows.
+\end{proof}
 \begin{prop}
@@
 \begin{prop}[3(i)]
-    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$ and $P = (\alpha_1, \beta_1) \in E(k)$ a (nontrivial) 5-torsion point.
+    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
+    Suppose that $E$ has a nontrivial 5-torsion point $P = (\alpha_1, \beta_1) \in E(k)$.
     wlog $\alpha_1 = 0$.
@@
     \end{equation*}
-    where
+    with
     \begin{equation*}
-        v = \frac {\beta_2} {\beta}, \quad t = -\frac {\beta_2} {2\beta}, \quad u^3 = \frac {\beta_2} {2\beta^2}, \quad s = \frac {u} {\alpha_2} ( \beta_2 + \beta )
+        v = \frac {\beta_2} {\beta}, \quad t = -\frac {\beta_2} {2\beta}, \quad u = -\frac {\alpha_2} {2\beta}, \quad s = \frac {u} {\alpha_2} ( \beta_2 + \beta )
     \end{equation*}
@@
     \end{align*}
-    Assume for now that $u^2 \alpha_2 = -v$.
-    Under $\psi$, we see that
+    By Lemma~\ref{prop:relation_y_uv} we have that $\alpha_2^3 = -4\beta\beta_2$ and so
     \begin{equation*}
-        (0, \beta) \mapsto (0, u^3 \beta + t) = \left( 0, \frac {\beta} {2\beta_2} - \frac {\beta} {2\beta_2} \right) = (0, 0) \in E'
+        u^3 = \left( -\frac {\alpha_2} {2\beta} \right)^3 = -\frac {\alpha_2^3} {8\beta^3} = \frac {4\beta\beta_2} {8\beta^3} = \frac {\beta_2} {2\beta^2}
+    \end{equation*}
+
+    Under $\psi$, we now see that
+    \begin{equation*}
+        (0, \ \beta) \mapsto (0, u^3 \beta + t) = \left( 0, \ \frac {\beta} {2\beta_2} - \frac {\beta} {2\beta_2} \right) = (0, 0) \in E'
     \end{equation*}
@@
     \begin{align*}
-        (\alpha_2, \beta_2) \mapsto (u^2 \alpha_2, u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(-v, \frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
-        &= \left( -v, \frac {\beta_2^2} {\beta^2} \right) = (-v, v^2) \in E'
+        (\alpha_2, \ \beta_2) \mapsto (u^2 \alpha_2, \ u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(\frac {\alpha_2^3} {4\beta^2}, \ \frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
+        &= \left( -\frac {\beta_2} {\beta}, \ \frac {\beta_2^2} {\beta^2} \right) = (-v, \ v^2) \in E'
     \end{align*}
@@
     \begin{align*}
-        (\alpha_2, \beta_2) \mapsto (u^2 \alpha_2, -u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(-v, -\frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
-        &= (-v, 0) \in E'
+        (\alpha_2, \beta_2) \mapsto (u^2 \alpha_2, \ -u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(\frac {\alpha_2^3} {4\beta^2}, \ -\frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
+        &= ( -\frac {\beta_2} {\beta}, \ 0) = (-v, \ 0) \in E'
     \end{align*}
@@
     \begin{align*}
-        (0, -\beta) \mapsto (0, -u^3 \beta + t) = \left( 0, -\frac {\beta_2} {2\beta} - \frac {\beta_2} {2\beta} \right) = (0, -v) \in E'
+        (0, \ -\beta) \mapsto (0, -u^3 \beta + t) = \left( 0, \ -\frac {\beta_2} {2\beta} - \frac {\beta_2} {2\beta} \right) = (0, \ -v) \in E'
     \end{align*}
@@
     Hence we have $\#(E' \cap E'') \geq 5$ and by the previous proposition we see that $E' = E''$.
-
-    So it is left to show that $\beta/(2\beta^2)$ has a third root in $\Q$ and that $u^2 \alpha_2 = -v$.
 \end{proof}

### 2022-03-16 Elliptic Curves/submission.tex
Continued with 3ii

@@
 \end{proof}
-\begin{prop}
+\begin{lemma}
     Let
@@
     then $E = E'$.
-\end{prop}
+\end{lemma}
 \begin{proof}
@@
 \end{proof}
-\begin{prop}[3(i)]
+\begin{prop}
+    \label{prop:characterization_5_torsion}
     Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
-    Suppose that $E$ has a nontrivial 5-torsion point $P = (\alpha_1, \beta_1) \in E(k)$.
-    wlog $\alpha_1 = 0$.
-    Let further $[2]P = (\alpha_2, \beta_2)$ and note that $\alpha_1 = 0 \neq \alpha_2$.
+    Suppose that $E$ has a nontrivial 5-torsion point $P = (0, \beta) \in E(k)$.
+    Let further $[2]P = (\alpha_2, \beta_2)$ and note that $0 \neq \alpha_2$.
     Then there exists a birational equivalence $E \to E'$ where $E': y^2 + (1 + v) x y + v y = x^3 + v x^2$ given by
@@
 \end{proof}
+\begin{corollary}
+    Let $E$ be an Elliptic Curve defined over $\Q$.
+    Then $E(\Q)$ has a nontrivial 5-torsion point if and only if $E$ is isomorphic (over $\Q$) to an Elliptic Curve given by an equation of the form
+    \begin{equation*}
+        y^2 + (v + 1)x y + v y = x^3 + v x^2
+    \end{equation*}
+\end{corollary}
+In the lecture, it was mentioned that a theorem of Mazur states that the torsion group of an Elliptic Curve $E$ defined over $\Q$ has one of the following forms
+\begin{itemize}
+    \item $\Z/n\Z$ for $n \in \{ 1, ..., 10, 12 \}$
+    \item $\Z/n\Z \oplus \Z/2\Z$ for $n \in \{ 2, 4, 6, 8 \}$
+\end{itemize}
+Hence, we are quite limited for $N$ a similar idea can work.
+First, note that the case $N = 2$ is easy.
+\begin{prop}
+    Let $E$ be an Elliptic Curve defined over $\Q$.
+    Then $E(\Q)$ has a nontrivial 2-torsion point if and only if $E$ is isomorphic (over $\Q$) to an Elliptic Curve given by an equation of the form
+    \begin{equation*}
+        y^2 = x^3 + a_2 x^2 + a_4 x
+    \end{equation*}
+\end{prop}
+\begin{proof}
+    Assume $E: y^2 = x^3 + a_2 x^2 + a_4 x$ is an Elliptic Curve.
+    Then clearly $(0, 0) \in E(\Q)$ and $(0, 0) = -(0, 0)$, so $(0, 0)$ is nontrival 2-torsion point.
+    Hence, there is a nontrivial 2-torsion point in $E'(\Q)$ for all Elliptic Curves $E'$ that are isomorphic (over $\Q$) to $E$.
+
+    Conversely, let $E$ be an Elliptic Curve with a nontrivial 2-torsion point in $E(\Q)$.
+    Note that $E$ is isomorphic to an Elliptic Curve 
+    \begin{equation*}
+        E': y^2 = x^3 + a_2 x^2 + a_4 x + a_6
+    \end{equation*}
+    as this holds for every Elliptic Curve.
+    Now let $(\alpha, \beta) \in E'(\Q)$ be a nontrival 2-torsion point.
+    Thus $-(\alpha, \beta) = (\alpha, \beta)$, so $\beta = 0$ and $\alpha^3 + a_2 \alpha^2 + a_4 \alpha + a_6 = 0$.
+    Now consider the isomorphism
+    \begin{equation*}
+        E' \to E'', \quad (x, y) \mapsto (x - \alpha, y)
+    \end{equation*}
+    where
+    \begin{equation*}
+        E'': y^2 = x^3 + (3\alpha + a_2) x^2 + (3\alpha^2 + 2\alpha a_2 + a_4)x + \underbrace{\alpha^3 + \alpha^2a_2 + \alpha a_4 + a_6}_{= 0}
+    \end{equation*}
+    Observe that $E''$ is of the described form, and the claim follows. 
+\end{proof}
+The case $N = 3$ is slightly more interesting.
+For this, we first look at some basic transformations we can do to Weierstraß equations.
+\begin{prop}
+    \label{prop:weierstrass_transformations}
+    Let $E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
+    There are three nice types of transformations
+    \begin{description}
+        \item[Translation] Let $P = (s, t) \in E(k)$ be a point. Then the isomorphism
+        \begin{equation*}
+            E \to E', \quad (x, y) \mapsto (x - s, y - t)
+        \end{equation*}
+        maps $P$ to $(0, 0)$ and the curve $E$ to an Elliptic Curve
+        \begin{equation*}
+            E': y^2 + a_1 x y + (a_3 + 2t + a_1 s) y = x^3 + (a_2 + 3 s) x^2 + (a_4 - 3 s^2 + 2 a_2 s - a_1 t) x
+        \end{equation*}
+        This is very useful to clear $a_6$ and continue working with the point $(0, 0)$.
+        \item[Shearing] Let $r \in k$. Then the isomorphism
+        \begin{equation*}
+            E \to E', \quad (x, y) \mapsto (x, y - r x)
+        \end{equation*}
+        preserves $(0, 0)$ and maps $E$ to an Elliptic Curve
+        \begin{equation*}
+            E': y^2 + (a_1 + 2r) x y + a_3 y = x^3 + (a_2 + r^2 - a_1 r) x^2 + (a_4 - r a_3) x + a_6
+        \end{equation*}
+        This is very useful, as it does not change $a_3$ and $a_6$.
+        \item[Scaling] Let $u \in k^*$. Then the isomorphism
+        \begin{equation*}
+            E \to E', \quad (x, y) \mapsto (u^2 x, y^3 y)
+        \end{equation*}
+        preserves $(0, 0)$ and maps $E$ to an Elliptic Curve
+        \begin{equation*}
+            E': y^2 + \frac {a_1} u x y + \frac {a_3} {u^3} = x^3 + \frac {a_2} {u^2} x^2 + \frac {a_4} {u^4} x + \frac {a_6} {u^6}
+        \end{equation*}
+        This is very useful, as it does not change which of the $a_1, ..., a_4, a_6$ are zero.
+    \end{description}
+\end{prop}
+Now we can find a nice form for Elliptic Curves with a (nontrivial) 3-torsion point by the following step:
+\begin{itemize}
+    \item Apply a translation to get an isomorphic curve whose (nontrivial) 3-torsion point is $(0, 0)$.
+    \item Observe that $(0, 0)$ being a 3-torsion point is equivalent to the fact that the tangent at $E$ through $(0, 0)$ meets $E$ at $(0, 0)$ with multiplicity three.
+    \item Apply clever shearing and scaling to get a nice form. Note that this does not destroy the fact $a_6 = 0$.
+\end{itemize}
+Now we get
+\begin{prop}
+    Let $E$ be an Elliptic Curve defined over $\Q$.
+    Then $E(\Q)$ has a nontrivial 3-torsion point if and only if $E$ is isomorphic (over $\Q$) to an Elliptic Curve given by an equation of the form
+    \begin{equation*}
+        y^2 + x y + v y = x^3
+    \end{equation*}
+\end{prop}
+\begin{proof}
+    By Proposition~\ref{prop:weierstrass_transformations} we can assume wlog that
+    \begin{equation*}
+        E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2 + a_4 x
+    \end{equation*}
+    and $(0, 0) \in E(\Q)$ is a nontrivial 3-torsion point.
+    Now a shearing with $r = a_4 / a_3$ transforms $E$ into an Elliptic Curve
+    \begin{equation*}
+        E': y^2 + a'_1 x y + a'_3 y = x^3 + a'_2 x^2
+    \end{equation*}
+    Observe that $(0, 0)$ is still a nontrivial 3-torsion point of $E'(\Q)$.
+
+    Now note that the tangent at $(0, 0)$ has slope $m = a'_4/a'_3 = 0$.
+    Hence, since $-[2](0, 0) = (0, 0)$ is the third point of intersection of $E'$ and the tangent, we see that the tangent meets $E'$ at $(0, 0)$ with multiplicity three.
+    Thus
+    \begin{equation*}
+        x^3 + a'_2 x^2 
+    \end{equation*}
+    must already be $x^3$ and thus have $a'_2 = 0$.
+    Finally, apply a scaling with $u = a'_1$ (note that $a'_1 \neq 0$, otherwise the curve would be singular) and find that $E$ is isomorphic to the curve
+    \begin{equation*}
+        E'': y^2 + x y + v y = x^3
+    \end{equation*}
+    where $v = a'_3 / (a'_1)^3$.
+
+    Conversely, assume that $E$ is isomorphic to an Elliptic Curve of the above form, so wlog
+    \begin{equation*}
+        E: y^2 + x y + v y = x^3
+    \end{equation*}
+    We show that $(0, 0) \in E(\Q)$ has order 3.
+    The tangent at $(0, 0)$ has slope $0$, so is given by the line $y = 0$.
+    Plugging this in yields $x^3 = 0$, and so the third point of intersection with $E$ is $(0, 0)$.
+
+    Now consider the line through $\O$ and $(0, 0)$, which is given by $x = 0$.
+    Plugging this in yields $y^2 + v y = 0$ and so the third point of intersection is $(0, -v)$.
+    Now note that $(0, 0)$, $(0, -v)$ and $\O$ are colinear, so $(0, 0) + (0, -v) + \O = \O$, hence $(0, 0) = -[2](0, 0)$ has order 3.
+\end{proof}
 \end{document}

### 2022-03-16 Elliptic Curves/submission.tex
Did 4i

@@
 
-\newtheorem{prop}{Proposition}
-\newtheorem{theorem}[prop]{Theorem}
-\newtheorem{lemma}[prop]{Lemma}
-\newtheorem{corollary}[prop]{Corollary}
+\theoremstyle{definition}
 
-\theoremstyle{definition}
-\newtheorem{problem}[prop]{Problem}
-\newtheorem{alg}[prop]{Algorithm}
-\newtheorem{definition}[prop]{Definition}
-\newtheorem{example}[prop]{Example}
-\newtheorem{remark}[prop]{Remark}
+\newtheorem{prop}[subsection]{Proposition}
+\newtheorem{theorem}[subsection]{Theorem}
+\newtheorem{lemma}[subsection]{Lemma}
+\newtheorem{corollary}[subsection]{Corollary}
+
+\newtheorem{problem}[subsection]{Problem}
+\newtheorem{alg}[subsection]{Algorithm}
+\newtheorem{definition}[subsection]{Definition}
+\newtheorem{example}[subsection]{Example}
+\newtheorem{remark}[subsection]{Remark}
 
@@
 First, it is convenient to have a closed formula for the $x$-coordinate of $[2]P$ for a point $P$ on an Elliptic Curve.
-\begin{prop}
+\begin{prop}[Duplication Formula]
     \label{prop:duplication_formula}
@@
 
-\section*{Question 3}
+\section{Question 3}
 \begin{lemma}
@@
 \end{proof}
-\begin{corollary}
+\begin{corollary}[3(i)]
     Let $E$ be an Elliptic Curve defined over $\Q$.
@@
 \end{corollary}
+\begin{proof}
+    Note that $E$ is isomorphic (over $\Q$) to an Elliptic Curve defined by a Weierstraß equation, so assume wlog
+    \begin{equation*}
+        E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6
+    \end{equation*}
+    Now let $P = (\alpha, \beta)$ be a nontrivial 5-torsion point.
+    Then $E$ is isomorphic via $(x, y) \mapsto (x - \alpha, \beta)$ to an Elliptic Curve
+    \begin{equation*}
+        E': y^2 = x^3 + a'_2 x^2 + a'_4 x
+    \end{equation*}
+    and $(0, \beta)$ is a nontrivial 5-torsion point of $E'$.
+    The claim follows now by Proposition~\ref{prop:characterization_5_torsion}.
+
+    Conversely, assume that
+    \begin{equation*}
+        E: y^2 + (v + 1) x y + v y = x^3 + v x^2
+    \end{equation*}
+    For example by the duplication formula~\ref{prop:duplication_formula} find that
+    \begin{equation*}
+        [2](0, 0) = (-v, v^2), \quad [2](-v, v^2) = (0, -v)
+    \end{equation*}
+    and thus $[4](0, 0) + (0, 0) = \O$, hence $(0, 0)$ has order 5.
+\end{proof}
 In the lecture, it was mentioned that a theorem of Mazur states that the torsion group of an Elliptic Curve $E$ defined over $\Q$ has one of the following forms
@@
 First, note that the case $N = 2$ is easy.
-\begin{prop}
+\begin{prop}[3(ii)]
     Let $E$ be an Elliptic Curve defined over $\Q$.
@@
 \end{proof}
+
+\section{Question 4}
+
+\begin{example}
+    The Elliptic Curve $E: y^2 = x(x + 6 + 1)$ has rank $0$.
+\end{example}
+\begin{proof}
+    As in the lecture, consider
+    \begin{align*}
+        &E': y^2 = x(x^2 - 12x + 32) \\
+        &\phi: E \to E', \quad (u, v) \mapsto \left( \frac {y^2} {x^2}, \ y \frac {x^2 - 1} {x^2} \right) \\
+        &\hat{\phi}: E' \to E, \quad (u, v) \mapsto \left( \frac {y^2} {4x^2}, \ y \frac {x^2 - 1} {8x^2} \right) \\
+        &q: E'(\Q)/\phi(E(\Q)) \to \Q^*/S, \quad \overline{(u, v)} \mapsto \begin{cases}
+            \overline{u} & \text{if $u \neq 0$} \\
+            \overline{32} & \text{if $u = 0$}
+        \end{cases} \\
+        &\hat{q}: E(\Q)/\phi(E'(\Q)) \to \Q^*/S, \quad \overline{(u, v)} \mapsto \begin{cases}
+            \overline{u} & \text{if $u \neq 0$} \\
+            \overline{1} & \text{if $u = 0$}
+        \end{cases}
+    \end{align*}
+    \paragraph{Find $E'(\Q)/\phi(E(\Q))$} As in the lecture, consider $r \divides 32$ square-free, i.e. $r \in \{ \pm 1, \pm 2 \}$.
+
+    For $r = 2$, have that $(l, m, n) = (2, 1, 0)$ solves
+    \begin{equation*}
+        2l^4 - 12l^2m^2 + 16m^4 = n^2
+    \end{equation*}
+    and indeed we find $(8, 0) \in E'(\Q)$.
+
+    For $r = -1$, note that
+    \begin{equation*}
+        -l^4 - 12l^2m^2 - 32m^4 = n^2
+    \end{equation*}
+    has no nontrivial solutions in $\Q$, as the left-hand side is always $\leq 0$ and the right-hand side is $\geq 0$.
+
+    Since $-2 = -1 \cdot 2$, we see that $\im(q) = \langle 2 \rangle$ and $E'(\Q)/\phi(E(\Q)) = \langle (8, 0) \rangle$.
+
+    \paragraph{Find $E(\Q)/\hat{\phi}(E'(\Q))$} Consider $r \divides 1$, i.e. $r \in \{ \pm 1 \}$.
+
+    For $r = -1$, have that $(l, m, n) = (1, 1, 2)$ solves
+    \begin{equation*}
+        -l^4 + 6l^2m^2 - m^2 = n^2
+    \end{equation*}
+    and indeed find $(-1, 2) \in E(\Q)$.
+
+    Thus find $\im(\hat{q}) = \langle -1 \rangle$ and $E(\Q)/\hat{\phi}(E'(\Q)) = \langle (-1, 2) \rangle$.
+
+    \paragraph{Find the rank of $E$} By the above two steps, we see that
+    \begin{equation*}
+        E(\Q)/[2]E(\Q) = \langle (-1, 2), \hat{\phi}((8, 0)) \rangle = \langle (-1, 2), (0, 0) \rangle
+    \end{equation*}
+    Now observe that $[2](-1, 2) = (0, 0)$ and $[2](0, 0) = \O$.
+    Hence $E(\Q) = E_{\mathrm{tors}}(\Q)$ and the rank is 0 as claimed.
+\end{proof}
+
 \end{document}

### 2022-03-18 Elliptic Curves/submission.tex
Solved 4ii

@@
 
-\begin{example}
+Let $S = \{ x^2 \ | \ x \in \Q^2 \}$.
+\begin{example}[4(i)]
     The Elliptic Curve $E: y^2 = x(x + 6 + 1)$ has rank $0$.
@@
 \end{proof}
+To find an example with rank two, it seems like a good way to take a curve with many rational points.
+Further requiring those points to be non-integral increases our chance, as that way, they cannot be torsion points.
+
+For rank one, this is perfectly rigorous: If we find a curve with integral coefficients and at least one non-integral point, its rank must be $\geq 1$.
+Such a curve is easy to find by guessing a point and using linear algebra.
+Furthermore, if we have two points $P, Q$ with distinct $x$-coordinates ($\neq 1$), then we already see that $\overline{P} \neq \overline{Q} \in E(\Q)/\hat{q}(E'(\Q))$ and since both are non-torsion (they have non-integral coordinates), it follows that the rank is at least 2.
+\begin{example}
+    Guess the points
+    \begin{equation*}
+        P_1 = \left(-1, \frac 1 2\right), \quad P_2 = \left(-2, \frac 1 2\right)
+    \end{equation*}
+    and consider an Elliptic Curve given by
+    \begin{equation*}
+        y^2 = x^3 + a_2 x^2 + a_4 x
+    \end{equation*}
+    If $P_1, P_2, P_3 \in E$, we must have
+    \begin{align*}
+        &-1 + a_2 - a_4 = \frac 1 4 \\
+        &-8 + 4a_2 - 2a_4 = \frac 1 4
+    \end{align*}
+    This has the solution $(a_2, a_4) = (23/8, 13/8)$.
+    Hence, we consider the curve given by
+    \begin{equation*}
+        y^2 = x^3 + \frac {23} 8 x^2 + \frac {13/8} x
+    \end{equation*}
+    Putting it into standard form yields
+    \begin{equation*}
+        E: y^2 = x(x^2 + 46 x + 104)
+    \end{equation*}
+    Now we would like to compute the rank of this curve, however the standard method fails here.
+    The reason is that some of the equations, like
+    \begin{equation*}
+        13 l^4 + 65 l^2 m^2 + 8 m^4 = n^2
+    \end{equation*}
+    (resulting from $r = 13 \divides 104$) seem to have no integer solutions, but seem have one modulo any prime.
+
+    Note however that we find
+    \begin{equation*}
+        -l^4 + 46 l^2 m^2 - 104 m^4 = n^2 \quad \text{has solution $(l, m, n) = (2, 1, 8)$}
+    \end{equation*}
+    and
+    \begin{equation*}
+        104 l^4 + 46 l^2 m^2 + 1 m^4 = n^2 \quad \text{has solution $(l, m, n) = (0, 1, 1)$}
+    \end{equation*}
+    and
+    \begin{equation*}
+        2 l^4 + 46 l^2 m^2 + 52 m^4 = n^2 \quad \text{has solution $(l, m, n) = (1, 1, 10)$}
+    \end{equation*}
+    corresponding to the points $P_1, P_2$ and $(0, 0)$.
+
+    So we find that $(\Z/2\Z)^3 \hookrightarrow E(\Q)/[2]E(\Q)$ and since $x^2 + 46 x + 104$ has no rational roots (the discriminant $1700$ is not a perfect square), observe that $E_{\mathrm{tors}}(\Q) / [2]E(\Q) \cong \Z/2\Z$.
+    Thus
+    \begin{equation*}
+        (\Z/2\Z)^2 \hookrightarrow E_{\mathrm{torsion-free}}(\Q)/[2]E(\Q)
+    \end{equation*}
+    and $E$ has rank at least 2.
+\end{example}
+A lot of trying around shows that most curves that are generated in a ``clever'' way to satisfy nice properties (like high rank, or only few square-free $r \divides b$ resp.
+$r \divides b_1$) cause problems when computing the rank, due to resulting in hard-to-solve equations as above.
+So it would be good to find a method that generates ``nice'' curves, i.e. curves where each of the equations
+\begin{equation*}
+    r l^4 + a l^2 m^2 + \frac b r m^4 = n^4 \quad \text{resp} \quad r l^4 + a_1 l^2 m^2 + \frac {b_1} r m^4 = n^4
+\end{equation*}
+obviously has or hasn't a nontrivial solution.
+At the moment, I fail to see any elegant method to generate ``nice'' curves with desired properties.
+So lets fall back to brute force, which works quite well here as this condition is very easy to test via a computer.
+\begin{example}[4(ii)]
+    Consider the curve
+    \begin{equation*}
+        E: y^2 = x(x^2 + 47 x + 30)
+    \end{equation*}
+    Clearly $30 = 2 \cdot 3 \cdot 5$ has at least 3 different prime factors.
+    We want to compute the rank of $E$.
+    As always, have
+    \begin{equation*}
+        E': y^2 = x(x^2 - 92 x + 2089)
+    \end{equation*}
+
+    \paragraph{Find $E'(\Q)/\phi(E(\Q))$} Have $b_1 = 2089$ is prime, so consider $r \in \{ \pm 1, \pm 2098 \}$.
+    First note that for $r < 0$, the equation
+    \begin{equation*}
+        r l^4 - 92 l^2 m^2 + \frac {2089} r m^4 = n^2
+    \end{equation*}
+    has no real nontrivial solutions, as the left-hand side is $< 0$ and the right-hand side is $\geq 0$.
+    Hence, it is left to consider $r = 1$ and $r = 2089$.
+    Notice that the equations
+    \begin{equation*}
+        l^4 - 92 l^2 m^2 + 2089 m^4 = n^2 \quad \text{and} \quad 2089 l^4 - 92 l^2 m^2 + 1 m^4 = n^2
+    \end{equation*}
+    are symmetric w.r.t. swapping $l, m$.
+
+    Hence we only have the obvious solutions $(l, m, n) = (1, 0, 1)$ and $(l, m, n) = (0, 1, 1)$ that give the points $(0, 0)$ and $\O$.
+    So $E'(\Q)/\phi(E(\Q)) = \langle (0, 0) \rangle$.
+
+    \paragraph{Find $E(\Q)/\hat{\phi}(E'(\Q))$} Have $b = 30 = 2 \cdot 3 \cdot 5$, so consider
+    \begin{equation*}
+        r \in \{ \pm 1, \pm 2, \pm 3, \pm 5, \pm 6, \pm 10, \pm 15 \}
+    \end{equation*}
+
+    The equation
+    \begin{equation*}
+        -l^4 + 47 l^2 m^2 - 30 m^4 = n^2
+    \end{equation*}
+    has the solution $(l, m, n) = (1, 1, 4)$ which gives a point $(-1, 4) \in E(\Q)$.
+
+    The equation
+    \begin{equation*}
+        2l^4 + 47 l^2 m^2 + 15 m^4 = n^2
+    \end{equation*}
+    has the solution $(l, m, n) = (1, 1, 8)$ which gives a point $(2, 8) \in E(\Q)$.
+
+    The equation
+    \begin{equation*}
+        3l^4 + 47 l^2 m^2 + 10 m^4 = n^2
+    \end{equation*}
+    has the solution $(l, m, n) = (3, 1, 26)$ which gives a point $(27, 234) \in E(\Q)$.
+
+    The equation
+    \begin{equation*}
+        5l^4 + 47 l^2 m^2 + 6m^4 = n^2
+    \end{equation*}
+    has the solution $(l, m, n) = (1, 2, 17)$ which gives a point $(\frac 5 4, \frac {85} 8)$.
+
+    Since $\im(\hat{q})$ is a group and $-1, 2, 3, 5$ clearly generate
+    \begin{equation*}
+        \{ \pm 1, \pm 2, \pm 3, \pm 5, \pm 6, \pm 10, \pm 15 \} \subseteq \Q^*/S
+    \end{equation*}
+    we already see that $\im(\hat{q}) = \langle -1, 2, 3, 5 \rangle$.
+
+    \paragraph{Find the rank of $E$} Combining the above, we see that
+    \begin{equation*}
+        E(\Q)/[2]E(\Q) = \langle (-1, 4), (2, 8), (27, 234), (\frac 5 4, \frac {85} 8) \rangle
+    \end{equation*}
+    since $\hat{\phi}((0, 0)) = \O$.
+    This further shows that $E(\Q)/[2]E(\Q) \cong (\Z/2\Z)^4$.
+    Note that $x^2 + 47 x + 30$ has no rational root, so $(0, 0)$ is the only nontrivial 2-torsion points and thus
+    \begin{equation*}
+        E_{\mathrm{tors}}(\Q)/[2]E(\Q) \cong \Z/2\Z
+    \end{equation*}
+    Hence we see that the rank of $E$ is $4 - 1 = 3 \geq 2$.
+\end{example}
+Note that the computer also found other, similarly special curves, given by equations\footnote{I should have guessed that there is a solution involving 42.}
+\begin{align*}
+    E_1: y^2 = x(x^2 + 59 x^2 + 42) \\
+    E_2: y^2 = x(x^2 + 83 x^2 + 78)
+\end{align*}
 

### 2022-03-18 Elliptic Curves/3ii_computations.py

@@ -1,0 +1,63 @@
+from math import sqrt, gcd
+
+def eval(r, a, b, l, m):
+    return r * l**4 + a * l**2 * m**2 + b/r * m**4
+
+def is_square(n):
+    if n < 0:
+        return False
+    return int(sqrt(n))**2 == n
+
+def can_prove_has_sol(r, a, b):
+    for l in range(50):
+        for m in range(50):
+            if (l != 0 or m != 0) and gcd(l, m) == 1:
+                if is_square(eval(r, a, b, l, m)):
+                    return True
+    return False
+
+def can_prove_has_no_sol(r, a, b):
+    for q in [90, 82, 110]:
+        squares = { x**2 % q for x in range(q) }
+        if len([(l, m) for l in range(q) for m in range(q) if eval(r, a, b, l, m)%q in squares]) == 1:
+            return True
+    return False
+
+def is_nice(r, a, b):
+    return (r < 0 and a <= 0 and b >= 0) or can_prove_has_no_sol(r, a, b) or can_prove_has_sol(r, a, b)
+
+def squarefree_factors(b):
+    pos_factors = [n for n in range(2, b + 1) if b%n == 0]
+    pos_sqrfree_factors = [n for n in pos_factors if len([m for m in pos_factors if n % m**2 == 0]) == 0]
+    return [1, -1, *pos_sqrfree_factors, *[-n for n in pos_sqrfree_factors]]
+
+def is_curve_nice(a, b):
+    a1 = -2 * a
+    b1 = a**2 - 4 * b
+    for r in squarefree_factors(b):
+        if not is_nice(r, a, b):
+            return False
+    for r in squarefree_factors(b1):
+        if not is_nice(r, a1, b1):
+            return False
+    return True
+
+exit()
+
+for a in range(60):
+    for b in range(60):
+        if a**2 - 4 * b != 0:
+            if is_curve_nice(a, b) and len(squarefree_factors(b)) >= 14:
+                print(a, b, len(squarefree_factors(b)))
+
+for a in range(60):
+    for b in range(60, 100):
+        if a**2 - 4 * b != 0:
+            if is_curve_nice(a, b) and len(squarefree_factors(b)) >= 14:
+                print(a, b, len(squarefree_factors(b)))
+
+for a in range(60, 100):
+    for b in range(100):
+        if a**2 - 4 * b != 0:
+            if is_curve_nice(a, b) and len(squarefree_factors(b)) >= 14:
+                print(a, b, len(squarefree_factors(b)))

### 2022-03-18 Elliptic Curves/submission.tex
Solve 4iii

@@
 
-Let $S = \{ x^2 \ | \ x \in \Q^2 \}$.
+Let $S = \{ x^2 \ | \ x \in \Q^* \}$.
 \begin{example}[4(i)]
-    The Elliptic Curve $E: y^2 = x(x + 6 + 1)$ has rank $0$.
+    \label{ex:4i}
+    The Elliptic Curve $E: y^2 = x(x + 6x + 1)$ has rank $0$.
 \end{example}
@@
 
-    \paragraph{Find $E(\Q)/\hat{\phi}(E'(\Q))$} Consider $r \divides 1$, i.e. $r \in \{ \pm 1 \}$.
+    \paragraph{Find $E(\Q)/\hat{\phi}(E'(\Q))$} Consider $r \divides 1$ square-free, i.e. $r \in \{ \pm 1 \}$.
 
@@
     \begin{equation*}
-        -l^4 + 6l^2m^2 - m^2 = n^2
+        -l^4 + 6l^2m^2 - m^4 = n^2
     \end{equation*}
@@
 
-For rank one, this is perfectly rigorous: If we find a curve with integral coefficients and at least one non-integral point, its rank must be $\geq 1$.
+For rank one, this is very easy: If we find a curve with integral coefficients and at least one non-integral point, its rank must be $\geq 1$.
 Such a curve is easy to find by guessing a point and using linear algebra.
-Furthermore, if we have two points $P, Q$ with distinct $x$-coordinates ($\neq 1$), then we already see that $\overline{P} \neq \overline{Q} \in E(\Q)/\hat{q}(E'(\Q))$ and since both are non-torsion (they have non-integral coordinates), it follows that the rank is at least 2.
+Furthermore, if we have two points $P, Q$ whose $x$-coordinates are linearly independent in $\Q^*/S$ (as $\Z/2\Z$-module), then we already see that $\overline{P} \neq \overline{Q} \in E(\Q)/\hat{q}(E'(\Q))$ and since both are non-torsion (they have non-integral coordinates), it follows that the rank is at least 2.
 \begin{example}
@@
     \begin{equation*}
-        y^2 = x^3 + \frac {23} 8 x^2 + \frac {13/8} x
+        y^2 = x^3 + \frac {23} 8 x^2 + \frac {13} 8 x
     \end{equation*}
@@
 \begin{example}[4(ii)]
+    \label{ex:special_curve}
     Consider the curve
@@
     has no real nontrivial solutions, as the left-hand side is $< 0$ and the right-hand side is $\geq 0$.
-    Hence, it is left to consider $r = 1$ and $r = 2089$.
+    Hence, it is left to consider $r = 2089$.
     Notice that the equations
     \begin{equation*}
-        l^4 - 92 l^2 m^2 + 2089 m^4 = n^2 \quad \text{and} \quad 2089 l^4 - 92 l^2 m^2 + 1 m^4 = n^2
-    \end{equation*}
-    are symmetric w.r.t. swapping $l, m$.
-
-    Hence we only have the obvious solutions $(l, m, n) = (1, 0, 1)$ and $(l, m, n) = (0, 1, 1)$ that give the points $(0, 0)$ and $\O$.
-    So $E'(\Q)/\phi(E(\Q)) = \langle (0, 0) \rangle$.
+        2089 l^4 - 92 l^2 m^2 + m^4 = n^2
+    \end{equation*}
+    has the solution $(l, m, n) = (0, 1, 1)$ and so $E'(\Q)/\phi(E(\Q)) = \langle (0, 0) \rangle$.
 
@@
     \begin{equation*}
-        r \in \{ \pm 1, \pm 2, \pm 3, \pm 5, \pm 6, \pm 10, \pm 15 \}
+        r \in \{ \pm 1, \pm 2, \pm 3, \pm 5, \pm 6, \pm 10, \pm 15, \pm 30 \}
     \end{equation*}
@@
     \begin{equation*}
-        \{ \pm 1, \pm 2, \pm 3, \pm 5, \pm 6, \pm 10, \pm 15 \} \subseteq \Q^*/S
+        \{ \pm 1, \pm 2, \pm 3, \pm 5, \pm 6, \pm 10, \pm 15, \pm 30 \} \subseteq \Q^*/S
     \end{equation*}
@@
     \begin{equation*}
-        E(\Q)/[2]E(\Q) = \langle (-1, 4), (2, 8), (27, 234), (\frac 5 4, \frac {85} 8) \rangle
+        E(\Q)/[2]E(\Q) = \langle (-1, 4), (2, 8), (27, 234), \left(\frac 5 4, \frac {85} 8\right) \rangle
     \end{equation*}
@@
 
+\begin{prop}[4(iii)]
+    \label{prop:rank_bound}
+    Let $E: y^2 = x(x^2 + a x + b)$ be an Elliptic Curve such that $b(a^2 - 4b)$ has exactly $k$ prime factors.
+    Then $\mathrm{rank}(E) \leq 2k$.
+    Furthermore, we have
+    \begin{itemize}
+        \item If $a \leq 0, b \geq 0$, then $\mathrm{rank}(E) \leq 2k - 1$
+        \item If $a \perp b$ are coprime, then $\mathrm{rank}(E) \leq k$
+        \item If $a \perp b$ and $a \leq 0, b \geq 0$, then $\mathrm{rank}(E) \leq k - 1$
+    \end{itemize}
+    Note that if one of the additional conditions is fulfilled for $a_1, b_1$, then we get the corresponding bound for $\mathrm{rank}(E') = \mathrm{rank}(E)$ (isogenous curves have the same rank, as isogenies have finite kernel).
+\end{prop}
+\begin{proof}
+    Use $a_1, b_1, E', \phi, \hat{\phi}, q, \hat{q}$ as in the lecture.
+    Let $l$ denote the number of distinct prime factors of $a^2 - 4b = b_1$ and $m$ denote the number of distinct prime factors of $b$.
+    As shown in the lecture, have that $E'(\Q)/\phi(E(\Q)) \cong \im(q)$ and if $\overline{r} \in \im(q)$ with $r \in \Z$ square-free, then $r \divides b_1$.
+    Thus
+    \begin{equation*}
+        \#(E'(\Q)/\phi(E(\Q))) = \#\im(q) \leq \#\{ r \divides b_1 \ | \ r \in \Z \ \text{square-free}\}
+    \end{equation*}
+    Now observe that there is a bijection
+    \begin{equation*}
+        \mathfrak{P}(\{ -1 \} \cup \{ p \divides b_1 \ | \ p \ \text{prime}\}) \to \{ r \divides b_1 \ | \ r \in \Z \ \text{square-free} \}, \quad M \mapsto \prod_{x \in M} x
+    \end{equation*}
+    and so
+    \begin{equation*}
+        \#(E'(\Q)/\phi(E(\Q))) \leq 2^{l + 1}
+    \end{equation*}
+    Note that the map $\hat{\phi}$ is a group homomorphism with kernel of size 2, and therefore we find
+    \begin{equation*}
+        \#(\hat{\phi}(E'(\Q))/[2]E(\Q)) \leq 2^l
+    \end{equation*}
+    Similarly, find
+    \begin{equation*}
+        \#(E(\Q)/\hat{\phi}(E'(\Q))) \leq 2^{m + 1}
+    \end{equation*}
+    Since there is a surjection
+    \begin{equation*}
+        E(\Q)/\hat{\phi}(E'(\Q)) \oplus \hat{\phi}(E'(\Q))/[2]E(\Q) \to E(\Q)/[2]E(\Q)
+    \end{equation*}
+    we see that
+    \begin{equation*}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^{m + 1} = 2^{l + m + 1}
+    \end{equation*}
+    Finally, note that
+    \begin{equation*}
+        E(\Q)[2]E(\Q) \cong E_{\mathrm{tors}}(\Q)/[2]E(\Q) \oplus (\Z/2\Z)^{\mathrm{rank}(E)}
+    \end{equation*}
+    and thus $\Z/2\Z \hookrightarrow E_{\mathrm{tors}}(\Q)/[2]E(\Z)$ (there is the nontrivial 2-torsion point $(0, 0)$)
+    This yields
+    \begin{equation*}
+        \mathrm{rank}(E) \leq \log_2(\#(E(\Z)/[2]E(\Q)) / 2) \leq \log_2(2^{l + m}) = l + m \leq 2k
+    \end{equation*}
+
+    \paragraph{Assume $a \leq 0, b \geq 0$} Then the equation
+    \begin{equation*}
+        r l^4 + a l^2 m^2 + \frac b r = n^2
+    \end{equation*}
+    has no real nontrivial solutions for $r \leq 0$.
+    Since the solutions are in 1-to-1 correspondence with $\im(q)$, we see that
+    \begin{equation*}
+        \#(E(\Q)/\hat{\phi}(E'(\Q))) = \#\im(\hat{q}) \leq \#\{ r \divides b \ | \ r \in \Z \ \text{positive, square-free} \}
+    \end{equation*}
+    There is a bijection
+    \begin{equation*}
+        \mathfrak{P}(\{ p \divides b \ | \ p \ \text{prime} \}) \to \{ r \divides b \ | \ r \in \Z \ \text{positive, square-free} \}, \quad M \mapsto \prod_{x \in M} x
+    \end{equation*}
+    Thus
+    \begin{equation*}
+        \#(E(\Q)/\hat{\phi}(E'(\Q))) \leq 2^m
+    \end{equation*}
+    Hence as before find
+    \begin{equation*}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^m
+    \end{equation*}
+    and as before
+    \begin{equation*}
+        \mathrm{rank}(E) \leq \log_2(2^l \cdot 2^m / 2) = l + m - 1 \leq 2k - 1
+    \end{equation*}
+
+    \paragraph{Assume $a \perp b$} Then have that $b_1 = (a^2 - 4b) \perp b$ and thus we find that $l + m = k$.
+    Now have again
+    \begin{equation*}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^{m + 1}
+    \end{equation*}
+    and so
+    \begin{equation*}
+        \mathrm{rank}(E) \leq \log_2(2^{l + m + 1} / 2) = l + m = k
+    \end{equation*}
+
+    \paragraph{Assume $a \perp b$ and $a \leq 0, b \geq 0$} Now have both
+    \begin{equation*}
+        \#(E(\Q)/\hat{\phi}(E'(\Q))) \leq 2^m
+    \end{equation*}
+    and $m + l = k$.
+    As before, it follows
+    \begin{equation*}
+        \mathrm{rank}(E) \leq \log_2(2^{m + l} / 2) = m + l - 1 = k - 1
+    \end{equation*}
+\end{proof}
+Now we want to examine if the above inequalities are sharp.
+\begin{example}
+    Consider the curve $E: y^2 = x(x^2 - 6x + 1)$, which satisfies $a \leq 0, b \geq 0$ and $a \perp b$.
+    Furthermore, $b_1 = 6^2 - 4 = 32 = 2^5$ has only one prime factor.
+    Thus Proposition~\ref{prop:rank_bound} yields that $\mathrm{rank}(E) \leq 0$, so $\mathrm{rank}(E) = 0$.
+\end{example}
+Note that also Example~\ref{ex:special_curve} gives an example for the sharpness of part (iii), as the dual curve
+\begin{equation*}
+    E': y^2 = x(x - 92 x + 2089)
+\end{equation*}
+satisfies $a \leq 0, b \geq 0$ and $a \perp b$, and indeed its rank is $\mathrm{rank}(E') = 3 = 4 - 1$ (note that $2089 \cdot 30$ has exactly $4$ prime factors).
+
+The next example shows that also part (i) of Proposition~\ref{prop:rank_bound} is sharp.
+\begin{example}
+    Consider the curve $E: y^2 = x(x^2 + 8)$, which satisfies $a \leq 0, b \geq 0$.
+    Furthermore, $b b_1 = 8(-4 \cdot 8) = -256$ has only one prime factor.
+    Thus Proposition~\ref{prop:rank_bound} yields that $\mathrm{rank}(E) \leq 2 - 1 = 1$.
+    We claim that $\mathrm{rank}(E) = 1$.
+
+    As always, have the curve
+    \begin{equation*}
+        E': y^2 = x(x^2 - 32)
+    \end{equation*}
+    \paragraph{Find $E'(\Q)/\phi(E(\Q))$} Have $b_1 = -32$, so consider $r \in \{ \pm 1, \pm 2 \}$.
+
+    The equation
+    \begin{equation*}
+        -l^4 + 32m^4 = n^2
+    \end{equation*}
+    has the solution $(l, m, n) = (2, 1, 4)$ which gives a point $(-4, 8) \in E'(\Q)$.
+
+    The equation
+    \begin{equation*}
+        2l^4 -16m^4 = n^2
+    \end{equation*}
+    has the solution $(l, m, n) = (2, 1, 4)$ which gives a point $(8, 16) \in E'(\Q)$.
+
+    Hence also $-2 = -1 \cdot 2 \in \im(q)$ and we see that
+    \begin{equation*}
+        E'(\Q)/\phi(E(\Q)) = \langle (-4, 4), (8, 16) \rangle
+    \end{equation*}
+
+    \paragraph{Find $E(\Q)/\hat{\phi}(E'(\Q))$} Have $b = 8$, so consider $r \in \{ \pm 1, \pm 2 \}$.
+
+    The equation
+    \begin{equation*}
+        -l^4 - 8m^4 = n^2
+    \end{equation*}
+    has no solution in $\mathbb{R}$, thus no solution in $\Q$.
+
+    The equation
+    \begin{equation*}
+        2l^4 + 4m^4 = n^2
+    \end{equation*}
+    has the solution $(l, m, n) = (0, 1, 2)$ which gives a point $(0, 0) \in E(\Q)$.
+
+    Hence also $-2 = -1 \cdot 2 \notin \im(\hat{q})$ and we see that
+    \begin{equation*}
+        E(\Q)/\hat{\phi}(E'(\Q)) = \langle \hat{\phi}(-4, 8), \hat{\phi}(8, 16), (0, 0) \rangle = \langle (1, 3), (0, 0) \rangle
+    \end{equation*}
+
+    \paragraph{Find the rank of $E$} By the above, have
+    \begin{equation*}
+        E(\Q)/[2]E(\Q) = \langle (1, 3), (0, 0) \rangle
+    \end{equation*}
+    Note that the square of the $y$-coordinate $3^2 = 9$ does not divide $\Delta(E) = 4 \cdot 8^3 = 2^{11}$ and so $(1, 3)$ is not torsion by the Nagell-Lutz theorem.
+    So it is of infinite order, and we have indeed that $\mathrm{rank}(E) = 1$.
+\end{example}
+
+\section{Appendix}
+The curves from Example~\ref{ex:special_curve} were found by the following python script.
+\lstinputlisting[language = python]{4ii_computations.py}
+
 \end{document}

### 2022-03-18 Elliptic Curves/3ii_computations.py

@@ -1,63 +1,0 @@
-from math import sqrt, gcd
-
-def eval(r, a, b, l, m):
-    return r * l**4 + a * l**2 * m**2 + b/r * m**4
-
-def is_square(n):
-    if n < 0:
-        return False
-    return int(sqrt(n))**2 == n
-
-def can_prove_has_sol(r, a, b):
-    for l in range(50):
-        for m in range(50):
-            if (l != 0 or m != 0) and gcd(l, m) == 1:
-                if is_square(eval(r, a, b, l, m)):
-                    return True
-    return False
-
-def can_prove_has_no_sol(r, a, b):
-    for q in [90, 82, 110]:
-        squares = { x**2 % q for x in range(q) }
-        if len([(l, m) for l in range(q) for m in range(q) if eval(r, a, b, l, m)%q in squares]) == 1:
-            return True
-    return False
-
-def is_nice(r, a, b):
-    return (r < 0 and a <= 0 and b >= 0) or can_prove_has_no_sol(r, a, b) or can_prove_has_sol(r, a, b)
-
-def squarefree_factors(b):
-    pos_factors = [n for n in range(2, b + 1) if b%n == 0]
-    pos_sqrfree_factors = [n for n in pos_factors if len([m for m in pos_factors if n % m**2 == 0]) == 0]
-    return [1, -1, *pos_sqrfree_factors, *[-n for n in pos_sqrfree_factors]]
-
-def is_curve_nice(a, b):
-    a1 = -2 * a
-    b1 = a**2 - 4 * b
-    for r in squarefree_factors(b):
-        if not is_nice(r, a, b):
-            return False
-    for r in squarefree_factors(b1):
-        if not is_nice(r, a1, b1):
-            return False
-    return True
-
-exit()
-
-for a in range(60):
-    for b in range(60):
-        if a**2 - 4 * b != 0:
-            if is_curve_nice(a, b) and len(squarefree_factors(b)) >= 14:
-                print(a, b, len(squarefree_factors(b)))
-
-for a in range(60):
-    for b in range(60, 100):
-        if a**2 - 4 * b != 0:
-            if is_curve_nice(a, b) and len(squarefree_factors(b)) >= 14:
-                print(a, b, len(squarefree_factors(b)))
-
-for a in range(60, 100):
-    for b in range(100):
-        if a**2 - 4 * b != 0:
-            if is_curve_nice(a, b) and len(squarefree_factors(b)) >= 14:
-                print(a, b, len(squarefree_factors(b)))

### 2022-03-18 Elliptic Curves/4ii_computations.py

@@ -1,0 +1,63 @@
+from math import sqrt, gcd
+
+def eval(r, a, b, l, m):
+    return r * l**4 + a * l**2 * m**2 + b/r * m**4
+
+def is_square(n):
+    if n < 0:
+        return False
+    return int(sqrt(n))**2 == n
+
+def can_prove_has_sol(r, a, b):
+    for l in range(50):
+        for m in range(50):
+            if (l != 0 or m != 0) and gcd(l, m) == 1:
+                if is_square(eval(r, a, b, l, m)):
+                    return True
+    return False
+
+def can_prove_has_no_sol(r, a, b):
+    for q in [90, 82, 110]:
+        squares = { x**2 % q for x in range(q) }
+        sol_count_mod_q =  len([(l, m) 
+            for l in range(q) 
+            for m in range(q) 
+            if eval(r, a, b, l, m)%q in squares])
+        if sol_count_mod_q == 1:
+            return True
+    return False
+
+def is_nice(r, a, b):
+    return (r < 0 and a <= 0 and b >= 0) or \
+        can_prove_has_no_sol(r, a, b) or \
+        can_prove_has_sol(r, a, b)
+
+def sqrfree_factors(b):
+    pos_factors = [n for n in range(2, b + 1) if b%n == 0]
+    pos_sqrfree_factors = [n 
+        for n in pos_factors 
+        if len([m for m in pos_factors if n % m**2 == 0]) == 0]
+    return [
+        1, -1, 
+        *pos_sqrfree_factors, 
+        *[-n for n in pos_sqrfree_factors]
+    ]
+
+def is_curve_nice(a, b):
+    a1 = -2 * a
+    b1 = a**2 - 4 * b
+    for r in sqrfree_factors(b):
+        if not is_nice(r, a, b):
+            return False
+    for r in sqrfree_factors(b1):
+        if not is_nice(r, a1, b1):
+            return False
+    return True
+
+exit()
+
+for a in range(100):
+    for b in range(100):
+        if a**2 - 4 * b != 0 and len(sqrfree_factors(b)) >= 14:
+            if is_curve_nice(a, b):
+                print(a, b, len(squarefree_factors(b)))

### 2022-03-19 Schemes/submission.tex
Initial commit
Started schemes

--- 2022-03-11 Elliptic Curves/submission.tex
@@
 
-\title{Miniproject - Elliptic Curves}
+\title{Miniproject - Introduction to Schemes}
 \author{Simon Pohmann}
@@
 \newcommand{\p}{\mathfrak{p}}
+\newcommand{\m}{\mathfrak{m}}
+\renewcommand{\a}{\mathfrak{a}}
+\renewcommand{\b}{\mathfrak{b}}
+\renewcommand{\m}{\mathfrak{m}}
 \newcommand{\Set}{\mathrm{\textbf{Set}}}
@@
 \newcommand{\Spec}{\mathrm{Spec}}
+\newcommand{\Proj}{\mathrm{Proj}}
 \newcommand{\Quot}{\mathrm{Quot}}
@@
 \newtheorem{remark}[prop]{Remark}
+\newtheorem{reminder}[prop]{Reminder}
 
@@
 
+\section{Definition of $\Proj$}
+
+This section is based on \cite[II.2]{hartshorne}
+\begin{reminder}
+    A \emph{graded ring} $S$ is a ring $S$ with a decomposition $S = \oplus_{d \in \N} S_d$ into groups $S_i \subseteq S$ (w.r.t.
+addition in $S$) such that $S_i S_j \subseteq S_{i + j}$ for all $i, j \in \N$.
+    Write further $S_+ := \sum_{d > 0} S_d$.
+
+    An element $f \in S$ is called \emph{homogeneous} (of degree $n$), if $f \in S_n$.
+    An ideal $I \leq S$ is called \emph{homogeneous}, if it has a set of homogeneous generators.
+\end{reminder}
+\begin{definition}
+    For a graded ring $S$, define the set
+    \begin{equation*}
+        \Proj(S) := \{ \p \in \Spec(S) \ | \ \text{$\p$ homogeneous}, \ S_+ \not\subseteq \p \}
+    \end{equation*}
+    of homogeneous prime ideals not containing $S_+$.
+
+    This becomes a topological space by endowing it with the \emph{Zariski-topology} on $\Proj(S)$, given by the open sets
+    \begin{equation*}
+        D_{\a} := \{ \p \in \Proj(S) \ | \ \a \not\subseteq \p \}
+    \end{equation*}
+    for any homogeneous ideal $\a \leq S$.
+\end{definition}
+From now on let $S$ be a graded ring.
+\begin{prop}
+    The above definition is well-defined, i.e. the sets $D_\a$ indeed form a topology on $\Proj(S)$.
+\end{prop}
+\begin{proof}
+    Clearly $\Proj(S) = D_{\langle 1 \rangle}$ and $\emptyset = D_{\langle 0 \rangle}$ are open.
+    Furthermore, for open sets $D_\a$ and $D_\b$, have that
+    \begin{equation*}
+        D_\a \cap D_\b = \{ \p \in \Proj(S) \ | \ \a, \b \not\subseteq \p \} = \{ \p \in \Proj(S) \ | \ \a\b \not\subseteq \p \} = D_{\a\b}
+    \end{equation*}
+    This holds, as $\a, \b \not\subseteq \p$ implies that there are $f \in \a$ and $g \in \b$ with $f, g \notin \p$.
+    However, then $fg \notin \p$ as $\p$ is prime.
+    Obviously $\a\b$ is homogeneous, and so $D_\a \cap D_\b$ is open.
+
+    Finally, given a collection $\mathcal{A}$ of homogeneous ideals in $S$, have that
+    \begin{align*}
+        \bigcup_{\a \in \mathcal{A}} D_\a =& \{ \p \in \Proj(S) \ | \ \exists \a \in \mathcal{A}:\ \a \not\subseteq \p \} = \{ \p \in \Proj(S) \ | \ \exists \a \in \mathcal{A} \exists f \in \a:\ f \notin \p \} \\
+        =& \Bigl\{ \p \in \Proj(S) \ \Bigm| \ \exists f \in \sum_{\a \in \mathcal{A}} \a:\ f \notin \p \Bigr\} = D_{\b} \quad \text{for $\b = \sum_{\a \in \mathcal{A}} \a$}
+    \end{align*}
+    Clearly $\b$ is again homogeneous, and so $\bigcup_{\a \in \mathcal{A}} D_\a$ is open.
+\end{proof}
+\begin{prop}
+    The sets $D_f := D_{\langle f \rangle}$ for homogeneous $f \in S$ form a basis of the topology on $\Proj(S)$.
+\end{prop}
+\begin{proof}
+    Clearly $\langle f \rangle$ is a homogenous ideal, so $D_f$ is open.
+    For any homogeneous ideal $\a = \langle f_i \ | \ i \in I \rangle$ with $f_i \in S$ homogeneous have
+    \begin{equation*}
+        \a = \bigcup_{i \in I} D_{f_i}
+    \end{equation*}
+    as $\a \not\subseteq \p$ implies there is some $g = \sum_{i \in I} g_i f_i \notin \p$, with $g_i \in S$.
+    Hence, at least one $g_j f_j \notin \p$ and so $f_j \notin \p$, thus $\p \in D_{f_j}$.
+    It follows that the $D_f$ generate the topology on $\Proj(S)$, so it is left to show that they are a basis.
+
+    Consider $\p \in D_f \cap D_g$, so $f, g \notin \p$.
+    Since $\p$ is prime, it follows that $fg \notin \p$ and so $D_{fg} \subseteq D_f \cap D_g$ is an open neighborhood of $\p$.
+\end{proof}
+\begin{lemma}
+    If $D_g \subseteq D_f$ then there is a homogeneous $h \in S$ such that $g^n = fh$ for some $n \in \N$.
+\end{lemma}
+\begin{proof}
+    Assume not, then $f$ is not a unit in $S_g$.
+    Thus $\langle f \rangle \subseteq \m$ for a maximal ideal $\m \leq S_g$.
+    Now let $\p$ be the preimage of $\m$ under the localization map $S \to S_g$, so $g \in \p$ and $f \notin \p$.
+
+\end{proof}
+\begin{prop}
+    Let $B = \{ D_f \ | \ \text{$f \in S$ homogeneous}\}$.
+    The functor
+    \begin{align*}
+        \mathcal{F}: \restr{\Top(\Proj(S))}{B} \to \Ring, \quad D_f &\mapsto S_f \\
+        (D_{fg} \subseteq D_f) &\mapsto \Bigl( \frac s {f^n} \mapsto \frac {sg^n} {(fg)^n} \Bigr)
+    \end{align*}
+    is a B-sheaf on $B$ (here $\Top(X)$ is the category given by the open sets of $X$ and their inclusion, as defined in the lecture).
+\end{prop}
+
 \printbibliography

### 2022-03-19 Schemes/submission.tex
Prepared everything for Proj(S) sheaf construction

@@
 This section is based on \cite[II.2]{hartshorne}
-\begin{reminder}
-    A \emph{graded ring} $S$ is a ring $S$ with a decomposition $S = \oplus_{d \in \N} S_d$ into groups $S_i \subseteq S$ (w.r.t.
-addition in $S$) such that $S_i S_j \subseteq S_{i + j}$ for all $i, j \in \N$.
-    Write further $S_+ := \sum_{d > 0} S_d$.
+\begin{definition}
+    A \emph{graded ring} $S$ is a ring $S$ with a decomposition $S = \oplus_{d \in \Z} S_d$ into groups $S_i \subseteq S$ (w.r.t.
+addition in $S$) such that $S_i S_j \subseteq S_{i + j}$ for all $i, j \in \Z$.
+    If all $S_d = \{ 0 \}$ for $d < 0$, call $S$ \emph{naturally graded ring}.
+    Write further $S_+ := \sum_{d \neq 0} S_d$.
+    For a homogeneous $f \in S_d$ say that $\deg(f) := d$ is its \emph{degree}.
 
@@
     An ideal $I \leq S$ is called \emph{homogeneous}, if it has a set of homogeneous generators.
-\end{reminder}
+\end{definition}
 \begin{definition}
-    For a graded ring $S$, define the set
+    For a naturally graded ring $S$, define the set
     \begin{equation*}
@@
 \end{definition}
-From now on let $S$ be a graded ring.
+From now on let $S$ be a naturally graded ring.
 \begin{prop}
@@
 \begin{lemma}
+    Let $S$ be a graded ring (not necessarily naturally graded) and $f \in S$ be homogeneous. Then $S_f$ becomes a graded ring via
+    \begin{equation*}
+        \left(S_f\right)_d = \{ \frac g {f^n} \ | \ g \in S_{d + n} \}
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    Clearly $(S_f)_i (S_f)_j \subseteq (S_f)_{i + j}$.
+    To see that $(S_f)_d$ is a subgroup of $S$, consider $g/f^n, h/f^m \in (S_f)_d$.
+    wlog $n = m$ as we can replace $g$ by $gf^{m - n}$ resp. $h$ by $hf^{n - m}$.
+    Now have that $\deg(g) = \deg(h) = d + n$ and so $g + h \in S_{d + n}$.
+    Thus
+    \begin{equation*}
+        \frac g {f^n} + \frac h {f^n} = \frac {g + h} {f^n} \in (S_f)_d
+    \end{equation*}
+    Finally, we show that $(S_f)_i \cap (S_f)_j = \{ 0 \}$ for $i \neq j$.
+    Assume there is $g/f^i = h/f^j \in (S_f)_n \cap (S_f)_m$.
+    Then there exists $t = f^d$ such that
+    \begin{equation*}
+        0 = t(gf^j - hf^i) = \underbrace{g f^{j + d}}_{\in S_{(j + d)\deg(f) + \deg(g)}} - \underbrace{h f^{i + n}}_{\in S_{(i + d)\deg(f) + \deg(h)}}
+    \end{equation*}
+    Thus either $(j + d)\deg(f) + \deg(g) = (i + d)\deg(f) + \deg(h)$ or $gf^{j + d} = hf^{i + d} = 0$.
+    However have that $\deg(g) = n - \deg(f)i$ and $\deg(h) = m - \deg(f)j$, so
+    \begin{equation*}
+        (j + d - i)\deg(f) + n \neq (i + d - j)\deg(f) + n
+    \end{equation*}
+    as $i \neq j$.
+    So $gf^{j + d} = hf^{i + d} = 0$ and hence $g/f^i = hf^j = 0$.
+    Therefore we have $(S_f)_i \cap (S_f)_j = \{ 0 \}$ as claimed.
+\end{proof}
+\begin{lemma}
+    \label{prop:homogeneous_part_prime}
+    Let $\p \leq S$ be a prime ideal.
+    Then
+    \begin{equation*}
+        \p' := \langle f \in \p \ | \ \text{$f$ homogeneous} \rangle \leq S
+    \end{equation*}
+    is a (homogeneous) prime ideal.
+\end{lemma}
+\begin{proof}
+    Consider $f, g \in S$ with $f g \in \p'$ and assume $f, g \notin \p'$.
+    Write $f = \sum_d f_d$ and $g = \sum_d g_d$ with $f_d, g_d \in S_d$.
+    So
+    \begin{equation*}
+        \sum_{i, j} f_i g_j = \sum_n \sum_{i + j = n} f_i g_j \in \p'
+    \end{equation*}
+    Since $\p'$ is homogeneous, it follows that
+    \begin{equation*}
+        \sum_{i + j = n} f_i g_j \in \p'
+    \end{equation*}
+    for all $n \in \Z$.
+
+    Let now $d$ resp. $e$ be maximal such that $f_d \notin \p'$ resp. $g_e \notin \p'$.
+    We have
+    \begin{equation*}
+        f_d g_e + \sum_{\substack{i + j = d + e\\(i, j) \neq (d, e)}} \underbrace{f_i g_j}_{\in \p'} = \sum_{i + j = d + e} f_i g_j \in \p'
+    \end{equation*}
+    and so $f_d g_e \in \p' \subseteq \p$.
+    Since $\p$ is prime, it follows that $f_d \in \p$ or $g_e \in \p$.
+    However both $f_d$ and $g_e$ are homogeneous, so $f_d \in \p'$ or $g_e \in \p'$, a contradiction.
+\end{proof}
+\begin{lemma}
     If $D_g \subseteq D_f$ then there is a homogeneous $h \in S$ such that $g^n = fh$ for some $n \in \N$.
@@
     Assume not, then $f$ is not a unit in $S_g$.
-    Thus $\langle f \rangle \subseteq \m$ for a maximal ideal $\m \leq S_g$.
-    Now let $\p$ be the preimage of $\m$ under the localization map $S \to S_g$, so $g \in \p$ and $f \notin \p$.
+    Hence, there is a maximal ideal $\m \leq S_g$ such that $f \in \m$.
+    Now let $\p$ be the preimage of $\m$ under the localization map $S \to S_g$.
+    Since $\m$ is maximal, we see that $\p$ is prime.
 
+    Now apply Lemma~\ref{prop:homogeneous_part_prime} and see that also
+    \begin{equation*}
+        \p' = \langle f \in \p \ | \ \text{$f$ homogeneous} \rangle \subseteq \p
+    \end{equation*}
+    is prime.
+    Furthermore, $g \notin \p$ and so $g \notin \p'$.
+    wlog we have that $g \in S_+$, so $S_+ \not\subseteq \p'$.
+    Since now $\p'$ is a homogeneous prime ideal, it follows that $\p' \in \Proj(S)$.
+
+    Finally, observe that $f \in \p'$ as $f \in \p$ and $f$ is homogeneous.
+    Hence, we have that $\p' \notin D_f$ and $\p' \in D_g$, which contradicts the assumption that $D_g \subseteq D_f$.
 \end{proof}
@@
     \begin{align*}
-        \mathcal{F}: \restr{\Top(\Proj(S))}{B} \to \Ring, \quad D_f &\mapsto S_f \\
+        \mathcal{F}: \restr{\Top(\Proj(S))}{B} \to \Ring, \quad D_f &\mapsto (S_f)_0 \\
         (D_{fg} \subseteq D_f) &\mapsto \Bigl( \frac s {f^n} \mapsto \frac {sg^n} {(fg)^n} \Bigr)
@@
 \end{prop}
+\begin{proof}
+    Clearly, $\mathcal{F}$ is a functor and thus a presheaf.
+    Hence, we have to show the local-to-global property.
+
+    Let $D_f = \bigcup_{i \in I} D_{g_if}$ be a cover and $s_i \in \mathcal{F}(D_{g_if})$ such that
+    \begin{equation*}
+        \forall x \in D_{g_if} \cap D_{g_jf} \ \exists V \in B: \ V \subseteq D_{g_if} \cap D_{g_jf}, \ x \in V, \ \frac {s_i} 1 = \frac {s_j} 1 \in \mathcal{F}(V)
+    \end{equation*}
+\end{proof}
 

### 2022-03-20 Schemes/submission.tex
Proved that (Proj(S), O) is a scheme

@@
 
-This section is based on \cite[II.2]{hartshorne}
 \begin{definition}
@@
 \begin{lemma}
-    Let $S$ be a graded ring (not necessarily naturally graded) and $f \in S$ be homogeneous. Then $S_f$ becomes a graded ring via
+    Let $S$ be a graded ring (not necessarily naturally graded) and $T \subseteq S$ a multiplicative set consisting of homogeneous elements. 
+    Then $T^{-1}S$ becomes a graded ring via
     \begin{equation*}
-        \left(S_f\right)_d = \{ \frac g {f^n} \ | \ g \in S_{d + n} \}
+        \left(T^{-1}S\right)_d = \Bigl\{ \frac g h \in T^{-1}S \ \Bigm| \ \text{$g$ homogeneous with $\deg(g) - \deg(h) = d$} \Bigr\}
     \end{equation*}
@@
 \begin{proof}
-    Clearly $(S_f)_i (S_f)_j \subseteq (S_f)_{i + j}$.
-    To see that $(S_f)_d$ is a subgroup of $S$, consider $g/f^n, h/f^m \in (S_f)_d$.
-    wlog $n = m$ as we can replace $g$ by $gf^{m - n}$ resp. $h$ by $hf^{n - m}$.
-    Now have that $\deg(g) = \deg(h) = d + n$ and so $g + h \in S_{d + n}$.
-    Thus
+    Clearly $(T^{-1}S)_i (T^{-1}S)_j \subseteq (T^{-1}S)_{i + j}$.
+    To see that $(T^{-1}S)_d$ is a subgroup of $S$, consider $g/f, l/h \in (T^{-1}S)_d$.
+    Now have
     \begin{equation*}
-        \frac g {f^n} + \frac h {f^n} = \frac {g + h} {f^n} \in (S_f)_d
+        \frac g f + \frac l h = \frac {gh + lf} {hf}
     \end{equation*}
-    Finally, we show that $(S_f)_i \cap (S_f)_j = \{ 0 \}$ for $i \neq j$.
-    Assume there is $g/f^i = h/f^j \in (S_f)_n \cap (S_f)_m$.
-    Then there exists $t = f^d$ such that
+    and by assumption, find $\deg(gh) = \deg(g) - \deg(h) = d + \deg(f) - d + \deg(l) = \deg(lf)$.
+    So $gh + lf$ is homogeneous and we have
     \begin{equation*}
-        0 = t(gf^j - hf^i) = \underbrace{g f^{j + d}}_{\in S_{(j + d)\deg(f) + \deg(g)}} - \underbrace{h f^{i + n}}_{\in S_{(i + d)\deg(f) + \deg(h)}}
+        \deg(gh + lf) - \deg(fh) = \deg(f) + \deg(l) - \deg(f) - \deg(h) = \deg(l) - \deg(h) = d
     \end{equation*}
-    Thus either $(j + d)\deg(f) + \deg(g) = (i + d)\deg(f) + \deg(h)$ or $gf^{j + d} = hf^{i + d} = 0$.
-    However have that $\deg(g) = n - \deg(f)i$ and $\deg(h) = m - \deg(f)j$, so
-    \begin{equation*}
-        (j + d - i)\deg(f) + n \neq (i + d - j)\deg(f) + n
-    \end{equation*}
-    as $i \neq j$.
-    So $gf^{j + d} = hf^{i + d} = 0$ and hence $g/f^i = hf^j = 0$.
-    Therefore we have $(S_f)_i \cap (S_f)_j = \{ 0 \}$ as claimed.
+    Thus $g/f + l/h \in (T^{-1}S)_d$.
+
+    Finally, we show that $(T^{-1}S)_n \cap (T^{-1}S)_m = \{ 0 \}$ for $i \neq j$.
+    Assume there is $g/f = l/h \in (T^{-1}S)_n \cap (T^{-1}S)_m$ with $\deg(g) - \deg(f) = n$ and $\deg(l) - \deg(h) = m$.
+    Then there exists $t \in T$ such that
+    \begin{align*}
+        0 = t(gh - lf) =& tgh - tlf \quad \text{with}\ tgh \in S_{\deg(t) + \deg(g) + \deg(h)} \\
+        &\text{and}\ tlf \in S_{\deg(t) + \deg(l) + \deg(f)} = S_{\deg(t) + \deg(g) + \deg(h) + (m - n)}
+    \end{align*}
+    If $n \neq m$, then $S_{\deg(t) + \deg(g) + \deg(h) + (m - n)} \cap S_{\deg(t) + \deg(g) + \deg(h)} = \{ 0 \}$ and so $tgh = tlf = 0$.
+    Thus $th(g - 0) = 0$ and so $g/f = 0/1 = 0$.
+    Thus $(T^{-1}S)_m \cap (T^{-1}S)_n = \{ 0 \}$.
 \end{proof}
@@
 \end{proof}
+The next proof works exactly as the corresponding one for $\Spec$ in the lecture.
 \begin{prop}
@@
         \mathcal{F}: \restr{\Top(\Proj(S))}{B} \to \Ring, \quad D_f &\mapsto (S_f)_0 \\
-        (D_{fg} \subseteq D_f) &\mapsto \Bigl( \frac s {f^n} \mapsto \frac {sg^n} {(fg)^n} \Bigr)
+        (D_{fg} \subseteq D_f) &\mapsto \Bigl( \restr{\cdot}{D_{fg}}: \frac s {f^n} \mapsto \frac {sg^n} {(fg)^n} \Bigr)
     \end{align*}
@@
     \end{equation*}
+    To show uniqueness, it suffices to show that if
+    \begin{equation*}
+        \restr{\alpha}{D_{h_i}} = \restr{\beta}{D_{h_i}} \quad \text{for any $h_i$ with}\ \Proj(S) = \bigcup_i D_{h_i}
+    \end{equation*}
+    then $\alpha = \beta$.
+
+    By assumption, have $h_i^{n_i}(\alpha - \beta) = 0$ for each $i$, and wlog there are only finitely many $i$.
+    Thus find $N = \max_i n_i \in \N$ and get that $h_i^N(\alpha - \beta) = 0$.
+    Since $\bigcup_i D_{h_i} = \Proj(S)$ it follows that $\bigcup_i D_{h_i^N} = \Proj(S)$ and so $1 \in \langle h_i^N \ | \ i \rangle$.
+    It follows that
+    \begin{equation*}
+        \alpha - \beta = 1(\alpha - \beta) \in \langle h_i^N \ | \ i \rangle (\alpha - \beta) = \langle h_i^N (\alpha - \beta) \ | \ i \rangle = \{ 0 \}
+    \end{equation*}
+    and so $\alpha = \beta$.
+
+    Now we show existence.
+    By the uniqueness above, it follows that
+    \begin{equation*}
+        \restr{s_i}{D_{fg_ig_j}} = \restr{s_i}{D_{fg_i} \cap D_{fg_j}} = \restr{s_j}{D_{fg_i} \cap D_{fg_j}} = \restr{s_j}{D_{fg_ig_j}}
+    \end{equation*}
+    wlog have again a finite cover, i.e. only finitely many $g_i$.
+    Hence find an $N \in \N$ such that each $s_i = s'_i / (fg_i)^N$ with $s'_i \in S$ homogeneous.
+    By possibly replacing $N$ with a bigger $N$, we can now assume that
+    \begin{equation*}
+        (f^2g_ig_j)^N \left( s'_i (fg_j)^N - s'_j (fg_i)^N \right) = 0 \quad \text{as $\restr{s_i}{D_{fg_ig_j}} = \restr{s_j}{D_{fg_ig_j}}$}
+    \end{equation*}
+    Now note that
+    \begin{equation*}
+        s_i = \frac {a_i} {b_i} \quad \text{with}\ a_i = s'_i(fg_i)^N, \ b_i = (fg_i)^{2N}
+    \end{equation*}
+    and
+    \begin{equation*}
+        a_i b_j - a_j b_i = s'_i (fg_i)^N (fg_j)^{2N} - s'_j (fg_j)^N (fg_i)^{2N} = \underbrace{(f^2g_ig_j)^N \left(s'_i (fg_j)^N - s'_j (fg_i)^N \right)}_{= 0}
+    \end{equation*}
+    Now observe that $D_{b_i} = D_{fg_i}$ and so $f^m \in \langle b_i \ | \ i \rangle$ for some $m$.
+    Let $1 = \sum_i r_i b_i$ and get
+    \begin{equation*}
+        a_i f^m = \sum_l r_l b_l a_i = \sum_l r_l a_l b_i = b_i \sum_l r_l a_l
+    \end{equation*}
+    Note that $a_i, b_i, f$ are homogeneous, and so we can also choose $r_i$ to be homogeneous.
+    Then find that $0 = \deg(s_i) = \deg(a_i) - \deg(b_i) = \deg(\sum r_l a_l) - m\deg(f)$.
+
+    Thus
+    \begin{equation*}
+        s_i = s := \frac {\sum_l r_l a_l} {f^m} \in S_f
+    \end{equation*}
+    and since $\deg(\sum r_l a_l) = m\deg(f)$ we find that $s \in (S_f)_0 = \mathcal{F}(D_f)$.
+    Clearly $\restr{s}{D_{fg_i}} = s_i$ and the claim follows.
 \end{proof}
+\begin{corollary}
+    Hence we can (uniquely) extend the B-sheaf $\mathcal{F}$ to a sheaf $\O_{\Proj(S)}$ on $\Proj(S)$.
+\end{corollary}
+The next to lemmas are based on \cite[II.2.5]{hartshorne} and show that $(\Proj(S), \O_{\Proj(S)})$ is a scheme.
+\begin{lemma}
+    For $\p \in \Proj(S)$, the stalk
+    \begin{equation*}
+        \O_{\Proj(S), \p} = (T^{-1}S)_0
+    \end{equation*}
+    is a local ring, where $T = \{ f \notin \p \ | \ \text{$f$ homogeneous}\}$ contains all homogeneous elements not in $\p$.
+\end{lemma}
+\begin{proof}
+    Consider the ideal
+    \begin{equation*}
+        \m = \Bigl\{ \frac f g \in (T^{-1}S)_0 \ \Bigm| \ f \in \p \Bigr\}
+    \end{equation*}
+    We claim this is the unique maximal ideal of $(T^{-1}S)_0$.
+
+    First, note that $1 \notin (T^{-1}S)_0$ as otherwise, there would be $f/g \in T^{-1}S, f \in \p$ with $t(f - g) = 0$ for some $t \in T$.
+    However then $tg = tf \in \p$, and so $g \in \p$ (as $t \notin \p$), contradicting $g \in T$.
+
+    Now assume there is any ideal $\a$ such that $\a \setminus \m \neq \emptyset$, i.e. there is $f/g \in \a \setminus \m$.
+    Then $f \in T$ as $f$ homogeneous and $f \notin \p$.
+    Thus $g/f \in (T^{-1}S)_0$ and so $f/g \in (T^{-1}S)_0^*$, which implies $\a = \langle 1 \rangle$.
+\end{proof}
+\begin{lemma}
+    For $f \in S_+$ homogeneous have that $(D_f, \restr{\O_{\Proj(S)}}{D_f})$ is an affine scheme.
+\end{lemma}
+\begin{proof}
+    Let $R = (S_f)_0$.
+    Consider the map
+    \begin{equation*}
+        f: D_f \to \Spec(R), \quad \p \mapsto \p S_f \cap (S_f)_0
+    \end{equation*}
+    Note that it is continuous, as the preimage of some basic open set $D_{g/f^n}$ is $D_{fg} \subseteq D_f$ open.
+    Furthermore, $f$ has the inverse
+    \begin{equation*}
+        f^{-1}: \Spec(R) \to D_f, \quad \p \mapsto \p S_f
+    \end{equation*}
+    which is also continuous, as the preimage of some basic open set $D_{fg}$ is $D_{g^n/f^m}$ where $n\deg(g) = m\deg(f)$.
+    Thus $f$ is a homeomorphism.
+
+    Now consider the natural transformation
+    \begin{equation*}
+        \eta: \O_{\Spec R} \Rightarrow f_*\Bigl( \restr{\O_{\Proj(S)}}{D_f} \Bigr)
+    \end{equation*}
+    given on basic open sets by
+    \begin{equation*}
+        \eta_{D_{g/f^n}}: R_{g/f^n} \to (S_{fg})_0, \quad \frac {h/f^m} {g/f^n} \mapsto \frac {h f^n} {g f^m}
+    \end{equation*}
+    Clearly this is a ring isomorphism, so $\eta$ is a natural isomorphism.
+    The claim follows.
+\end{proof}
+\begin{corollary}
+    $(\Proj(S), \O_{\Proj(S)})$ is a scheme.
+\end{corollary}
 

### 2022-03-24 Schemes/submission.tex
Prove PR x S = PS

@@
 \newcommand{\V}{\mathbb{V}}
+\newcommand{\A}{\mathbb{A}}
+\renewcommand{\P}{\mathbb{P}}
 \newcommand{\p}{\mathfrak{p}}
+\newcommand{\q}{\mathfrak{q}}
 \newcommand{\m}{\mathfrak{m}}
@@
 \renewcommand{\m}{\mathfrak{m}}
+\newcommand{\Nil}{\mathfrak{N}}
 \newcommand{\Set}{\mathrm{\textbf{Set}}}
@@
 \newcommand{\Proj}{\mathrm{Proj}}
-\newcommand{\Quot}{\mathrm{Quot}}
+\newcommand{\Frac}{\mathrm{Frac}}
 \newcommand{\im}{\mathrm{im}}
@@
 \maketitle
+
+\tableofcontents
 
@@
     \begin{equation*}
-        \a = \bigcup_{i \in I} D_{f_i}
+        D_\a = \bigcup_{i \in I} D_{f_i}
     \end{equation*}
@@
     \end{equation*}
-    To show uniqueness, it suffices to show that if
+    To show uniqueness, assume there are $\alpha/f^N, \beta/f^N \in D_f$ with
     \begin{equation*}
-        \restr{\alpha}{D_{h_i}} = \restr{\beta}{D_{h_i}} \quad \text{for any $h_i$ with}\ \Proj(S) = \bigcup_i D_{h_i}
+        \restr{\frac {\alpha} {f^N}}{D_{g_if}} = \restr{\frac {\beta} {f^N}}{D_{g_if}} \quad \text{for all $i$}
     \end{equation*}
-    then $\alpha = \beta$.
+    Therefore there is $n_i \in \N$ such that
+    \begin{equation*}
+        (fg_i)^{n_i}
+    \end{equation*}
 
@@
     Now observe that $D_{b_i} = D_{fg_i}$ and so $f^m \in \langle b_i \ | \ i \rangle$ for some $m$.
-    Let $1 = \sum_i r_i b_i$ and get
+    Let $f^m = \sum_i r_i b_i$ and get
     \begin{equation*}
@@
 \begin{lemma}
+    \label{prop:Df_affine}
     For $f \in S_+$ homogeneous have that $(D_f, \restr{\O_{\Proj(S)}}{D_f})$ is an affine scheme.
@@
     \begin{equation*}
-        \eta_{D_{g/f^n}}: R_{g/f^n} \to (S_{fg})_0, \quad \frac {h/f^m} {g/f^n} \mapsto \frac {h f^n} {g f^m}
+        \eta_{D_{g/f^n}}: R_{g/f^n} \to (S_{fg})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
     \end{equation*}
@@
 \end{corollary}
+\begin{definition}
+    For any ring $R$ and $n \in \N$, define the projective $n$-space as\footnote{Endow $R[x_0, ..., x_n]$ with the standard natural grading, i.e.
+$\deg(x_i) = 1$.
+Note that this makes $R[x_0, ..., x_n]_0 = R$, so all $r \in R$ are homogeneous of degree $0$.}
+    \begin{equation*}
+        \P_R^n := \Proj(R[x_0, ..., x_n])
+    \end{equation*}
+    which naturally becomes a scheme over $\Spec(R)$ via the morphism given by
+    \begin{align*}
+        &f: \Proj(R[x_0, ..., x_n]) \to \Spec(R), \quad \p \mapsto \p \cap R \\
+        &f^\#_{D_f}: R_f \to \O_{\Proj(S)}(D_f) = (R[x_0, ..., x_n]_f)_0, \quad r \mapsto r
+    \end{align*}
+\end{definition}
 
+\section{Projective space as a variety}
+For this section, let $R$ be a ring and $n \in \N$.
+\begin{prop}
+    Projective $n$-space $\P_R^n \to \Spec(R)$ over $\Spec(R)$ is separated.
+\end{prop}
+\begin{proof}
+    By Lemma~\ref{prop:Df_affine} we find a cover $\Proj(S) = \bigcup_i D_{x_i}$ of affine opens.
+    We use the characterization from the lecture and show that $D_{x_i} \cap D_{x_j}$ is an affine open and the canonical multiplication map
+    \begin{equation*}
+        \O_{\P_R^n}(D_{x_i}) \times \O_{\P_R^n}(D_{x_j}) \to \O_{\P_R^n}(D_{x_i} \cap D_{x_j})
+    \end{equation*}
+    is surjective.
+
+    First note that $D_{x_i} \cap D_{x_j} = D_{x_ix_j}$ which is affine open by Lemma~\ref{prop:Df_affine}.
+    By definition, we have $\O_{\P_R^n}(D_f) = (R[x_0, ..., x_n]_f)_0$ and so we have to show that
+    \begin{equation*}
+        (R[x_0, ..., x_n]_{x_i})_0 \times (R[x_0, ..., x_n]_{x_j})_0 \to (R[x_0, ..., x_n]_{x_ix_j})_0, \quad (a, b) \mapsto ab
+    \end{equation*}
+    is surjective.
+
+    However, for $f/(x_ix_j)^n \in (R[x_0, ..., x_n]_{x_ix_j})_0$ we have that
+    \begin{equation*}
+        \frac f {x_i^{2n}} \cdot \frac {x_i^n} {x_j^n} = \frac f {(x_ix_j)^n}
+    \end{equation*}
+    and clearly $f/x_i^{2n} \in (R[x_0, ..., x_n]_{x_i})_0$ as $\deg(f) = \deg(x_i) n + \deg(x_j) n = 2n$ and $x_i^n/x_j^n \in (R[x_0, ..., x_n]_{x_j})_0$.
+    The claim follows
+\end{proof}
+\begin{lemma}
+    \label{prop:nil_poly_ring}
+    It holds that $\Nil(R)R[x_0, ..., x_n] = \Nil(R[x_0, ..., x_n])$.
+\end{lemma}
+\begin{proof}
+    Clearly $\Nil(R)R[x_0, ..., x_n] \subseteq \Nil(R[x_0, ..., x_n])$, as for $\sum_{i = 1}^m f_i r_i$ with $f_i^n = 0$ have that
+    \begin{equation*}
+        \Bigl( \sum_{i = 1}^m f_i r_i \Bigr)^{m n} = \sum_{1 \leq i_1, ..., i_{mn} \leq m} \underbrace{f_{i_1} ...
+f_{i_{mn}}}_{\mathclap{\substack{= 0 \\ \text{as at least one $i$ repeats at least $n$ times in $i_1, ..., i_{mn}$}}}} r_{i_1} ...
+r_{i_mn}
+    \end{equation*}
+    Now note that $\Nil(R[x_0, ..., x_n]) \subseteq \a$ for all ideals $\a$ and the claim follows.
+\end{proof}
+\begin{prop}
+    Assume $\Spec(R)$ is irreducible.
+    Then $\P_R^n$ is an irreducible scheme.
+\end{prop}
+\begin{proof}
+    We show that $D_{x_0} \subseteq \P_R^n$ is dense.
+    The claim then follows, as any two nonempty, disjoint open sets give nonempty, disjoint open sets in $D_{x_0}$ which is isomorphic to the 
+    irreducible\footnote{This is obviously irreducible, as $R[x_0, ..., x_n]/\Nil(R[x_0, ..., x_n]) = (R/\Nil(R))[x_0, ..., x_n]$ is integral by assumption and Lemma~\ref{prop:nil_poly_ring}.}
+    affine scheme $\Spec(R[x_0, ..., x_n]_{x_0})_0$ by Lemma~\ref{prop:Df_affine}.
+
+    So consider any nonempty basic open $D_f \subseteq \P_R^n$ and find that $D_f \cap D_{x_0} = D_{fx_0}$.
+    By assumption, $\Nil(R)$ is a prime ideal and so $fx_0$ is not nilpotent (unless $f$ were nilpotent, but then $D_f = \emptyset$), i.e. the ring $R[x_0, ..., x_n]_{fx_0}$ is not the zero ring.
+    Hence, it has a maximal ideal $\m$.
+    Let $\p$ be the preimage of $\m$ under the localization map $R[x_0, ..., x_n] \to R[x_0, ..., x_n]_{fx_0}$, which is clearly prime with $fx_0 \notin \p$.
+    By Lemma~\ref{prop:homogeneous_part_prime}, we now see that
+    \begin{equation*}
+        \p' := \langle f \in \p \ | \ \text{$f$ homogeneous} \rangle \leq R[x_0, ..., x_n]
+    \end{equation*}
+    is a homogeneous prime ideal, and since $fx_0 \notin \p \supseteq \p'$, we see that $S_+ \not\subseteq \p'$, i.e. $\p' \in \Proj(R[x_0, ..., x_n])$.
+    Now it follows that $\p' \in D_{fx_0}$, so $D_{fx_0} \neq \emptyset$.
+\end{proof}
+\begin{prop}
+    Assume $R$ is reduced.
+    Then $\P_R^n$ is a reduced scheme.
+\end{prop}
+\begin{proof}
+    By the lecture, it suffices to show that each $\O_{\P_R^n}(D_{x_i}) \cong \Spec(R[x_0, ..., x_n]_{x_i})_0$ is reduced.
+    However this is trivial, as taking the polynomial ring $R[x_0, ..., x_n]$ preserves reducedness by Lemma~\ref{prop:nil_poly_ring}, and localizing (and of course taking the subring $S_0$) also do.
+\end{proof}
+\begin{corollary}
+    Assume $R$ is integral.
+    Then $\P_R^n$ is an integral scheme.
+\end{corollary}
+\begin{prop}
+    $\P_R^n \to \Spec(R)$ is of finite type.
+\end{prop}
+\begin{proof}
+    First note that $\P_R^n$ is covered by a finite number of affine opens $D_{x_i}$ where the canonical morphisms
+    \begin{equation*}
+        D_{x_i} \cong \Spec(R[x_0, ..., x_n]_{x_i})_0 \to \Spec(R)
+    \end{equation*}
+    are quasi-compact (they are induced by ring homomorphisms $R \to (R[x_0, ..., x_n]_{x_i})_0$), hence $\P_R^n$ is quasi-compact.
+
+    To see that it is locally of finite type, show that there is the cover by affine opens $\P_R^n = \bigcup_i D_{x_i}$ such that the ring homomorphisms $R \to \O_{\P_R^n}(D_{x_i})$ are of finite type.
+    This is clearly the case, as
+    \begin{equation*}
+        \O_{\P_R^n}(D_{x_i}) = (R[x_0, ..., x_n]_{x_i})_0 \cong R[y_0, ..., y_{i - 1}, y_i, ..., y_n]
+    \end{equation*}
+    is a finitely generated $R$-algebra.
+\end{proof}
+\begin{corollary}
+    If $k$ is an algebraically closed field, then $\P_k^n$ is a variety.
+\end{corollary}
+
+\section{Projective space is proper}
+We already know that $\P_R^n$ is separated and of finite type over $\Spec(R)$, hence it is left to show that it is universally closed.
+\begin{lemma}
+    Let $X, Y$ be topological spaces and $f: X \to Y$ a continuous map.
+    Let further $Y = \bigcup_i V_i$ be a cover by open sets.
+    If each of the maps
+    \begin{equation*}
+        \restr{f}{f^{-1}(V_i)}: f^{-1}(V_i) \to V_i
+    \end{equation*}
+    is closed (as a map into $V_i$), then $f$ is closed.
+\end{lemma}
+\begin{proof}
+    Consider some closed $C \subseteq X$ and $x \in Y \setminus f(C)$.
+    Since the $V_i$ cover $Y$, there is $i$ such that $x \in V_i$.
+    As $\restr{f}{f^{-1}(V_i)}$ is closed, we see that
+    \begin{equation*}
+        f(C) \cap V_i = \restr{f}{f^{-1}(V_i)}(C)
+    \end{equation*}
+    is closed in $V_i$, hence there is an open neighborhood $U \subseteq V_i$ of $x$ with $U \cap f(C) = \emptyset$.
+    Now note that $V_i \subseteq Y$ is open, and so $U$ is also an open neighborhood of $x$ in $Y$.
+    This holds for all $x \in Y \setminus f(C)$, hence $f(C)$ is closed.
+\end{proof}
+\begin{corollary}
+    A scheme $X$ over $\Spec(R)$ is universally closed, if for all ring homomorphisms $R \to S$ have the following:
+    The map $X \times_{\Spec(R)} \Spec(S) \to \Spec(S)$ that makes the diagram
+    \begin{center}
+        \begin{tikzpicture}
+            \node (SX) at (0, 0) {$\Spec(S) \times_{\Spec(R)} X$};
+            \node (S) at (0, -1.5) {$\Spec(S)$};
+            \node (X) at (4, 0) {$X$};
+            \node (R) at (4, -1.5) {$\Spec(R)$};
+
+            \draw [->] (SX) -- (S);
+            \draw [->] (SX) -- (X);
+            \draw [->] (S) -- (R);
+            \draw [->] (X) -- (R);
+        \end{tikzpicture}
+    \end{center}
+    is closed.
+\end{corollary}
+\begin{proof}
+    Consider any scheme $Y$ over $\Spec(R)$.
+    We have to show that the map $\pi: Y \times_{\Spec(R)} X \to Y$ that makes the diagram
+    \begin{center}
+        \begin{tikzpicture}
+            \node (YX) at (0, 0) {$Y \times_{\Spec(R)} X$};
+            \node (Y) at (0, -1.5) {$Y$};
+            \node (X) at (4, 0) {$X$};
+            \node (R) at (4, -1.5) {$\Spec(R)$};
+
+            \draw [->] (YX) -- (Y) node [midway, left] {$\pi$};
+            \draw [->] (YX) -- (X);
+            \draw [->] (Y) -- (R);
+            \draw [->] (X) -- (R);
+        \end{tikzpicture}
+    \end{center}
+    commute, is closed.
+
+    Let $Y = \bigcup_i V_i$ be a cover by affine opens.
+    For each $i$, note that the diagram
+    \begin{center}
+        \begin{tikzpicture}
+            \node (YX) at (0, 0) {$\pi^{-1}(V_i)$};
+            \node (Y) at (0, -2) {$V_i$};
+            \node (X) at (4, 0) {$X$};
+            \node (R) at (4, -2) {$\Spec(R)$};
+
+            \draw [->] (YX) -- (Y) node [midway, left] {$\pi_i := \restr{\pi}{\pi^{-1}(V_i)}$};
+            \draw [->] (YX) -- (X);
+            \draw [->] (Y) -- (R);
+            \draw [->] (X) -- (R);
+        \end{tikzpicture}
+    \end{center}
+    commutes.
+    By the universal property of $V_i \times_{\Spec(R)} X$ we now find a morphism
+    \begin{equation*}
+        \psi: \pi^{-1}(V_i) \to V_i \times_{\Spec(R)} X
+    \end{equation*}
+    of schemes over $Y \times X$, i.e. the inclusion $\pi^{-1}(V_i)$ factors as
+    \begin{equation*}
+        \pi^{-1}(V_i) \ \overset{\psi}{\to} \ V_i \times_{\Spec(R)} X \ \to \ Y \times_{\Spec(R)} X
+    \end{equation*}
+    Considering $V_i \times_{\Spec(R)} X$ as an open subscheme of $Y \times_{\Spec(R)} X$, we thus see that $\psi$ must already be the identity and so $\pi^{-1}(V_i) \subseteq V_i \times_{\Spec(R)} X$.
+    It follows that $\pi^{-1}(V_i) = V_i \times_{\Spec(R)} X$.
+
+    By assumption we know that each $\pi_i$ is closed, as $V_i \cong \Spec(\O_Y(V_i))$ is affine.
+    Now the previous lemma yields that also $\pi$ is closed.
+\end{proof}
+\begin{remark}
+    \label{prop:functoriality_proj}
+    Note that $\Proj$ is not functorial, in the sense that a homomorphism of graded rings $S \to T$ does not induce a natural morphism $\Proj(T) \to \Proj(S)$ (like $\Spec$ does).
+    Namely, given $\alpha: S \to T$, we might want to consider
+    \begin{equation*}
+        \Proj(T) \to \Proj(S), \quad \p \mapsto \alpha^{-1}(\p)
+    \end{equation*}
+    However, in general this is not well-defined, as $\alpha^{-1}(\p)$ might contain $S_+$.
+
+    If we further require the map $\alpha: S \to T$ to fulfill $T_+ \subseteq \alpha(S_+)T$, then this works out and we get a morphism
+    \begin{align*}
+        \Proj(\alpha): \Proj(T) &\to \Proj(S), \quad \p \mapsto \alpha^{-1}(\p), \\
+        \Proj(\alpha)^\#_{D_f}: \O_{\Proj(S)}(D_f) &\to \O_{\Proj(T)}(D_{\alpha(f)}), \quad \frac x y \mapsto \frac {\alpha(x)} {\alpha(y)}
+    \end{align*}
+    Note that this is indeed a well-defined morphism, as for $\p \in \Proj(T)$ there is some $f \in T_+ \setminus \p$ and by assumption, have $g \in S_+, t \in T$ with $\alpha(g)t = f$.
+    Now $g \notin \alpha^{-1}(\p)$, as $g \in \alpha^{-1}(\p)$ would imply $\alpha(g) \in \p$, thus $f = t\alpha(g) \in \p$.
+
+    In particular, any ring homomorphism $R \to S$ induces a canonical morphism $\P_S^n \to \P_R^n$ of schemes, since the induced ring homomorphism $R[x_0, ..., x_n] \to S[x_0, ..., x_n]$ satisfies the above additional condition.
+\end{remark}
+\begin{lemma}
+    Let $S, T$ be $R$-algebras via $f: R \to S$ and $g: R \to T$.
+    Let $\p \leq S, \q \leq T$ be prime ideals with $\b = f^{-1}(\p) = g^{-1}(\q)$.
+    Then have the canonical map
+    \begin{equation*}
+        S \otimes_R T \to \Frac(S/\p) \otimes_R \Frac(T/\q) = \Frac{S/\p} \otimes_{R/\b} \Frac(T/\q)
+    \end{equation*}
+    Then the preimage $\a \leq S \otimes_R T$ of a prime ideal in $\Frac{S/\p} \otimes_{R/\b} \Frac(T/\q)$ is a prime ideal such that
+    \begin{equation*}
+        \iota_S^{-1}(\a) = \p \quad \text{and} \quad \iota_T^{-1}(\a) = \q
+    \end{equation*}
+    where $\iota_S: S \to S \otimes_R T$ and $\iota_T: T \to S \otimes_R T$ are the tensor maps.
+\end{lemma}
+\begin{lemma}
+    Let $R \to S$ be a ring homomorphism.
+    Then the base change of $\P_R^n$ is
+    \begin{equation*}
+        \P_R^n \times_{\Spec(R)} \Spec(S) = \P_S^n
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    Consider the canonical map $\alpha: R[x_0, ..., x_n] \to S[x_0, ..., x_n]$ induced by $R \to S$.
+    Note that
+    \begin{equation*}
+        S \otimes_R (R[x_0, ..., x_n]_f)_0 \cong (S[x_0, ..., x_n]_{\alpha(f)})_0 \quad \text{via} \quad \iota_f: s \otimes \frac r {f^n} \mapsto \frac {s\alpha(r)} {\alpha(f)^n}
+    \end{equation*}
+    for all homogeneous $f \in R[x_0, ..., x_n]$.
+    By Lemma~\ref{prop:Df_affine}, we see that $D_f$ for $f \in S[x_0, ..., x_n]$ homogeneous form an affine open cover of $\P_S^n$.
+    Furthermore, we have a cover by affine opens $D_f \times_{\Spec(R)} \Spec(S)$ of $\P_R^n \times_{\Spec(R)} \Spec(S)$ for $f \in R[x_0, ..., x_n]$ homogeneous.
+    Together, we see that it suffices to show that the isomorphisms (induced by $\iota_f$)
+    \begin{equation*}
+        \phi_f: D_{\alpha(f)} = \Spec((S[x_0, ..., x_n]_{\alpha(f)})_0) \to D_f \times_{\Spec(R)} \Spec(S)
+    \end{equation*}
+    glue to an isomorphism $\Proj(S[x_0, ..., x_n]) \to \P_R^n \times_{\Spec(R)} \Spec(S)$.
+    By the gluing lemma, it suffices that the compatibility conditions are satisfied, i.e. that for all $f, g \in R[x_0, ..., x_n]$ homogeneous the diagram
+    \begin{center}
+        \begin{tikzpicture}
+            \node (Sfg) at (0, 0) {$D_{\alpha(f)} \cap D_{\alpha(g)} = D_{\alpha(fg)}$};
+            \node (Sf) at (3, 1) {$D_{\alpha(f)}$};
+            \node (Sg) at (3, -1) {$D_{\alpha(g)}$};
+            \node (f) at (7, 1) {$D_f \times_{\Spec(R)} \Spec(S)$};
+            \node (g) at (7, -1) {$D_g \times_{\Spec(R)} \Spec(S)$};
+            \node (all) at (10, 0) {$\P_R^n \times_{\Spec(R)} \Spec(S)$};
+
+            \draw [->] (Sfg) -- (Sf);
+            \draw [->] (Sfg) -- (Sg);
+            \draw [->] (Sf) -- (f) node [midway, above] {$\phi_f$};
+            \draw [->] (Sg) -- (g) node [midway, above] {$\phi_g$};
+            \draw [->] (f) -- (all);
+            \draw [->] (g) -- (all);
+        \end{tikzpicture}
+    \end{center}
+    commutes.
+
+    For a prime ideal $\p \in D_{\alpha(fg)}$ have that
+    \begin{equation*}
+        \phi_f(\p) = \iota_f^{-1}(\p \cap (S[x_0, ..., x_n]_f)_0) \in D_f \times_{\Spec(R)} \Spec(S)
+    \end{equation*}
+    and so $g \notin \phi_f(\p)$, i.e. $\phi_f(\p) \in D_{fg} \times_{\Spec(R)} \Spec(S)$.
+    Hence, we have that both restrictions
+    \begin{equation*}
+        \restr{\phi_f}{D_{\alpha(fg)}}, \ \restr{\phi_g}{D_{\alpha(fg)}}: D_{\alpha(fg)} \to D_{fg} \times_{\Spec(R)} \Spec(S)
+    \end{equation*}
+    map into $D_{fg} \times_{\Spec(R)} \Spec(S)$.
+    Now note that the diagram
+    \begin{center}
+        \begin{tikzpicture}
+            \node (Rf) at (0, 0) {$S \otimes_R (R[x_0, ..., x_n]_f)_0$};
+            \node (Rg) at (-3, -2) {$S \otimes_R (R[x_0, ..., x_n]_g)_0$};
+            \node (Rfg) at (0, -4) {$S \otimes_R (R[x_0, ..., x_n]_{fg})_0$};
+
+            \node (Sf) at (5, 0) {$(S[x_0, ..., x_n]_f)_0$};
+            \node (Sg) at (8, -2) {$(S[x_0, ..., x_n]_g)_0$};
+            \node (Sfg) at (5, -4) {$(S[x_0, ..., x_n]_{fg})_0$};
+
+            \draw [->] (Rf) -- (Sf) node [midway, above] {$\iota_f$};
+            \draw [->] (Rg) -- (Sg) node [midway, above] {$\iota_g$};
+            \draw [->] (Rfg) -- (Sfg) node [midway, above] {$\iota_{fg}$};
+
+            \draw [->] (Rf) -- (Rfg);
+            \draw [->] (Rg) -- (Rfg);
+            \draw [->] (Sf) -- (Sfg);
+            \draw [->] (Sg) -- (Sfg);
+        \end{tikzpicture}
+    \end{center}
+    commutes, and so the restrictions of $\phi_f$ resp. $\phi_g$ to $D_{\alpha(fg)}$ are both induced by the homomorphism $\iota_{fg}$, hence they are equal.
+    The claim follows.
+\end{proof}
 \printbibliography

### 2022-03-25 Schemes/submission.tex
Projective space is universally closed proven

@@
 \newcommand{\im}{\mathrm{im}}
+\newcommand{\cont}{\mathrm{cont}}
 \renewcommand{\O}{\mathcal{O}}
@@
         &f: \Proj(R[x_0, ..., x_n]) \to \Spec(R), \quad \p \mapsto \p \cap R \\
-        &f^\#_{D_f}: R_f \to \O_{\Proj(S)}(D_f) = (R[x_0, ..., x_n]_f)_0, \quad r \mapsto r
+        &f^\#_{D_f}: R_f \to \O_{\Proj(R[x_0, ..., x_n])}(D_f) = (R[x_0, ..., x_n]_f)_0 = R_f, \quad r \mapsto r
     \end{align*}
@@
 \begin{prop}
+    \label{prop:p_quasi_compact}
     $\P_R^n \to \Spec(R)$ is of finite type.
@@
 \end{proof}
+\cite[66.9.5.]{stacks}
 \begin{corollary}
+    \label{prop:universally_closed_affines}
     A scheme $X$ over $\Spec(R)$ is universally closed, if for all ring homomorphisms $R \to S$ have the following:
-    The map $X \times_{\Spec(R)} \Spec(S) \to \Spec(S)$ that makes the diagram
+    The base change map $X \times_{\Spec(R)} \Spec(S) \to \Spec(S)$, i.e. the map that makes the diagram
     \begin{center}
@@
     \end{center}
-    is closed.
+    commute, is closed.
 \end{corollary}
@@
 \begin{lemma}
-    Let $S, T$ be $R$-algebras via $f: R \to S$ and $g: R \to T$.
-    Let $\p \leq S, \q \leq T$ be prime ideals with $\b = f^{-1}(\p) = g^{-1}(\q)$.
-    Then have the canonical map
-    \begin{equation*}
-        S \otimes_R T \to \Frac(S/\p) \otimes_R \Frac(T/\q) = \Frac{S/\p} \otimes_{R/\b} \Frac(T/\q)
-    \end{equation*}
-    Then the preimage $\a \leq S \otimes_R T$ of a prime ideal in $\Frac{S/\p} \otimes_{R/\b} \Frac(T/\q)$ is a prime ideal such that
-    \begin{equation*}
-        \iota_S^{-1}(\a) = \p \quad \text{and} \quad \iota_T^{-1}(\a) = \q
-    \end{equation*}
-    where $\iota_S: S \to S \otimes_R T$ and $\iota_T: T \to S \otimes_R T$ are the tensor maps.
-\end{lemma}
-\begin{lemma}
+    \label{prop:projective_space_base_change}
     Let $R \to S$ be a ring homomorphism.
@@
     \begin{equation*}
-        \P_R^n \times_{\Spec(R)} \Spec(S) = \P_S^n
+        \P_R^n \times_{\Spec(R)} \Spec(S) \cong \P_S^n
     \end{equation*}
+    as schemes over $\Spec(S)$.
 \end{lemma}
@@
         \begin{tikzpicture}
-            \node (Rf) at (0, 0) {$S \otimes_R (R[x_0, ..., x_n]_f)_0$};
-            \node (Rg) at (-3, -2) {$S \otimes_R (R[x_0, ..., x_n]_g)_0$};
-            \node (Rfg) at (0, -4) {$S \otimes_R (R[x_0, ..., x_n]_{fg})_0$};
+            \node (Rf) at (-3, 0) {$S \otimes_R (R[x_0, ..., x_n]_f)_0$};
+            \node (Rg) at (0, -2) {$S \otimes_R (R[x_0, ..., x_n]_g)_0$};
+            \node (Rfg) at (-3, -4) {$S \otimes_R (R[x_0, ..., x_n]_{fg})_0$};
 
-            \node (Sf) at (5, 0) {$(S[x_0, ..., x_n]_f)_0$};
-            \node (Sg) at (8, -2) {$(S[x_0, ..., x_n]_g)_0$};
-            \node (Sfg) at (5, -4) {$(S[x_0, ..., x_n]_{fg})_0$};
+            \node (Sf) at (8, 0) {$(S[x_0, ..., x_n]_f)_0$};
+            \node (Sg) at (5, -2) {$(S[x_0, ..., x_n]_g)_0$};
+            \node (Sfg) at (8, -4) {$(S[x_0, ..., x_n]_{fg})_0$};
 
@@
 \end{proof}
+The next lemma is directly from \cite[II.4.5]{hartshorne}.
+\begin{lemma}
+    \label{prop:im_closed_iff_stable_specialization}
+    Let $f: X \to Y$ be a quasi-compact morphism.
+    Then $f(|X|)$ is closed if and only if it is stable under specialization.
+\end{lemma}
+\begin{lemma}
+    \label{prop:adding_coeff_ideal_does_not_introduce_irrelevant_ideal}
+    Let $\p \leq R[x_0, ..., x_n]$ be a homogeneous prime ideal with $R[x_0, ..., x_n]_+ \not\subseteq \p$.
+    Further let $\q \leq R$ be a prime ideal such that $\p \cap R \subseteq \q$.
+    Then there some $i$ such that no $\alpha x_i^m$ is in $\b := \p + \q R[x_0, ..., x_n]$, for any $\alpha \in R \setminus \b$ and any $m \in \N$.
+\end{lemma}
+\begin{proof}
+    Assume there is $m \in \N$ such that $\alpha_i x_i^m \in \b$ for all $i$ and some $\alpha_i \in \b \setminus R$.
+    Since $\b \cap R = \q$ is prime, have that $\alpha := \prod_i \alpha_i \notin \b$.
+    Further we have that $\alpha x_i^m \in \b$ for all $i$.
+
+    Consider now the vector $(w_i)_{i < N}$ containing all monomials of degree $(n + 1)m$.
+    By assumption, all $\alpha w_i \in \b$.
+    Since $\p$ is homogeneous, observe that now there are $r_{ij} \in \q$ such that
+    \begin{equation*}
+        \alpha w_i - \sum_{j < N} r_{ij} w_j \in \p
+    \end{equation*}
+    Working modulo $\p$, we see that $A w = \alpha w$ where $A \in (\b/\p)^{N \times N}$.
+
+    Now observe that $\alpha \notin \b/\p$ since $\alpha \notin \b$.
+    Hence there exists a prime ideal in $R/\p$ containing $\b/\p$ and not containing $\alpha$.
+    Localizing at that prime ideal gives a local ring $S$ with maximal ideal $\mathfrak{l}$.
+    Now assume that $w \in S^n$ and $A/\alpha \in \mathfrak{l}^{n \times n}$.
+    Note that we still have $(A/\alpha) w = w$.
+
+    wlog $S$ is noetherian, otherwise continue with the ring
+    \begin{equation*}
+        \tilde{S} := \begin{cases}
+            \Z[A/\alpha, x] & \text{if $\mathrm{char}(S) = 0$} \\
+            (\Z/\mathrm{char}(R)\Z)[A/\alpha, x] & \text{if $\mathrm{char}(S) \neq 0$}
+        \end{cases}
+    \end{equation*}
+    generated by the coefficients of $A/\alpha$ and $w$ (this is noetherian, as it is a quotient of a polynomial ring in finitely many variables).
+
+    Now equip $S_{\mathfrak{l}}$ with the $\mathfrak{l}$-adic topology.
+    Note that $S$ is noetherian and local, thus the Krull intersection theorem shows that the $\mathfrak{l}$-adic topology is Hausdorff and we find
+    \begin{equation*}
+        w = \lim_{i \to \infty} w = \lim_{i \to \infty} \frac {A^i} {\alpha^i} w = \Bigl( \lim_{i \to \infty} \frac {A^i} {\alpha^i} \Bigr) w = 0 w = 0
+    \end{equation*}
+    since $(A/\alpha)^i$ has coefficients in $\mathfrak{l}^i$, thus converges to $0$ as $i \to \infty$.
+
+    Thus $w \equiv 0 \mod \p$ and so $x_i^N \equiv 0 \mod \p$, i.e. $x_i^N \in \p$ for all $i$.
+    However, since $\p$ is prime, this implies $R[x_0, ..., x_n]_+ = \langle x_0, ..., x_n \rangle \subseteq \p$, contradicting the assumption. 
+\end{proof}
+\begin{prop}
+    \label{prop:projective_structure_morphism_closed}
+    The morphism $\P_R^n \to \Spec(R)$ is closed.
+\end{prop}
+\begin{proof}
+    Denote $\P_R^n \to \Spec(R)$ by $\phi$.
+    Consider a closed set $\V(\a) = \P_R^n \setminus D_\a$ given by a homogeneous ideal $\a \leq R[x_0, ..., x_n]$.
+    By Lemma~\ref{prop:im_closed_iff_stable_specialization}, it suffices to show that $\phi(\V(\a))$ is closed under specialization (note that $\P_R^n \to \Spec(R)$ is quasi-compact, e.g.
+by Proposition~\ref{prop:p_quasi_compact}).
+
+    Consider $\q \in \phi(\V(\a)) \subseteq \Spec(R)$ and a prime ideal $\q'$ that specializes $\q$, i.e. $\q' \supseteq \q$.
+    Then there is a $\p \in \V(\a)$ with $\p \cap R = \q$, in particular $\a \subseteq \p$.
+    We want to show that $\q' \in \phi(\V(\a))$.
+
+    Note that by Lemma~\ref{prop:adding_coeff_ideal_does_not_introduce_irrelevant_ideal}, there is $i$ such that the multiplicative set
+    \begin{equation*}
+        T := \{ \alpha x_i^m \ | \ \alpha \in R \setminus \q', \ m \in \N \}
+    \end{equation*}
+    has empty intersection with the ideal $\b := \p + \q' R[x_0, ..., x_n]$.
+
+    Hence, the ring $T^{-1}(R[x_0, ..., x_n]/\b)$ is nonzero, thus has a prime.
+    Taking its preimage under
+    \begin{equation*}
+        R[x_0, ..., x_n] \to R[x_0, ..., x_n]/\b \to T^{-1}(R[x_0, ..., x_n]/\b)
+    \end{equation*}
+    yields a prime ideal $\p'$ such that $x_i \notin \p'$ and $\b \subseteq \p'$.
+    Clearly have that $\q' \subseteq \p'$ and since $\p' \cap T = \emptyset$, find that $\p' \cap R = \q'$.
+    By Lemma~\ref{prop:homogeneous_part_prime}, assume wlog that $\p'$ is homogeneous.
+    Now have a homogeneous prime ideal $\p'$ with $\a \subseteq \p \subseteq \p'$, i.e. $\p' \in \V(\a)$ and $\phi(\p') = \p' \cap R = \q'$.
+    Thus $\q \in \phi(\V(\a))$ and the claim follows.
+\end{proof}
+\begin{corollary}
+    The morphism $\P_R^n \to \Spec(R)$ is universally closed.
+\end{corollary}
+\begin{proof}
+    Use Lemma~\ref{prop:universally_closed_affines}, so consider an affine base change $f_{\Spec(S)}: \P_R^n \times_{\Spec(R)} \Spec(S) \to \Spec(S)$.
+    By Lemma~\ref{prop:projective_space_base_change}, have that $\P_R^n \times_{\Spec(R)} \Spec(S) \cong \P_S^n$ as schemes over $S$, hence $f_{\Spec(S)}$ is isomorphic to $\P_S^n \to \Spec(S)$.
+    This morphism is closed by Proposition~\ref{prop:projective_structure_morphism_closed} and the claim follows.
+\end{proof}
+\begin{corollary}
+    Projective space $\P_R^n$ over $\Spec(R)$ is proper.
+\end{corollary}
+\begin{corollary}
+    Let $k$ be an algebraically closed field.
+    Then projective space $\P_k^n$ over $\Spec(k)$ is a complete variety.
+\end{corollary}
+
+\section{Valuative criterion of properness}
+\begin{prop}
+    Let $X$ be noetherian and $f: X \to Y$ a morphism of finite type.
+    The following are equivalent
+    \begin{itemize}
+        \item $f$ is proper
+        \item For every valuation ring $R$ with field of fractions $K = \Frac(R)$ and all morphisms $\Spec(R) \to Y$, $\Spec(K) \to X$ that make the diagram
+        \begin{center}
+            \begin{tikzpicture}
+                \node (K) at (0, 0) {$\Spec(K)$};
+                \node (R) at (0, -2) {$\Spec(R)$};
+                \node (X) at (3, 0) {$X$};
+                \node (Y) at (3, -2) {$Y$};
+
+                \draw [->] (K) -- (R);
+                \draw [->] (K) -- (X);
+                \draw [->] (R) -- (Y);
+                \draw [->] (X) -- (Y) node [midway, right] {$f$};
+            \end{tikzpicture}
+        \end{center}
+        commute, there exists a unique compatible morphism $\Spec(R) \to X$.
+    \end{itemize}
+\end{prop}
 \printbibliography

### 2022-03-26 Schemes/submission.tex
Fixed subtle bug in the covering trick

@@
 \newcommand{\Q}{\mathbb{Q}}
-\newcommand{\I}{\mathbb{I}}
-\newcommand{\V}{\mathbb{V}}
+\newcommand{\V}[1]{\mathrm{V}_+(#1)}
+\newcommand{\D}[1]{\mathrm{D}_+(#1)}
 \newcommand{\A}{\mathbb{A}}
@@
 
+First of all, we will start with a reminder on graded rings, as they are the fundamental object used in the $\Proj$-construction.
 \begin{definition}
-    A \emph{graded ring} $S$ is a ring $S$ with a decomposition $S = \oplus_{d \in \Z} S_d$ into groups $S_i \subseteq S$ (w.r.t.
+    A \emph{graded ring} $S$ is a ring $S$ with a decomposition $S = \oplus_{d \in \N} S_d$ into groups $S_i \subseteq S$ (w.r.t.
 addition in $S$) such that $S_i S_j \subseteq S_{i + j}$ for all $i, j \in \Z$.
-    If all $S_d = \{ 0 \}$ for $d < 0$, call $S$ \emph{naturally graded ring}.
     Write further $S_+ := \sum_{d \neq 0} S_d$.
@@
 \end{definition}
+From now on let $S$ be a graded ring.
 \begin{definition}
-    For a naturally graded ring $S$, define the set
+    Define the set
     \begin{equation*}
@@
     \begin{equation*}
-        D_{\a} := \{ \p \in \Proj(S) \ | \ \a \not\subseteq \p \}
+        \D{\a} := \{ \p \in \Proj(S) \ | \ \a \not\subseteq \p \}
     \end{equation*}
@@
 \end{definition}
-From now on let $S$ be a naturally graded ring.
 \begin{prop}
-    The above definition is well-defined, i.e. the sets $D_\a$ indeed form a topology on $\Proj(S)$.
+    The above definition is well-defined, i.e. the sets $\D{\a}$ indeed form a topology on $\Proj(S)$.
 \end{prop}
 \begin{proof}
-    Clearly $\Proj(S) = D_{\langle 1 \rangle}$ and $\emptyset = D_{\langle 0 \rangle}$ are open.
-    Furthermore, for open sets $D_\a$ and $D_\b$, have that
+    Clearly $\Proj(S) = \D{\langle 1 \rangle}$ and $\emptyset = \D{\langle 0 \rangle}$ are open.
+    Furthermore, for open sets $\D{\a}$ and $\D{\b}$, have that
     \begin{equation*}
-        D_\a \cap D_\b = \{ \p \in \Proj(S) \ | \ \a, \b \not\subseteq \p \} = \{ \p \in \Proj(S) \ | \ \a\b \not\subseteq \p \} = D_{\a\b}
+        \D{\a} \cap \D{\b} = \{ \p \in \Proj(S) \ | \ \a, \b \not\subseteq \p \} = \{ \p \in \Proj(S) \ | \ \a\b \not\subseteq \p \} = \D{\a\b}
     \end{equation*}
@@
     However, then $fg \notin \p$ as $\p$ is prime.
-    Obviously $\a\b$ is homogeneous, and so $D_\a \cap D_\b$ is open.
+    Obviously $\a\b$ is homogeneous, and so $\D{\a} \cap \D{\b}$ is open.
 
@@
     \begin{align*}
-        \bigcup_{\a \in \mathcal{A}} D_\a =& \{ \p \in \Proj(S) \ | \ \exists \a \in \mathcal{A}:\ \a \not\subseteq \p \} = \{ \p \in \Proj(S) \ | \ \exists \a \in \mathcal{A} \exists f \in \a:\ f \notin \p \} \\
-        =& \Bigl\{ \p \in \Proj(S) \ \Bigm| \ \exists f \in \sum_{\a \in \mathcal{A}} \a:\ f \notin \p \Bigr\} = D_{\b} \quad \text{for $\b = \sum_{\a \in \mathcal{A}} \a$}
+        \bigcup_{\a \in \mathcal{A}} \D{\a} =& \{ \p \in \Proj(S) \ | \ \exists \a \in \mathcal{A}:\ \a \not\subseteq \p \} = \{ \p \in \Proj(S) \ | \ \exists \a \in \mathcal{A} \exists f \in \a:\ f \notin \p \} \\
+        =& \Bigl\{ \p \in \Proj(S) \ \Bigm| \ \exists f \in \sum_{\a \in \mathcal{A}} \a:\ f \notin \p \Bigr\} = \D{\b} \quad \text{for $\b = \sum_{\a \in \mathcal{A}} \a$}
     \end{align*}
-    Clearly $\b$ is again homogeneous, and so $\bigcup_{\a \in \mathcal{A}} D_\a$ is open.
+    Clearly $\b$ is again homogeneous, and so $\bigcup_{\a \in \mathcal{A}} \D{\a}$ is open.
+\end{proof}
+As opposed to Hartshorne \cite{hartshorne}, we follow an approach similar to the construction of $\O_{\Spec(R)}$ to construct a sheaf of rings on $\Proj(S)$.
+In particular, we will define $\O_{\Proj(S)}$ on a basis of the topology, and extend it to a sheaf.
+This will be somewhat more tedious, but gives a nice idea of how $\O_{\Proj(S)}(U)$ looks like.
+\begin{lemma}
+    \label{prop:Splus_invariance}
+    For a homogeneous ideal $\a$ have $\D{\a} = \D{\a S_+}$.
+\end{lemma}
+\begin{proof}
+    The inclusion $\supseteq$ is clear, as $\a S_+ \subseteq \a$.
+    So assume there is a $\p \in \D{\a}$.
+    Since $\p \in \Proj(S)$ find $S_+ \not\subseteq \p$ and by assumption, $\a \not\subseteq \p$.
+    Thus there are $s \in S_+$ and $a \in \a$ with $a, s \notin \p$.
+    Since $\p$ is prime, it follows that $as \notin \p$ and so $\a S_+ \not\subseteq \p$.
 \end{proof}
 \begin{prop}
-    The sets $D_f := D_{\langle f \rangle}$ for homogeneous $f \in S$ form a basis of the topology on $\Proj(S)$.
+    \label{prop:basis_topology}
+    The sets $\D{f} := \D{\langle f \rangle}$ for homogeneous $f \in S_+$ form a basis of the topology on $\Proj(S)$.
 \end{prop}
 \begin{proof}
-    Clearly $\langle f \rangle$ is a homogenous ideal, so $D_f$ is open.
-    For any homogeneous ideal $\a = \langle f_i \ | \ i \in I \rangle$ with $f_i \in S$ homogeneous have
+    Clearly $\langle f \rangle$ is a homogenous ideal, so $\D{f}$ is open.
+    For any homogeneous ideal $\a = \langle f_i \ | \ i \in I \rangle$ with $f_i \in S$ homogeneous have that $\D{\a} = \D{\a S_+}$ by Lemma~\ref{prop:Splus_invariance}, so we can assume wlog that all $f_i \in S_+$.
+    Now have
     \begin{equation*}
-        D_\a = \bigcup_{i \in I} D_{f_i}
+        \D{\a} = \bigcup_{i \in I} \D{f_i}
     \end{equation*}
     as $\a \not\subseteq \p$ implies there is some $g = \sum_{i \in I} g_i f_i \notin \p$, with $g_i \in S$.
-    Hence, at least one $g_j f_j \notin \p$ and so $f_j \notin \p$, thus $\p \in D_{f_j}$.
-    It follows that the $D_f$ generate the topology on $\Proj(S)$, so it is left to show that they are a basis.
+    Hence, at least one $g_j f_j \notin \p$ and so $f_j \notin \p$, thus $\p \in \D{f_j}$.
+    It follows that the $\D{f}$ generate the topology on $\Proj(S)$, so it is left to show that they are a basis.
 
-    Consider $\p \in D_f \cap D_g$, so $f, g \notin \p$.
-    Since $\p$ is prime, it follows that $fg \notin \p$ and so $D_{fg} \subseteq D_f \cap D_g$ is an open neighborhood of $\p$.
-\end{proof}
-\begin{lemma}
-    Let $S$ be a graded ring (not necessarily naturally graded) and $T \subseteq S$ a multiplicative set consisting of homogeneous elements. 
-    Then $T^{-1}S$ becomes a graded ring via
-    \begin{equation*}
-        \left(T^{-1}S\right)_d = \Bigl\{ \frac g h \in T^{-1}S \ \Bigm| \ \text{$g$ homogeneous with $\deg(g) - \deg(h) = d$} \Bigr\}
-    \end{equation*}
-\end{lemma}
-\begin{proof}
-    Clearly $(T^{-1}S)_i (T^{-1}S)_j \subseteq (T^{-1}S)_{i + j}$.
-    To see that $(T^{-1}S)_d$ is a subgroup of $S$, consider $g/f, l/h \in (T^{-1}S)_d$.
-    Now have
-    \begin{equation*}
-        \frac g f + \frac l h = \frac {gh + lf} {hf}
-    \end{equation*}
-    and by assumption, find $\deg(gh) = \deg(g) - \deg(h) = d + \deg(f) - d + \deg(l) = \deg(lf)$.
-    So $gh + lf$ is homogeneous and we have
-    \begin{equation*}
-        \deg(gh + lf) - \deg(fh) = \deg(f) + \deg(l) - \deg(f) - \deg(h) = \deg(l) - \deg(h) = d
-    \end{equation*}
-    Thus $g/f + l/h \in (T^{-1}S)_d$.
-
-    Finally, we show that $(T^{-1}S)_n \cap (T^{-1}S)_m = \{ 0 \}$ for $i \neq j$.
-    Assume there is $g/f = l/h \in (T^{-1}S)_n \cap (T^{-1}S)_m$ with $\deg(g) - \deg(f) = n$ and $\deg(l) - \deg(h) = m$.
-    Then there exists $t \in T$ such that
-    \begin{align*}
-        0 = t(gh - lf) =& tgh - tlf \quad \text{with}\ tgh \in S_{\deg(t) + \deg(g) + \deg(h)} \\
-        &\text{and}\ tlf \in S_{\deg(t) + \deg(l) + \deg(f)} = S_{\deg(t) + \deg(g) + \deg(h) + (m - n)}
-    \end{align*}
-    If $n \neq m$, then $S_{\deg(t) + \deg(g) + \deg(h) + (m - n)} \cap S_{\deg(t) + \deg(g) + \deg(h)} = \{ 0 \}$ and so $tgh = tlf = 0$.
-    Thus $th(g - 0) = 0$ and so $g/f = 0/1 = 0$.
-    Thus $(T^{-1}S)_m \cap (T^{-1}S)_n = \{ 0 \}$.
+    Consider $\p \in \D{f} \cap \D{g}$, so $f, g \notin \p$.
+    Since $\p$ is prime, it follows that $fg \notin \p$ and so $\D{fg} \subseteq \D{f} \cap \D{g}$ is an open neighborhood of $\p$.
 \end{proof}
@@
 \end{proof}
-\begin{lemma}
-    If $D_g \subseteq D_f$ then there is a homogeneous $h \in S$ such that $g^n = fh$ for some $n \in \N$.
+\begin{lemma}[``Covering Trick'']
+    \label{prop:covering_trick}
+    Let $f, f_i \in S_+$ be homogeneous.
+    Then $\D{f} \subseteq \bigcup_i \D{f_i}$ if and only if $f^n \in \langle f_i \ | \ i \rangle$ for some $n \in \N$
 \end{lemma}
 \begin{proof}
-    Assume not, then $f$ is not a unit in $S_g$.
-    Hence, there is a maximal ideal $\m \leq S_g$ such that $f \in \m$.
-    Now let $\p$ be the preimage of $\m$ under the localization map $S \to S_g$.
-    Since $\m$ is maximal, we see that $\p$ is prime.
-
-    Now apply Lemma~\ref{prop:homogeneous_part_prime} and see that also
-    \begin{equation*}
-        \p' = \langle f \in \p \ | \ \text{$f$ homogeneous} \rangle \subseteq \p
-    \end{equation*}
-    is prime.
-    Furthermore, $g \notin \p$ and so $g \notin \p'$.
-    wlog we have that $g \in S_+$, so $S_+ \not\subseteq \p'$.
-    Since now $\p'$ is a homogeneous prime ideal, it follows that $\p' \in \Proj(S)$.
-
-    Finally, observe that $f \in \p'$ as $f \in \p$ and $f$ is homogeneous.
-    Hence, we have that $\p' \notin D_f$ and $\p' \in D_g$, which contradicts the assumption that $D_g \subseteq D_f$.
+    The direction $\Leftarrow$ is clear.
+    So assume $\D{f} \subseteq \bigcup_i \D{f_i}$.
+    If no $f^n$ is in $\a := \langle f_i \ | \ i \rangle$, then $f$ is not nilpotent in $S/\a$ and so $S/\a$ is not the zero ring.
+    Hence, $(S/\a)_f$ has a prime ideal, and its preimage under $S \to S/\a \to (S/\a)_f$ yields a prime ideal $\p'$ containing $\a$ and not containing $f$.
+    Since $f \in S_+$ note that $S_+ \not\subseteq \p'$ and as both $f$ and $\a$ are homogeneous, Lemma~\ref{prop:homogeneous_part_prime} yields now that $\langle g \in \p' \ | \ \text{$g$ homogeneous} \rangle$ is a prime ideal in $\D{f}$ but not in $\bigcup_i \D{f_i}$, contradicting the assumption.
+\end{proof}
+\begin{corollary}
+    \label{prop:basic_set_inclusion_divisibility}
+    If $\D{g} \subseteq \D{f}$ with $f, g \in S_+$, then there is a homogeneous $h \in S$ such that $g^n = fh$ for some $n \in \N$.
+\end{corollary}
+\begin{proof}
+    By assumption, $\D{f}$ covers $\D{g}$, thus by the Covering Trick (Lemma~\ref{prop:covering_trick}), observe that $g^n \in \langle f \rangle$ for some $n \in \N$.
+    The claim follows.
 \end{proof}
@@
 \begin{prop}
-    Let $B = \{ D_f \ | \ \text{$f \in S$ homogeneous}\}$.
-    The functor
+    Let $B = \{ \D{f} \ | \ \text{$f \in S_+$ homogeneous}\}$.
+    The functor\footnote{The map on arrows is well-defined by Corollary~\ref{prop:basic_set_inclusion_divisibility}.}
     \begin{align*}
-        \mathcal{F}: \restr{\Top(\Proj(S))}{B} \to \Ring, \quad D_f &\mapsto (S_f)_0 \\
-        (D_{fg} \subseteq D_f) &\mapsto \Bigl( \restr{\cdot}{D_{fg}}: \frac s {f^n} \mapsto \frac {sg^n} {(fg)^n} \Bigr)
+        \mathcal{F}: \restr{\Top(\Proj(S))}{B} \to \Ring, \quad \D{f} &\mapsto (S_f)_0 \\
+        (\D{fg} \subseteq \D{f}) &\mapsto \Bigl( \restr{\cdot}{\D{fg}}: \frac s {f^n} \mapsto \frac {sg^n} {(fg)^n} \Bigr)
     \end{align*}
@@
 
-    Let $D_f = \bigcup_{i \in I} D_{g_if}$ be a cover and $s_i \in \mathcal{F}(D_{g_if})$ such that
+    Let $\D{f} = \bigcup_{i \in I} \D{g_if}$ be a cover and $s_i \in \mathcal{F}(\D{g_if})$ such that
     \begin{equation*}
-        \forall x \in D_{g_if} \cap D_{g_jf} \ \exists V \in B: \ V \subseteq D_{g_if} \cap D_{g_jf}, \ x \in V, \ \frac {s_i} 1 = \frac {s_j} 1 \in \mathcal{F}(V)
+        \forall x \in \D{g_if} \cap \D{g_jf} \ \exists V \in B: \ V \subseteq \D{g_if} \cap \D{g_jf}, \ x \in V, \ \frac {s_i} 1 = \frac {s_j} 1 \in \mathcal{F}(V)
     \end{equation*}
-    To show uniqueness, assume there are $\alpha/f^N, \beta/f^N \in D_f$ with
+
+    To show uniqueness, assume there are $\alpha/f^N, \beta/f^N \in \D{f}$ with
     \begin{equation*}
-        \restr{\frac {\alpha} {f^N}}{D_{g_if}} = \restr{\frac {\beta} {f^N}}{D_{g_if}} \quad \text{for all $i$}
+        \restr{\frac {\alpha} {f^N}}{\D{g_if}} = \restr{\frac {\beta} {f^N}}{\D{g_if}} \quad \text{for all $i$}
     \end{equation*}
@@
     \begin{equation*}
-        (fg_i)^{n_i}
+        (fg_i)^{n_i} (\alpha f^N + \beta f^N) = 0
     \end{equation*}
 
-    By assumption, have $h_i^{n_i}(\alpha - \beta) = 0$ for each $i$, and wlog there are only finitely many $i$.
-    Thus find $N = \max_i n_i \in \N$ and get that $h_i^N(\alpha - \beta) = 0$.
-    Since $\bigcup_i D_{h_i} = \Proj(S)$ it follows that $\bigcup_i D_{h_i^N} = \Proj(S)$ and so $1 \in \langle h_i^N \ | \ i \rangle$.
-    It follows that
+    wlog there are only finitely many $i$ (by the Covering Trick, Lemma~\ref{prop:covering_trick}).
+
+    wlog $N$ is sufficiently large (we can always increase $N$), and so $(fg_i)^N(\alpha - \beta) = 0$.
+
+    Since $\bigcup_i \D{(fg_i)^N} = \bigcup_i \D{fg_i} = \D{f}$ it follows that $f^n \in \langle (fg_i)^N \ | \ i \rangle$ for some $n \in \N$ (again the Covering Trick, Lemma~\ref{prop:covering_trick}).
+    Therefore we find
     \begin{equation*}
-        \alpha - \beta = 1(\alpha - \beta) \in \langle h_i^N \ | \ i \rangle (\alpha - \beta) = \langle h_i^N (\alpha - \beta) \ | \ i \rangle = \{ 0 \}
+        f^n(\alpha - \beta) \in \langle (fg_i)^N \ | \ i \rangle (\alpha - \beta) = \langle (fg_i)^N (\alpha - \beta) \ | \ i \rangle = \{ 0 \}
     \end{equation*}
-    and so $\alpha = \beta$.
+    and so $\alpha = \beta \in S_f$.
 
@@
     \begin{equation*}
-        \restr{s_i}{D_{fg_ig_j}} = \restr{s_i}{D_{fg_i} \cap D_{fg_j}} = \restr{s_j}{D_{fg_i} \cap D_{fg_j}} = \restr{s_j}{D_{fg_ig_j}}
+        \restr{s_i}{\D{fg_ig_j}} = \restr{s_i}{\D{fg_i} \cap \D{fg_j}} = \restr{s_j}{\D{fg_i} \cap \D{fg_j}} = \restr{s_j}{\D{fg_ig_j}}
     \end{equation*}
@@
     \begin{equation*}
-        (f^2g_ig_j)^N \left( s'_i (fg_j)^N - s'_j (fg_i)^N \right) = 0 \quad \text{as $\restr{s_i}{D_{fg_ig_j}} = \restr{s_j}{D_{fg_ig_j}}$}
+        (f^2g_ig_j)^N \left( s'_i (fg_j)^N - s'_j (fg_i)^N \right) = 0 \quad \text{as $\restr{s_i}{\D{fg_ig_j}} = \restr{s_j}{\D{fg_ig_j}}$}
     \end{equation*}
@@
     \end{equation*}
-    Now observe that $D_{b_i} = D_{fg_i}$ and so $f^m \in \langle b_i \ | \ i \rangle$ for some $m$.
-    Let $f^m = \sum_i r_i b_i$ and get
+    Now observe that $\D{b_i} = \D{fg_i}$ and so $f^n \in \langle b_i \ | \ i \rangle$ for some $n$ (once again the Covering Trick, Lemma~\ref{prop:covering_trick}).
+    Let $f^n = \sum_i r_i b_i$ and get
     \begin{equation*}
-        a_i f^m = \sum_l r_l b_l a_i = \sum_l r_l a_l b_i = b_i \sum_l r_l a_l
+        a_i f^n = \sum_l r_l b_l a_i = \sum_l r_l a_l b_i = b_i \sum_l r_l a_l
     \end{equation*}
     Note that $a_i, b_i, f$ are homogeneous, and so we can also choose $r_i$ to be homogeneous.
-    Then find that $0 = \deg(s_i) = \deg(a_i) - \deg(b_i) = \deg(\sum r_l a_l) - m\deg(f)$.
+    Then find that $0 = \deg(s_i) = \deg(a_i) - \deg(b_i) = \deg(\sum r_l a_l) - n\deg(f)$.
 
@@
     \begin{equation*}
-        s_i = s := \frac {\sum_l r_l a_l} {f^m} \in S_f
+        s_i = s := \frac {\sum_l r_l a_l} {fn} \in S_f
     \end{equation*}
-    and since $\deg(\sum r_l a_l) = m\deg(f)$ we find that $s \in (S_f)_0 = \mathcal{F}(D_f)$.
-    Clearly $\restr{s}{D_{fg_i}} = s_i$ and the claim follows.
+    and since $\deg(\sum r_l a_l) = n\deg(f)$ we find that $s \in (S_f)_0 = \mathcal{F}(\D{f})$.
+    Clearly $\restr{s}{\D{fg_i}} = s_i$ and the claim follows.
 \end{proof}
+Now we the B-sheaf extension theorem from the lecture (from Section 1.11) yields the following corollary.
 \begin{corollary}
-    Hence we can (uniquely) extend the B-sheaf $\mathcal{F}$ to a sheaf $\O_{\Proj(S)}$ on $\Proj(S)$.
+    The B-sheaf $\mathcal{F}$ can be (uniquely, up to isomorphism) extended to a sheaf $\O_{\Proj(S)}$ on $\Proj(S)$.
 \end{corollary}
@@
 
-    First, note that $1 \notin (T^{-1}S)_0$ as otherwise, there would be $f/g \in T^{-1}S, f \in \p$ with $t(f - g) = 0$ for some $t \in T$.
+    First, note that $1 \notin \m$ as otherwise, there would be $f/g \in T^{-1}S, f \in \p$ with $t(f - g) = 0$ for some $t \in T$.
     However then $tg = tf \in \p$, and so $g \in \p$ (as $t \notin \p$), contradicting $g \in T$.
@@
     \label{prop:Df_affine}
-    For $f \in S_+$ homogeneous have that $(D_f, \restr{\O_{\Proj(S)}}{D_f})$ is an affine scheme.
+    For $f \in S_+$ homogeneous have that $(\D{f}, \restr{\O_{\Proj(S)}}{\D{f}})$ is an affine scheme.
 \end{lemma}
@@
     \begin{equation*}
-        f: D_f \to \Spec(R), \quad \p \mapsto \p S_f \cap (S_f)_0
+        \phi: \D{f} \to \Spec(R), \quad \p \mapsto \p S_f \cap R
     \end{equation*}
-    Note that it is continuous, as the preimage of some basic open set $D_{g/f^n}$ is $D_{fg} \subseteq D_f$ open.
-    Furthermore, $f$ has the inverse
+    Note that it is continuous, as the preimage of some basic open set $D_{g/f^n}$ is $\D{fg} \subseteq \D{f}$ open.
+    Furthermore, have the map
     \begin{equation*}
-        f^{-1}: \Spec(R) \to D_f, \quad \p \mapsto \p S_f
+        \phi': \Spec(R) \to \D{f}, \quad \p \mapsto \p S_f \cap S
     \end{equation*}
-    which is also continuous, as the preimage of some basic open set $D_{fg}$ is $D_{g^n/f^m}$ where $n\deg(g) = m\deg(f)$.
-    Thus $f$ is a homeomorphism.
+    which is also continuous, as the preimage of some basic open set $\D{fg}$ is $D_{g^n/f^m}$ where $n\deg(g) = m\deg(f)$.
+    Note that $\phi \circ \phi' = \mathrm{id}_{\Spec(R)}$ because $\p \subseteq (\p S_f \cap S) S_f \cap R$ and
+    \begin{equation*}
+        (\p S_f \cap S) S_f \cap R \subseteq \p S_f \cap S_f \cap R = \p S_f \cap (S_f)_0 = \p
+    \end{equation*}
+    where the last equality holds, since $\p \leq (S_f)_0$ is homogeneous.
+
+    To see that $\phi' \circ \phi = \mathrm{id}_{\D{f}}$, it suffices now to show that $\phi$ is injective ($\phi$ has a right-inverse, hence it is then bijective, and the one-sided inverse $\phi'$ is already the inverse).
+    Let $\p, \q \leq S$ homogeneous primes with $f \notin \p, \q$.
+    Assume there is $g \in \p \setminus \q$.
+    Then
+    \begin{equation*}
+        g^{\deg(f)} \in \p S_f \setminus \q S_f  \ \Rightarrow \ \frac {g^{\deg(f)}} {f^{\deg(g)}} \in (\p S_f \setminus \q S_f) \cap R = (\p S_f \cap R) \setminus (\q S_f \cap R)
+    \end{equation*}
+    and so $\phi(\p) \neq \phi(\q)$. Thus $\phi$ is a homeomorphism.
 
@@
     \begin{equation*}
-        \eta: \O_{\Spec R} \Rightarrow f_*\Bigl( \restr{\O_{\Proj(S)}}{D_f} \Bigr)
+        \eta: \O_{\Spec R} \Rightarrow \phi_*\Bigl( \restr{\O_{\Proj(S)}}{\D{f}} \Bigr)
     \end{equation*}
@@
 \begin{definition}
-    For any ring $R$ and $n \in \N$, define the projective $n$-space as\footnote{Endow $R[x_0, ..., x_n]$ with the standard natural grading, i.e.
+    For any ring $R$ and $n \in \N$, define the \emph{projective $n$-space} as\footnote{Endow $R[x_0, ..., x_n]$ with the standard natural grading, i.e.
 $\deg(x_i) = 1$.
@@
         &f: \Proj(R[x_0, ..., x_n]) \to \Spec(R), \quad \p \mapsto \p \cap R \\
-        &f^\#_{D_f}: R_f \to \O_{\Proj(R[x_0, ..., x_n])}(D_f) = (R[x_0, ..., x_n]_f)_0 = R_f, \quad r \mapsto r
+        &f^\#_{D_f}: R_f \to \O_{\Proj(R[x_0, ..., x_n])}(\D{f}) = R_f[x_0, ..., x_n], \quad r \mapsto r
     \end{align*}
@@
 For this section, let $R$ be a ring and $n \in \N$.
+
+First, we will study the property of being separated.
 \begin{prop}
-    Projective $n$-space $\P_R^n \to \Spec(R)$ over $\Spec(R)$ is separated.
+    The morphism $\P_R^n \to \Spec(R)$ is separated.
 \end{prop}
 \begin{proof}
-    By Lemma~\ref{prop:Df_affine} we find a cover $\Proj(S) = \bigcup_i D_{x_i}$ of affine opens.
-    We use the characterization from the lecture and show that $D_{x_i} \cap D_{x_j}$ is an affine open and the canonical multiplication map
+    By Lemma~\ref{prop:Df_affine} we find a cover $\Proj(S) = \bigcup_i \D{x_i}$ of affine opens.
+    We use the characterization from the lecture and show that $\D{x_i} \cap \D{x_j}$ is an affine open and the canonical multiplication map
     \begin{equation*}
-        \O_{\P_R^n}(D_{x_i}) \times \O_{\P_R^n}(D_{x_j}) \to \O_{\P_R^n}(D_{x_i} \cap D_{x_j})
+        \O_{\P_R^n}(\D{x_i}) \times \O_{\P_R^n}(\D{x_j}) \to \O_{\P_R^n}(\D{x_i} \cap \D{x_j})
     \end{equation*}
@@
 
-    First note that $D_{x_i} \cap D_{x_j} = D_{x_ix_j}$ which is affine open by Lemma~\ref{prop:Df_affine}.
-    By definition, we have $\O_{\P_R^n}(D_f) = (R[x_0, ..., x_n]_f)_0$ and so we have to show that
+    First note that $\D{x_i} \cap \D{x_j} = \D{x_ix_j}$ which is affine open by Lemma~\ref{prop:Df_affine}.
+    By definition, we have $\O_{\P_R^n}(\D{f}) = (R[x_0, ..., x_n]_f)_0$ and so we have to show that
     \begin{equation*}
@@
     and clearly $f/x_i^{2n} \in (R[x_0, ..., x_n]_{x_i})_0$ as $\deg(f) = \deg(x_i) n + \deg(x_j) n = 2n$ and $x_i^n/x_j^n \in (R[x_0, ..., x_n]_{x_j})_0$.
-    The claim follows
+    The claim follows.
 \end{proof}
+To study integrality, it is useful to have the next small lemma on the nilradical.
 \begin{lemma}
@@
 \begin{proof}
-    We show that $D_{x_0} \subseteq \P_R^n$ is dense.
+    We show that $\D{x_0} \subseteq \P_R^n$ is dense.
     The claim then follows, as any two nonempty, disjoint open sets give nonempty, disjoint open sets in $D_{x_0}$ which is isomorphic to the 
@@
 
-    So consider any nonempty basic open $D_f \subseteq \P_R^n$ and find that $D_f \cap D_{x_0} = D_{fx_0}$.
-    By assumption, $\Nil(R)$ is a prime ideal and so $fx_0$ is not nilpotent (unless $f$ were nilpotent, but then $D_f = \emptyset$), i.e. the ring $R[x_0, ..., x_n]_{fx_0}$ is not the zero ring.
+    So consider any nonempty basic open $\D{f} \subseteq \P_R^n$ and find that $\D{f} \cap \D{x_0} = \D{fx_0}$.
+    By assumption, $\Nil(R)$ is a prime ideal and so $fx_0$ is not nilpotent (unless $f$ were nilpotent, but then $\D{f} = \emptyset$), i.e. the ring $R[x_0, ..., x_n]_{fx_0}$ is not the zero ring.
     Hence, it has a maximal ideal $\m$.
@@
     is a homogeneous prime ideal, and since $fx_0 \notin \p \supseteq \p'$, we see that $S_+ \not\subseteq \p'$, i.e. $\p' \in \Proj(R[x_0, ..., x_n])$.
-    Now it follows that $\p' \in D_{fx_0}$, so $D_{fx_0} \neq \emptyset$.
+    Now it follows that $\p' \in \D{fx_0}$, so $\D{fx_0} \neq \emptyset$.
 \end{proof}
@@
 \begin{proof}
-    By the lecture, it suffices to show that each $\O_{\P_R^n}(D_{x_i}) \cong \Spec(R[x_0, ..., x_n]_{x_i})_0$ is reduced.
+    By the lecture, it suffices to show that each $\O_{\P_R^n}(\D{x_i}) \cong \Spec(R[x_0, ..., x_n]_{x_i})_0$ is reduced.
     However this is trivial, as taking the polynomial ring $R[x_0, ..., x_n]$ preserves reducedness by Lemma~\ref{prop:nil_poly_ring}, and localizing (and of course taking the subring $S_0$) also do.
@@
     \label{prop:p_quasi_compact}
-    $\P_R^n \to \Spec(R)$ is of finite type.
+    The morphism $\P_R^n \to \Spec(R)$ is of finite type.
 \end{prop}
 \begin{proof}
-    First note that $\P_R^n$ is covered by a finite number of affine opens $D_{x_i}$ where the canonical morphisms
+    First note that $\P_R^n$ is covered by a finite number of affine opens $\D{x_i}$ where the canonical morphisms
     \begin{equation*}
-        D_{x_i} \cong \Spec(R[x_0, ..., x_n]_{x_i})_0 \to \Spec(R)
+        \D{x_i} \cong \Spec(R[x_0, ..., x_n]_{x_i})_0 \to \Spec(R)
     \end{equation*}
@@
 
-    To see that it is locally of finite type, show that there is the cover by affine opens $\P_R^n = \bigcup_i D_{x_i}$ such that the ring homomorphisms $R \to \O_{\P_R^n}(D_{x_i})$ are of finite type.
+    To see that it is locally of finite type, show that there is the cover by affine opens $\P_R^n = \bigcup_i \D{x_i}$ such that the ring homomorphisms $R \to \O_{\P_R^n}(\D{x_i})$ are of finite type.
     This is clearly the case, as
     \begin{equation*}
-        \O_{\P_R^n}(D_{x_i}) = (R[x_0, ..., x_n]_{x_i})_0 \cong R[y_0, ..., y_{i - 1}, y_i, ..., y_n]
+        \O_{\P_R^n}(\D{x_i}) = (R[x_0, ..., x_n]_{x_i})_0 \cong R[y_0, ..., y_{i - 1}, y_i, ..., y_n]
     \end{equation*}
@@
 \section{Projective space is proper}
-We already know that $\P_R^n$ is separated and of finite type over $\Spec(R)$, hence it is left to show that it is universally closed.
+We already know that $\P_R^n$ is separated and of finite type over $\Spec(R)$, now we want to show that it is proper.
+Both in Hartshorne \cite{hartshorne} and the Stacks project \cite{stacks}, and in every other source I could find, this is done using the ``valuative criterion for properness'' (see also Section~\ref{prop:valuative_criterion_properness}).
+However, its proof is apparently quite lengthy and requires a lot of abstract algebra.
+In the following, I tried to find a simpler and shorter proof.
+That was only partially successful, as the proof I came up with is shorter, but definitely not simpler.
+However, it gives a slightly different perspective onto the issue, which is quite nice.
 \begin{lemma}
@@
 \end{proof}
-\cite[66.9.5.]{stacks}
+I am slightly surprised that the following lemma was to be found nowhere, except in \cite[66.9.5.]{stacks} (for general algebraic spaces).
+It seems to be the kind of characterization I would expect to find in most textbooks.
 \begin{corollary}
     \label{prop:universally_closed_affines}
-    A scheme $X$ over $\Spec(R)$ is universally closed, if for all ring homomorphisms $R \to S$ have the following:
+    A scheme $X$ over $\Spec(R)$ is universally closed, if for all ring homomorphisms $R \to S$ satisfy the following:
     The base change map $X \times_{\Spec(R)} \Spec(S) \to \Spec(S)$, i.e. the map that makes the diagram
@@
     \end{equation*}
-    However, in general this is not well-defined, as $\alpha^{-1}(\p)$ might contain $S_+$.
+    However, in general this is not well-defined, as $\alpha^{-1}(\p)$ might contain $S_+$\footnote{Just consider the inclusion $R[x] \to R[x, y]$ and the ideal $\langle x \rangle \in \Proj(R[x, y])$.}.
 
@@
         \Proj(\alpha): \Proj(T) &\to \Proj(S), \quad \p \mapsto \alpha^{-1}(\p), \\
-        \Proj(\alpha)^\#_{D_f}: \O_{\Proj(S)}(D_f) &\to \O_{\Proj(T)}(D_{\alpha(f)}), \quad \frac x y \mapsto \frac {\alpha(x)} {\alpha(y)}
+        \Proj(\alpha)^\#_{\D{f}}: \O_{\Proj(S)}(\D{f}) &\to \O_{\Proj(T)}(\D{\alpha(f)}), \quad \frac x y \mapsto \frac {\alpha(x)} {\alpha(y)}
     \end{align*}
@@
     for all homogeneous $f \in R[x_0, ..., x_n]$.
-    By Lemma~\ref{prop:Df_affine}, we see that $D_f$ for $f \in S[x_0, ..., x_n]$ homogeneous form an affine open cover of $\P_S^n$.
-    Furthermore, we have a cover by affine opens $D_f \times_{\Spec(R)} \Spec(S)$ of $\P_R^n \times_{\Spec(R)} \Spec(S)$ for $f \in R[x_0, ..., x_n]$ homogeneous.
+    By Lemma~\ref{prop:Df_affine}, we see that $\D{f}$ for $f \in S[x_0, ..., x_n]$ homogeneous form an affine open cover of $\P_S^n$.
+    Furthermore, we have a cover by affine opens $\D{f} \times_{\Spec(R)} \Spec(S)$ of $\P_R^n \times_{\Spec(R)} \Spec(S)$ for $f \in R[x_0, ..., x_n]$ homogeneous.
     Together, we see that it suffices to show that the isomorphisms (induced by $\iota_f$)
     \begin{equation*}
-        \phi_f: D_{\alpha(f)} = \Spec((S[x_0, ..., x_n]_{\alpha(f)})_0) \to D_f \times_{\Spec(R)} \Spec(S)
+        \phi_f: \D{\alpha(f)} = \Spec((S[x_0, ..., x_n]_{\alpha(f)})_0) \to \D{f} \times_{\Spec(R)} \Spec(S)
     \end{equation*}
@@
         \begin{tikzpicture}
-            \node (Sfg) at (0, 0) {$D_{\alpha(f)} \cap D_{\alpha(g)} = D_{\alpha(fg)}$};
-            \node (Sf) at (3, 1) {$D_{\alpha(f)}$};
-            \node (Sg) at (3, -1) {$D_{\alpha(g)}$};
-            \node (f) at (7, 1) {$D_f \times_{\Spec(R)} \Spec(S)$};
-            \node (g) at (7, -1) {$D_g \times_{\Spec(R)} \Spec(S)$};
-            \node (all) at (10, 0) {$\P_R^n \times_{\Spec(R)} \Spec(S)$};
+            \node (Sfg) at (1, 0) {$\D{\alpha(f)} \cap \D{\alpha(g)} = \D{\alpha(fg)}$};
+            \node (Sf) at (3, 1.5) {$\D{\alpha(f)}$};
+            \node (Sg) at (3, -1.5) {$\D{\alpha(g)}$};
+            \node (f) at (7, 1.5) {$\D{f} \times_{\Spec(R)} \Spec(S)$};
+            \node (g) at (7, -1.5) {$\D{g} \times_{\Spec(R)} \Spec(S)$};
+            \node (all) at (9, 0) {$\P_R^n \times_{\Spec(R)} \Spec(S)$};
 
@@
 
-    For a prime ideal $\p \in D_{\alpha(fg)}$ have that
+    For a prime ideal $\p \in \D{\alpha(fg)}$ have that
     \begin{equation*}
-        \phi_f(\p) = \iota_f^{-1}(\p \cap (S[x_0, ..., x_n]_f)_0) \in D_f \times_{\Spec(R)} \Spec(S)
+        \phi_f(\p) = \iota_f^{-1}(\p \cap (S[x_0, ..., x_n]_f)_0) \in \D{f} \times_{\Spec(R)} \Spec(S)
     \end{equation*}
-    and so $g \notin \phi_f(\p)$, i.e. $\phi_f(\p) \in D_{fg} \times_{\Spec(R)} \Spec(S)$.
+    and so $g \notin \phi_f(\p)$, i.e. $\phi_f(\p) \in \D{fg} \times_{\Spec(R)} \Spec(S)$.
     Hence, we have that both restrictions
     \begin{equation*}
-        \restr{\phi_f}{D_{\alpha(fg)}}, \ \restr{\phi_g}{D_{\alpha(fg)}}: D_{\alpha(fg)} \to D_{fg} \times_{\Spec(R)} \Spec(S)
+        \restr{\phi_f}{\D{\alpha(fg)}}, \ \restr{\phi_g}{\D{\alpha(fg)}}: \D{\alpha(fg)} \to \D{fg} \times_{\Spec(R)} \Spec(S)
     \end{equation*}
-    map into $D_{fg} \times_{\Spec(R)} \Spec(S)$.
+    map into $\D{fg} \times_{\Spec(R)} \Spec(S)$.
     Now note that the diagram
@@
     \end{center}
-    commutes, and so the restrictions of $\phi_f$ resp. $\phi_g$ to $D_{\alpha(fg)}$ are both induced by the homomorphism $\iota_{fg}$, hence they are equal.
+    commutes, and so the restrictions of $\phi_f$ resp. $\phi_g$ to $\D{\alpha(fg)}$ are both induced by the homomorphism $\iota_{fg}$, hence they are equal.
     The claim follows.
 \end{proof}
+We now come close to the core of the proof.
+However, there is one further notion we need.
+\begin{definition}
+    Let $x \in X$ be a point in a scheme (or more generally, a topological space).
+    A point $x' \in X$ is said to \emph{specialize} $x$, if it is contained in the closure $x' \in \overline{\{x\}}$.
+\end{definition}
 The next lemma is directly from \cite[II.4.5]{hartshorne}.
@@
 \end{lemma}
+\begin{proof}
+    The implication $\Leftarrow$ is clear.
+    It suffices to show that $f(|X|) \cap V \subseteq V$ is closed for all affine opens $V \subseteq Y$.
+
+    Note that the preimage $f^{-1}(V)$ is quasi-compact, hence has a finite cover of affine opens $U_i \subseteq X$.
+    Now let $V_i = \overline{f(|U_i|)}$ be the closed subscheme of $V$ with the canonical (reduced) scheme structure\footnote{As in the Lecture Notes, Section 5.6.}.
+    Since $V$ is affine, also $V_i$ is affine.
+    Note that now it suffices to show that $f(|U_i|) \subseteq V_i$ is closed.
+
+    In other words, we have reduced the situation to the case that
+    \begin{equation*}
+        f' = \restr{f}{U_i}: U_i = \Spec(A) \to V_i = \Spec(B)
+    \end{equation*}
+    is a morphism between affine schemes with dense image.
+    We want to show that $f'(|U_i|)$ is already $V_i$.
+
+    Consider some $\p \in V_i$.
+    By Zorn's Lemma, there is a minimal prime ideal $\p' \subseteq \p$ in the ring $B$.
+    Note that $\p$ is a specialization of $\p'$.
+    Hence, it suffices to show that $\p' \in f'(|U_i|)$.
+    Note that $B_{\p'}$ must be a field, otherwise we could take a proper nonzero prime ideal of $B_{\p'}$ and its preimage under $B \to B_{\p'}$ would be a smaller prime ideal in $B$.
+
+    Since $f': \Spec(A) \to \Spec(B)$ has dense image, we find that $B \to A$ is injective.
+    Consider $A$ as a $B$-algebra.
+    Let $\q$ be a prime ideal of $A \otimes_B B_{\p'}$ (this is not the zero ring, as $B_{\p'}$ is a flat $B$-module and so the inclusion $B \to B_{\p'}$ induces an inclusion $B_{\p'} \to A \otimes_B B_{\p'}$).
+
+    Taking the preimage of $\q$ under the map $A \to A \otimes_B B_{\p'}$ now gives a prime ideal $\q' \leq A$.
+    Since $\q \cap B_{\p'} = \{ 0 \}$ (here we use that $B_{\p'}$ is a field), find $\q' \cap B = \p'$, thus $\q'$ maps to $\p'$ under $\Spec(A) \to \Spec(B)$.
+    This shows $\p' \in f'(|U_i|)$ and the claim follows.
+\end{proof}
+The next lemma is now the decisive statement that will allow us to show that $\P_R^n \to \Spec(R)$ is closed.
+It is also the place where things get somewhat ugly, and we require a good deal of commutative algebra to prove it.
 \begin{lemma}
@@
     \begin{equation*}
-        \tilde{S} := \begin{cases}
-            \Z[A/\alpha, x] & \text{if $\mathrm{char}(S) = 0$} \\
-            (\Z/\mathrm{char}(R)\Z)[A/\alpha, x] & \text{if $\mathrm{char}(S) \neq 0$}
-        \end{cases}
+        \tilde{S} := \bigl( \Z / \mathrm{char}(S) \Z \bigr) \bigl[ A/\alpha, x \bigr]
     \end{equation*}
@@
     Now equip $S_{\mathfrak{l}}$ with the $\mathfrak{l}$-adic topology.
-    Note that $S$ is noetherian and local, thus the Krull intersection theorem shows that the $\mathfrak{l}$-adic topology is Hausdorff and we find
+    Note that $S$ is noetherian and local, thus the Krull intersection theorem \cite[8.41]{comalg_notes} shows that the $\mathfrak{l}$-adic topology is Hausdorff and we find
     \begin{equation*}
@@
 \end{proof}
+As we will see in the next proof, this lemma shows that if $\P_R^n \to \Spec(R)$ maps a point $\p$ to a point $\q$, then it also maps a specialization of $\p$ to any specialization of $\q$.
+From this, we can derive the next proposition.
 \begin{prop}
@@
 \section{Valuative criterion of properness}
+\label{prop:valuative_criterion_properness}
+Instead of using some magical ad-hoc argument as before, there is also the following nice characterization of the notion of properness.
+We will omit the proof here, but present it as it can give more geometric intuition on properness and why $\P_R^n$ is proper.
 \begin{prop}
+    \label{prop:valuative_criterion_properness}
     Let $X$ be noetherian and $f: X \to Y$ a morphism of finite type.
@@
 \end{prop}
+\begin{proof}
+    Omitted, see e.g. \cite[II.4.7]{hartshorne}
+\end{proof}
+\begin{prop}
+    The morphism $\P_R^n \to \Spec(R)$ is proper.
+\end{prop}
+\begin{proof}[Alternative Proof]
+    Since properness is preserved under base change, by Lemma~\ref{prop:projective_space_base_change} it suffices to show the statement for $\P_\Z^n \to \Spec(\Z)$.
+
+    Apply Proposition~\ref{prop:valuative_criterion_properness}.
+    Let $R$ be a valuation ring, $K = \Frac(R)$ and assume we have morphisms $\Spec(R) \to Y$, $\Spec(K) \to X$ such that the diagram
+    \begin{center}
+        \begin{tikzpicture}
+            \node (K) at (0, 0) {$\Spec(K)$};
+            \node (R) at (0, -2) {$\Spec(R)$};
+            \node (X) at (3, 0) {$X$};
+            \node (Y) at (3, -2) {$Y$};
+
+            \draw [->] (K) -- (R);
+            \draw [->] (K) -- (X);
+            \draw [->] (R) -- (Y);
+            \draw [->] (X) -- (Y) node [midway, right] {$f$};
+        \end{tikzpicture}
+    \end{center}
+    commutes.
+    Note that $\Spec(K) = \{ \langle 0 \rangle \}$, so let $\xi_1 \in X$ be the image of $\langle 0 \rangle$ under $\Spec(K) \to X$.
+    Since $\langle x_0, ..., x_n \rangle \not\subseteq \xi$, there is $x_i \not\in \xi$.
+    Now let
+    \begin{equation*}
+        f_j := \begin{cases}
+            x_j & \text{if $x_j \notin \xi_1$} \\
+            x_j - x_i & \text{if $x_j \in \xi_1$}
+        \end{cases}
+    \end{equation*}
+    Thus all $f_j$ are homogeneous of degree 1 with $\langle f_j \ | \ j \rangle = \langle x_0, ..., x_n \rangle$.
+    It follows that $X = \bigcup_j \D{f_j}$ is a cover by affine opens such that $\xi_1 \in \bigcap_j \D{f_j}$.
+    Now possibly apply a linear automorphism $f_j \to x_j$ and thus assume wlog that $f_j = x_j$.
+    In particular, find $x_j \in \O_{X, \xi_1}^*$.
+
+    The morphism $\Spec(K) \to X$ now gives an inclusion $k(\xi_1) \subseteq K$.
+    Since $x_j \in \O_{X, \xi_1}^*$, observe that $g_{ij} := x_i / x_j \in K$ is well-defined and nonzero with $g_{ij} g_{jk} = g_{ik}$.
+
+    As $R$ is a valuation ring, we find $k$ such that $g_{k0}$ is the smallest element (w.r.t. divisibility by $R$) among $g_{00}, ..., g_{n0}$.
+    So we see that $g_{ik} = g_{i0} / g_{k0} \in R$ for all $i$.
+    In particular, we find a ring homomorphism
+    \begin{equation*}
+        \Z\left[ \frac {x_0} {x_k}, ..., \frac {x_n} {x_k} \right] \to R, \quad \frac {x_j} {x_k} \mapsto g_{ik}
+    \end{equation*}
+    that is compatible with the field inclusion $k(\xi_1) \subseteq K$.
+
+    The induced morphism
+    \begin{equation*}
+        \Spec(R) \to \Spec(\Z\Bigl[ \frac {x_0} {x_k}, ..., \frac {x_n} {x_k} \Bigr]) = \D{x_j} \subseteq X
+    \end{equation*}
+    is now a compatible morphism $\Spec(R) \to X$.
+
+    Also it is not too hard to show that the morphism is unique, and the claim follows.
+\end{proof}
+Note that in some way, this is the same proof as before.
+The core idea - namely the choice of the smallest element $g_{k0}$ (w.r.t.
+divisibility by $R$) - more or less achieves the same effect as the more complicated ideal argument from Lemma~\ref{prop:adding_coeff_ideal_does_not_introduce_irrelevant_ideal}.
 \printbibliography

### 2022-03-26 Schemes/submission.tex
Finished schemes

@@
 \DeclareMathOperator*{\colim}{colim}
+\newcommand{\citestacks}[1]{\cite[\href{https://stacks.math.columbia.edu/tag/#1}{Tag #1}]{stacks}}
 
@@
 
-\newtheorem{prop}{Proposition}
-\newtheorem{theorem}[prop]{Theorem}
-\newtheorem{lemma}[prop]{Lemma}
-\newtheorem{corollary}[prop]{Corollary}
+\newtheorem{prop}[subsection]{Proposition}
+\newtheorem{theorem}[subsection]{Theorem}
+\newtheorem{lemma}[subsection]{Lemma}
+\newtheorem{corollary}[subsection]{Corollary}
 
 \theoremstyle{definition}
-\newtheorem{problem}[prop]{Problem}
-\newtheorem{alg}[prop]{Algorithm}
-\newtheorem{definition}[prop]{Definition}
-\newtheorem{example}[prop]{Example}
-\newtheorem{remark}[prop]{Remark}
-\newtheorem{reminder}[prop]{Reminder}
+\newtheorem{problem}[subsection]{Problem}
+\newtheorem{alg}[subsection]{Algorithm}
+\newtheorem{definition}[subsection]{Definition}
+\newtheorem{example}[subsection]{Example}
+\newtheorem{remark}[subsection]{Remark}
+\newtheorem{reminder}[subsection]{Reminder}
 
@@
 \begin{definition}
-    A \emph{graded ring} $S$ is a ring $S$ with a decomposition $S = \oplus_{d \in \N} S_d$ into groups $S_i \subseteq S$ (w.r.t.
-addition in $S$) such that $S_i S_j \subseteq S_{i + j}$ for all $i, j \in \Z$.
+    A \emph{graded ring} $S$ is a ring $S$ with a decomposition\footnote{We use the convention that $0 \in \N$.} $S = \oplus_{d \in \N} S_d$ into subgroups $S_i \subseteq S$ (w.r.t.
+addition in $S$) such that $S_i \cdot S_j \subseteq S_{i + j}$ for all $i, j \in \Z$.
     Write further $S_+ := \sum_{d \neq 0} S_d$.
@@
     Clearly $\Proj(S) = \D{\langle 1 \rangle}$ and $\emptyset = \D{\langle 0 \rangle}$ are open.
-    Furthermore, for open sets $\D{\a}$ and $\D{\b}$, have that
+    To show that finite intersections and arbitrary unions of open sets are open, notice that as usual
     \begin{equation*}
-        \D{\a} \cap \D{\b} = \{ \p \in \Proj(S) \ | \ \a, \b \not\subseteq \p \} = \{ \p \in \Proj(S) \ | \ \a\b \not\subseteq \p \} = \D{\a\b}
+        \D{\a} \cap \D{\b} = \D{\a\b} \quad \text{and} \quad \bigcup_{\a \in \mathcal{A}} \D{\a} = \D{\b} \quad \text{where} \ \b = \sum_{\a \in \mathcal{A}} \a
     \end{equation*}
-    This holds, as $\a, \b \not\subseteq \p$ implies that there are $f \in \a$ and $g \in \b$ with $f, g \notin \p$.
-    However, then $fg \notin \p$ as $\p$ is prime.
-    Obviously $\a\b$ is homogeneous, and so $\D{\a} \cap \D{\b}$ is open.
-
-    Finally, given a collection $\mathcal{A}$ of homogeneous ideals in $S$, have that
-    \begin{align*}
-        \bigcup_{\a \in \mathcal{A}} \D{\a} =& \{ \p \in \Proj(S) \ | \ \exists \a \in \mathcal{A}:\ \a \not\subseteq \p \} = \{ \p \in \Proj(S) \ | \ \exists \a \in \mathcal{A} \exists f \in \a:\ f \notin \p \} \\
-        =& \Bigl\{ \p \in \Proj(S) \ \Bigm| \ \exists f \in \sum_{\a \in \mathcal{A}} \a:\ f \notin \p \Bigr\} = \D{\b} \quad \text{for $\b = \sum_{\a \in \mathcal{A}} \a$}
-    \end{align*}
-    Clearly $\b$ is again homogeneous, and so $\bigcup_{\a \in \mathcal{A}} \D{\a}$ is open.
+    Clearly the ideals $\a\b$ and $\b$ are again homogeneous.
 \end{proof}
-As opposed to Hartshorne \cite{hartshorne}, we follow an approach similar to the construction of $\O_{\Spec(R)}$ to construct a sheaf of rings on $\Proj(S)$.
+As opposed to Hartshorne \cite{hartshorne}, we follow an approach to construct a sheaf of rings on $\Proj(S)$ will be similar to the construction of $\Spec(R)$.
 In particular, we will define $\O_{\Proj(S)}$ on a basis of the topology, and extend it to a sheaf.
-This will be somewhat more tedious, but gives a nice idea of how $\O_{\Proj(S)}(U)$ looks like.
+This is also the definition used in \citestacks{01M6}.
+IT will be somewhat more tedious, but gives a nice idea of how $\O_{\Proj(S)}(U)$ looks like.
 \begin{lemma}
@@
 \end{prop}
-\begin{proof}
+\begin{proof}\footnote{I guess I have included the proof mostly for the sake of completeness - apart from presentational issues, it is just copied from the lecture notes.}
     Clearly, $\mathcal{F}$ is a functor and thus a presheaf.
@@
 \end{corollary}
-The next to lemmas are based on \cite[II.2.5]{hartshorne} and show that $(\Proj(S), \O_{\Proj(S)})$ is a scheme.
+The next to lemmas are based on \cite[Prop. II.2.5]{hartshorne} and will be used to deduce that $(\Proj(S), \O_{\Proj(S)})$ is a scheme.
 \begin{lemma}
@@
     \begin{equation*}
-        \eta_{D_{g/f^n}}: R_{g/f^n} \to (S_{fg})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
+        \eta_{\D{g/f^n}}: R_{g/f^n} \to (S_{fg})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
     \end{equation*}
@@
 For this section, let $R$ be a ring and $n \in \N$.
-
-First, we will study the property of being separated.
 \begin{prop}
@@
 \begin{proof}
+    This is the same proof as for \citestacks{01MC}.
     By Lemma~\ref{prop:Df_affine} we find a cover $\Proj(S) = \bigcup_i \D{x_i}$ of affine opens.
@@
     \label{prop:nil_poly_ring}
-    It holds that $\Nil(R)R[x_0, ..., x_n] = \Nil(R[x_0, ..., x_n])$.
+    If $\Spec(R)$ is irreducible, then $\Nil(R)R[x_0, ..., x_n] = \Nil(R[x_0, ..., x_n])$.
 \end{lemma}
@@
     \end{equation*}
-    Now note that $\Nil(R[x_0, ..., x_n]) \subseteq \a$ for all ideals $\a$ and the claim follows.
+    Now note that $\Nil(R[x_0, ..., x_n]) \subseteq \a$ for all prime ideals $\a$, and the claim follows since $\Nil(R)$ is prime by assumption that $\Spec(R)$ is irreducible.
 \end{proof}
@@
     By the lecture, it suffices to show that each $\O_{\P_R^n}(\D{x_i}) \cong \Spec(R[x_0, ..., x_n]_{x_i})_0$ is reduced.
-    However this is trivial, as taking the polynomial ring $R[x_0, ..., x_n]$ preserves reducedness by Lemma~\ref{prop:nil_poly_ring}, and localizing (and of course taking the subring $S_0$) also do.
+    However this is trivial, as taking the polynomial ring $R[x_0, ..., x_n]$ preserves reducedness, and localizing (and of course taking the subring $S_0$) also do.
 \end{proof}
@@
 However, it gives a slightly different perspective onto the issue, which is quite nice.
+
+I am slightly surprised that the following lemma was to be found nowhere, except in \citestacks{03IT} (for general algebraic spaces).
+It seems to be the kind of characterization I would expect to find in most textbooks.
 \begin{lemma}
-    Let $X, Y$ be topological spaces and $f: X \to Y$ a continuous map.
-    Let further $Y = \bigcup_i V_i$ be a cover by open sets.
-    If each of the maps
-    \begin{equation*}
-        \restr{f}{f^{-1}(V_i)}: f^{-1}(V_i) \to V_i
-    \end{equation*}
-    is closed (as a map into $V_i$), then $f$ is closed.
-\end{lemma}
-\begin{proof}
-    Consider some closed $C \subseteq X$ and $x \in Y \setminus f(C)$.
-    Since the $V_i$ cover $Y$, there is $i$ such that $x \in V_i$.
-    As $\restr{f}{f^{-1}(V_i)}$ is closed, we see that
-    \begin{equation*}
-        f(C) \cap V_i = \restr{f}{f^{-1}(V_i)}(C)
-    \end{equation*}
-    is closed in $V_i$, hence there is an open neighborhood $U \subseteq V_i$ of $x$ with $U \cap f(C) = \emptyset$.
-    Now note that $V_i \subseteq Y$ is open, and so $U$ is also an open neighborhood of $x$ in $Y$.
-    This holds for all $x \in Y \setminus f(C)$, hence $f(C)$ is closed.
-\end{proof}
-I am slightly surprised that the following lemma was to be found nowhere, except in \cite[66.9.5.]{stacks} (for general algebraic spaces).
-It seems to be the kind of characterization I would expect to find in most textbooks.
-\begin{corollary}
     \label{prop:universally_closed_affines}
@@
     commute, is closed.
-\end{corollary}
+\end{lemma}
 \begin{proof}
@@
     \end{equation*}
-    of schemes over $Y \times X$, i.e. the inclusion $\pi^{-1}(V_i)$ factors as
+    of schemes over $Y \times X$, i.e. the inclusion of $\pi^{-1}(V_i)$ into $Y \times_{\Spec(R)} X$ factors as
     \begin{equation*}
@@
     It follows that $\pi^{-1}(V_i) = V_i \times_{\Spec(R)} X$.
+    By assumption, we now get that each $\pi_i$ is closed, as $V_i \cong \Spec(\O_Y(V_i))$ is affine.
 
-    By assumption we know that each $\pi_i$ is closed, as $V_i \cong \Spec(\O_Y(V_i))$ is affine.
-    Now the previous lemma yields that also $\pi$ is closed.
+    To show that $\pi$ is closed, let $C \subseteq Y \times_{\Spec(R)} X$ be closed.
+    Consider some $x \in Y \setminus \pi(C)$.
+    Since the $V_i$ cover $Y$, there is $i$ such that $x \in V_i$.
+    As $\pi = \restr{\pi}{f^{-1}(V_i)}$ is closed, we see that
+    \begin{equation*}
+        \pi(C) \cap V_i = \pi_i(C) \quad \text{is closed in $V_i$}
+    \end{equation*}
+    Hence there is an open neighborhood $U \subseteq V_i$ of $x$ with $U \cap \pi(C) = \emptyset$.
+    Now note that $V_i \subseteq Y$ is open, and so $U$ is also an open neighborhood of $x$ in $Y$.
+    This holds for all $x \in Y \setminus \pi(C)$, hence $\pi(C)$ is closed.
 \end{proof}
@@
             \node (Rf) at (-3, 0) {$S \otimes_R (R[x_0, ..., x_n]_f)_0$};
-            \node (Rg) at (0, -2) {$S \otimes_R (R[x_0, ..., x_n]_g)_0$};
-            \node (Rfg) at (-3, -4) {$S \otimes_R (R[x_0, ..., x_n]_{fg})_0$};
+            \node (Rg) at (0, -1.5) {$S \otimes_R (R[x_0, ..., x_n]_g)_0$};
+            \node (Rfg) at (-3, -3) {$S \otimes_R (R[x_0, ..., x_n]_{fg})_0$};
 
             \node (Sf) at (8, 0) {$(S[x_0, ..., x_n]_f)_0$};
-            \node (Sg) at (5, -2) {$(S[x_0, ..., x_n]_g)_0$};
-            \node (Sfg) at (8, -4) {$(S[x_0, ..., x_n]_{fg})_0$};
+            \node (Sg) at (5, -1.5) {$(S[x_0, ..., x_n]_g)_0$};
+            \node (Sfg) at (8, -3) {$(S[x_0, ..., x_n]_{fg})_0$};
 
@@
 \end{proof}
-We now come close to the core of the proof.
-However, there is one further notion we need.
+Before we come to the proof now, there is one last notion to present.
 \begin{definition}
@@
     \label{prop:adding_coeff_ideal_does_not_introduce_irrelevant_ideal}
-    Let $\p \leq R[x_0, ..., x_n]$ be a homogeneous prime ideal with $R[x_0, ..., x_n]_+ \not\subseteq \p$.
-    Further let $\q \leq R$ be a prime ideal such that $\p \cap R \subseteq \q$.
+    Let $\p \in \Proj(R[x_0, ..., x_n])$ and let $\q \leq R$ be a prime ideal such that $\p \cap R \subseteq \q$.
     Then there some $i$ such that no $\alpha x_i^m$ is in $\b := \p + \q R[x_0, ..., x_n]$, for any $\alpha \in R \setminus \b$ and any $m \in \N$.
@@
 \begin{proof}
-    Assume there is $m \in \N$ such that $\alpha_i x_i^m \in \b$ for all $i$ and some $\alpha_i \in \b \setminus R$.
-    Since $\b \cap R = \q$ is prime, have that $\alpha := \prod_i \alpha_i \notin \b$.
-    Further we have that $\alpha x_i^m \in \b$ for all $i$.
+    Assume for a contradiction  that there is $m \in \N$ such that $\alpha_i x_i^m \in \b$ for all $i$ and some $\alpha_i \in \b \setminus R$.
+    Since $\b \cap R = \q$ is prime, have that $\alpha := \prod_i \alpha_i \notin \b$ and further $\alpha^n \notin \b$ for all $n \in \N$.
+    Furthermore, we obviously have $\alpha x_i^m \in \b$ for all $i$.
 
     Consider now the vector $(w_i)_{i < N}$ containing all monomials of degree $(n + 1)m$.
-    By assumption, all $\alpha w_i \in \b$.
+    By assumption, all\footnote{Since a monomial of degree $(n + 1)m$ in $n + 1$ variables is divisible by $x_i^m$ for at least one $i$, by the pigeonhole principle.} $\alpha w_i \in \b$.
     Since $\p$ is homogeneous, observe that now there are $r_{ij} \in \q$ such that
@@
     \end{equation*}
-    Working modulo $\p$, we see that $A w = \alpha w$ where $A \in (\b/\p)^{N \times N}$.
+    Working modulo $\p$, we see that $A w = \alpha w$ where $A \in (\b/\p)^{N \times N}$ is a matrix with coefficients in $\b/\p$.
 
-    Now observe that $\alpha \notin \b/\p$ since $\alpha \notin \b$.
-    Hence there exists a prime ideal in $R/\p$ containing $\b/\p$ and not containing $\alpha$.
+    Now observe that no power of $\alpha$ is in $\b/\p$ (as mentioned before).
+    Hence there exists a prime ideal\footnote{By the usual argument, i.e.
+take a preimage of a prime ideal under the map $R \to R/\p \to (R/\p)_\alpha$.} in $R/\p$ containing $\b/\p$ and not containing $\alpha$.
     Localizing at that prime ideal gives a local ring $S$ with maximal ideal $\mathfrak{l}$.
-    Now assume that $w \in S^n$ and $A/\alpha \in \mathfrak{l}^{n \times n}$.
+    Now we continue in $S$, replacing $w$ and $A/\alpha$ by their images under $R \to S$.
+    So $w \in S^n$ and $A/\alpha \in \mathfrak{l}^{n \times n}$.
     Note that we still have $(A/\alpha) w = w$.
@@
     Denote $\P_R^n \to \Spec(R)$ by $\phi$.
-    Consider a closed set $\V(\a) = \P_R^n \setminus D_\a$ given by a homogeneous ideal $\a \leq R[x_0, ..., x_n]$.
-    By Lemma~\ref{prop:im_closed_iff_stable_specialization}, it suffices to show that $\phi(\V(\a))$ is closed under specialization (note that $\P_R^n \to \Spec(R)$ is quasi-compact, e.g.
+    Consider a closed set $\V{\a} = \P_R^n \setminus \D{\a}$ given by a homogeneous ideal $\a \leq R[x_0, ..., x_n]$.
+    By Lemma~\ref{prop:im_closed_iff_stable_specialization}, it suffices to show that $\phi(\V{\a})$ is closed under specialization (note that $\P_R^n \to \Spec(R)$ is quasi-compact, e.g.
 by Proposition~\ref{prop:p_quasi_compact}).
 
-    Consider $\q \in \phi(\V(\a)) \subseteq \Spec(R)$ and a prime ideal $\q'$ that specializes $\q$, i.e. $\q' \supseteq \q$.
-    Then there is a $\p \in \V(\a)$ with $\p \cap R = \q$, in particular $\a \subseteq \p$.
-    We want to show that $\q' \in \phi(\V(\a))$.
+    Consider $\q \in \phi(\V{\a}) \subseteq \Spec(R)$ and a prime ideal $\q'$ that specializes $\q$, i.e. $\q' \supseteq \q$.
+    Then there is a $\p \in \V{\a}$ with $\p \cap R = \q$, in particular $\a \subseteq \p$.
+    We want to show that $\q' \in \phi(\V{\a})$.
 
@@
 
-    Hence, the ring $T^{-1}(R[x_0, ..., x_n]/\b)$ is nonzero, thus has a prime.
+    Hence, the ring $T^{-1}(R[x_0, ..., x_n]/\b)$ is nonzero, thus has a prime ideal.
     Taking its preimage under
@@
     By Lemma~\ref{prop:homogeneous_part_prime}, assume wlog that $\p'$ is homogeneous.
-    Now have a homogeneous prime ideal $\p'$ with $\a \subseteq \p \subseteq \p'$, i.e. $\p' \in \V(\a)$ and $\phi(\p') = \p' \cap R = \q'$.
-    Thus $\q \in \phi(\V(\a))$ and the claim follows.
+    Now have a homogeneous prime ideal $\p'$ with $\a \subseteq \p \subseteq \p'$, i.e. $\p' \in \V{\a}$ and $\phi(\p') = \p' \cap R = \q'$.
+    Thus $\q \in \phi(\V{\a})$ and the claim follows.
 \end{proof}
+I must say, I find this proof and also the more geometric proof later (Proposition~\ref{prop:projective_space_proper_alternative_proof}) extremely fascinating.
+In particular, I like how generic points are quite important for the proof.
+It also reminds me of the only classical proof of an equivalent statement (projections from projective space are closed) I have ever seen.
+The idea was - more or less - to consider points $y \in \im(f) \subseteq \P_k^n$ with preimages $x \in X \subseteq \P_k^m$ and deduce (using Hilbert's Nullstellensatz) that there is some ``generic preimage'' $\tilde{x} \in \P_K^m$ in projective space over the algebraic closure $K = \overline{k(Y)}$ of the ``generic point'' $\tilde{y} = [y_0 : ...
+: y_n] \in \P_K^n$.
+A ``partial evaluation homomorphism'' (i.e. not defined on the whole domain) $K \dashrightarrow k$ can then be used to ``evaluate'' the ``generic preimage point'' on each image point.
+The core of that proof is exactly constructing this ``partial evaluation homomorphism'', which corresponds exactly to Lemma~\ref{prop:adding_coeff_ideal_does_not_introduce_irrelevant_ideal}.
+
+But now enough of talking, here is the main result.
 \begin{corollary}
@@
 \section{Valuative criterion of properness}
-\label{prop:valuative_criterion_properness}
+\label{sec:valuative_criterion_properness}
 Instead of using some magical ad-hoc argument as before, there is also the following nice characterization of the notion of properness.
-We will omit the proof here, but present it as it can give more geometric intuition on properness and why $\P_R^n$ is proper.
+We will omit the proof here, but present the statement as it can give more geometric intuition on properness and why $\P_R^n$ is proper.
 \begin{prop}
@@
                 \node (K) at (0, 0) {$\Spec(K)$};
-                \node (R) at (0, -2) {$\Spec(R)$};
+                \node (R) at (0, -1.5) {$\Spec(R)$};
                 \node (X) at (3, 0) {$X$};
-                \node (Y) at (3, -2) {$Y$};
+                \node (Y) at (3, -1.5) {$Y$};
 
@@
 \begin{proof}
-    Omitted, see e.g. \cite[II.4.7]{hartshorne}
+    Omitted, see e.g. \cite[II.4.7]{hartshorne} or \citestacks{01NH}.
 \end{proof}
 \begin{prop}
+    \label{prop:projective_space_proper_alternative_proof}
     The morphism $\P_R^n \to \Spec(R)$ is proper.
@@
             \node (K) at (0, 0) {$\Spec(K)$};
-            \node (R) at (0, -2) {$\Spec(R)$};
+            \node (R) at (0, -1.5) {$\Spec(R)$};
             \node (X) at (3, 0) {$X$};
-            \node (Y) at (3, -2) {$Y$};
+            \node (Y) at (3, -1.5) {$Y$};
 

### 2022-03-26 Schemes/submission.tex
Finalized schemes

@@
     \begin{equation*}
-        (fg_i)^{n_i} (\alpha f^N + \beta f^N) = 0
+        (f g_i)^{n_i} (\alpha f^N + \beta f^N) = 0
     \end{equation*}
@@
     \begin{equation*}
-        f^n(\alpha - \beta) \in \langle (fg_i)^N \ | \ i \rangle (\alpha - \beta) = \langle (fg_i)^N (\alpha - \beta) \ | \ i \rangle = \{ 0 \}
+        f^n(\alpha - \beta) \in \langle (f g_i)^N \ | \ i \rangle (\alpha - \beta) = \langle (f g_i)^N (\alpha - \beta) \ | \ i \rangle = \{ 0 \}
     \end{equation*}
@@
     \begin{equation*}
-        (f^2g_ig_j)^N \left( s'_i (fg_j)^N - s'_j (fg_i)^N \right) = 0 \quad \text{as $\restr{s_i}{\D{fg_ig_j}} = \restr{s_j}{\D{fg_ig_j}}$}
+        (f^2g_ig_j)^N \left( s'_i (f g_j)^N - s'_j (f g_i)^N \right) = 0 \quad \text{as $\restr{s_i}{\D{fg_ig_j}} = \restr{s_j}{\D{fg_ig_j}}$}
     \end{equation*}
@@
     \begin{equation*}
-        s_i = \frac {a_i} {b_i} \quad \text{with}\ a_i = s'_i(fg_i)^N, \ b_i = (fg_i)^{2N}
+        s_i = \frac {a_i} {b_i} \quad \text{with}\ a_i = s'_i(f g_i)^N, \ b_i = (f g_i)^{2N}
     \end{equation*}
@@
     \begin{equation*}
-        a_i b_j - a_j b_i = s'_i (fg_i)^N (fg_j)^{2N} - s'_j (fg_j)^N (fg_i)^{2N} = \underbrace{(f^2g_ig_j)^N \left(s'_i (fg_j)^N - s'_j (fg_i)^N \right)}_{= 0}
+        a_i b_j - a_j b_i = s'_i (f g_i)^N (f g_j)^{2N} - s'_j (f g_j)^N (f g_i)^{2N} = \underbrace{(f^2g_ig_j)^N \left(s'_i (fg_j)^N - s'_j (fg_i)^N \right)}_{= 0}
     \end{equation*}
@@
     \begin{equation*}
-        \eta_{\D{g/f^n}}: R_{g/f^n} \to (S_{fg})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
+        \eta_{\D{g/f^n}}: R_{g/f^n} \to (S_{f g})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
     \end{equation*}
@@
 \begin{prop}
+    \label{prop:projective_space_separated}
     The morphism $\P_R^n \to \Spec(R)$ is separated.
@@
 f_{i_{mn}}}_{\mathclap{\substack{= 0 \\ \text{as at least one $i$ repeats at least $n$ times in $i_1, ..., i_{mn}$}}}} r_{i_1} ...
-r_{i_mn}
+r_{i_{m n}}
     \end{equation*}
@@
 
-    wlog $S$ is noetherian, otherwise continue with the ring
+    wlog $S$ is Noetherian, otherwise continue with the ring
     \begin{equation*}
@@
     \end{equation*}
-    generated by the coefficients of $A/\alpha$ and $w$ (this is noetherian, as it is a quotient of a polynomial ring in finitely many variables).
+    generated by the coefficients of $A/\alpha$ and $w$ (this is Noetherian, as it is a quotient of a polynomial ring in finitely many variables).
 
     Now equip $S_{\mathfrak{l}}$ with the $\mathfrak{l}$-adic topology.
-    Note that $S$ is noetherian and local, thus the Krull intersection theorem \cite[8.41]{comalg_notes} shows that the $\mathfrak{l}$-adic topology is Hausdorff and we find
+    Note that $S$ is Noetherian and local, thus the Krull intersection theorem \cite[8.41]{comalg_notes} shows that the $\mathfrak{l}$-adic topology is Hausdorff and we find
     \begin{equation*}
@@
 
-But now enough of talking, here is the main result.
+But now enough of talking, here is the main corollary, which is also the main result of the miniproject.
 \begin{corollary}
@@
     \label{prop:valuative_criterion_properness}
-    Let $X$ be noetherian and $f: X \to Y$ a morphism of finite type.
+    Let $X$ be Noetherian and $f: X \to Y$ a morphism of finite type.
     The following are equivalent
@@
 \begin{proof}
-    Omitted, see e.g. \cite[II.4.7]{hartshorne} or \citestacks{01NH}.
+    Omitted, see e.g. \cite[II.4.7]{hartshorne} or \citestacks{0BX5}.
 \end{proof}
@@
     commutes.
-    Note that $\Spec(K) = \{ \langle 0 \rangle \}$, so let $\xi_1 \in X$ be the image of $\langle 0 \rangle$ under $\Spec(K) \to X$.
+    Note that $\Spec(K) = \{ \langle 0 \rangle \}$, so let $\xi \in X$ be the image of $\langle 0 \rangle$ under $\Spec(K) \to X$.
     Since $\langle x_0, ..., x_n \rangle \not\subseteq \xi$, there is $x_i \not\in \xi$.
@@
     Thus all $f_j$ are homogeneous of degree 1 with $\langle f_j \ | \ j \rangle = \langle x_0, ..., x_n \rangle$.
-    It follows that $X = \bigcup_j \D{f_j}$ is a cover by affine opens such that $\xi_1 \in \bigcap_j \D{f_j}$.
-    Now possibly apply a linear automorphism $f_j \to x_j$ and thus assume wlog that $f_j = x_j$.
+    It follows that $X = \bigcup_j \D{f_j}$ is a cover by affine opens such that $\xi \in \bigcap_j \D{f_j}$.
+    Now possibly apply a linear automorphism $f_j \to x_j$, so have wlog $f_j = x_j$.
     In particular, find $x_j \in \O_{X, \xi_1}^*$.
 
-    The morphism $\Spec(K) \to X$ now gives an inclusion $k(\xi_1) \subseteq K$.
-    Since $x_j \in \O_{X, \xi_1}^*$, observe that $g_{ij} := x_i / x_j \in K$ is well-defined and nonzero with $g_{ij} g_{jk} = g_{ik}$.
+    The morphism $\Spec(K) \to X$ now gives an inclusion $k(\xi) \subseteq K$.
+    Since $x_j \in \O_{X, \xi}^*$, observe that $g_{ij} := x_i / x_j \in K$ is well-defined and nonzero with $g_{ij} g_{jk} = g_{ik}$.
 
@@
     \begin{equation*}
-        \Z\left[ \frac {x_0} {x_k}, ..., \frac {x_n} {x_k} \right] \to R, \quad \frac {x_j} {x_k} \mapsto g_{ik}
+        \Z\left[ \frac {x_0} {x_k}, ..., \frac {x_n} {x_k} \right] \to R, \quad \frac {x_j} {x_k} \mapsto g_{i k}
     \end{equation*}
-    that is compatible with the field inclusion $k(\xi_1) \subseteq K$.
+    that is compatible with the field inclusion $k(\xi) \subseteq K$.
 
@@
 
-    Also it is not too hard to show that the morphism is unique, and the claim follows.
+    It is not hard to show that the morphism is unique\footnote{In fact, the statement that there is at most one such morphism is equivalent to $\P_R^n \to \Spec(R)$ being separated (by \citestacks{01L0}), so follows from Proposition~\ref{prop:projective_space_separated}.}, and the claim follows.
 \end{proof}

### 2022-03-26 Schemes/submission.tex
Replaced name by candidate number
Played around some more with schemes

@@
 \title{Miniproject - Introduction to Schemes}
-\author{Simon Pohmann}
+\author{Candidate Number: 1059926}
 
@@
 
-First of all, we will start with a reminder on graded rings, as they are the fundamental object used in the $\Proj$-construction.
+First of all, we introduce the fundamental object used in the $\Proj$-construction.
 \begin{definition}
-    A \emph{graded ring} $S$ is a ring $S$ with a decomposition\footnote{We use the convention that $0 \in \N$.} $S = \oplus_{d \in \N} S_d$ into subgroups $S_i \subseteq S$ (w.r.t.
-addition in $S$) such that $S_i \cdot S_j \subseteq S_{i + j}$ for all $i, j \in \Z$.
+    A \emph{graded ring}\footnote{
+        Unlike most authors, we consider graded rings with homogeneous elements of negative degree (i.e. not naturally graded rings), so that we can talk about the grading of a localization.
+        Namely, if $T \subseteq S$ is a multiplicative subset containing only homogeneous elements of a graded ring $S$, then $T^{-1}S$ has the canonical grading given by $\deg(f/t) = \deg(f) - \deg(t)$.
+    } $S$ is a ring $S$ with a decomposition $S = \oplus_{d \in \Z} S_d$ into subgroups $S_i \subseteq S$ (w.r.t. addition in $S$) such that $S_i \cdot S_j \subseteq S_{i + j}$ for all $i, j \in \Z$.
+    We call $S$ \emph{naturally graded}, if $S_i = \{ 0 \}$ for $i < 0$.
     Write further $S_+ := \sum_{d \neq 0} S_d$.
@@
 \end{definition}
-From now on let $S$ be a graded ring.
+From now on let $S$ be a naturally graded ring.
 \begin{definition}
-    Define the set
+    Define the \emph{projective spectrum} $\Proj(S)$ as all homogeneous prime ideals that do not contain the ``irrelevant ideal'' $S_+$
     \begin{equation*}
@@
     \end{equation*}
-    of homogeneous prime ideals not containing $S_+$.
-
     This becomes a topological space by endowing it with the \emph{Zariski-topology} on $\Proj(S)$, given by the open sets
@@
 \end{proof}
-As opposed to Hartshorne \cite{hartshorne}, we follow an approach to construct a sheaf of rings on $\Proj(S)$ will be similar to the construction of $\Spec(R)$.
-In particular, we will define $\O_{\Proj(S)}$ on a basis of the topology, and extend it to a sheaf.
+As opposed to Hartshorne \cite{hartshorne}, our approach to construct a sheaf of rings on $\Proj(S)$ will be similar to the construction of $\Spec(R)$, i.e.
+we will first specify $\O_{\Proj(S)}$ on a topological basis.
 This is also the definition used in \citestacks{01M6}.
-IT will be somewhat more tedious, but gives a nice idea of how $\O_{\Proj(S)}(U)$ looks like.
 \begin{lemma}
@@
     for all $n \in \Z$.
-
     Let now $d$ resp. $e$ be maximal such that $f_d \notin \p'$ resp. $g_e \notin \p'$.
@@
 \end{proof}
-The next proof works exactly as the corresponding one for $\Spec$ in the lecture.
 \begin{prop}

### 2022-03-28 Elliptic Curves/submission.tex
Started schemes
Fixed Elliptic Curves 3i and found examples for 2ii

@@
 \usepackage{tikz}
+\usepackage{thmtools}
 \usepackage{hyperref}
@@
 \maketitle
+\listoftheorems
 
@@
 For the next exercise, we first summarize the techniques we have used above.
-\begin{prop}
+\begin{prop}[Existence of points over $\Z_p$]
     \label{prop:p_adic_points_techniques}
@@
 This already shows that we do not have to worry to much about the condition $E(\Z_p) \neq \{\O\}$ for $p \neq 2, 3, 5, 7$ prime, as we expect that it is fulfilled quite often.
-This gives the following condition.
-\begin{prop}
-    Let $f_0, f_1, f_2 \in \Z$ and consider the Elliptic Curve $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$.
-    Let $p \in \{3, 5, 7\}$.
-    Then there is no $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ if and only if
-    \begin{align*}
-        p = 3 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 0, 2 \mod 3 \\
-        p = 5 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 0, 2, 3 \mod 5 \\
-        p = 7 \ \Rightarrow \ n^3 + f_2 n^2 + f_1 n + f_0 &\equiv 0, 3, 5, 6 \mod 7
-    \end{align*}
-    for all $n \in \Z$.
-
-    In particular, this is necessary for $E$ to satisfy the desired properties, i.e. there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ if and only if $p \neq 3, 5, 7$
-    \footnote{I understood the task here to be ``if and only if''. As mentioned later, this interpretation is probably wrong, and I will discuss the other case next.}.
-\end{prop}
-\begin{proof}
-    Let $p \in \{3, 5, 7\}$.
-    Assume there is some $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_p), x, y \in \Z$ with $\tilde{y} \neq 0$.
-    Then have
-    \begin{equation*}
-        y^2 \equiv x^3 + f_2 x^2 + f_1 x + f_0 \mod p
-    \end{equation*}
-    and so $x^3 + f_2 x^2 + f_1 x + f_0$ is a quadratic residue modulo $p$.
-
-    By checking all elements in $\F_3$, $\F_5$ and $\F_7$, one finds
-    \begin{align*}
-        \text{$n$ quadratic residue modulo $3$} \ &\Leftrightarrow \ n \equiv 0, 1 \mod 3 \\
-        \text{$n$ quadratic residue modulo $5$} \ &\Leftrightarrow \ n \equiv 0, 1, 4 \mod 5 \\
-        \text{$n$ quadratic residue modulo $7$} \ &\Leftrightarrow \ n \equiv 0, 1, 4, 2 \mod 7
-    \end{align*}
-    Except for $n \equiv 0 \mod p$, these cases have been excluded by assumption.
-    However we assumed that $y \not\equiv 0 \mod p$, so $y^2 \not\equiv 0 \mod p$ and the claim follows.
-
-    The other direction follows by reversing the above computation.
-    The claim now follows from Proposition~\ref{prop:p_adic_points_techniques}.
-\end{proof}
-However, there is one problem here.
-Using a computer, one can easily find (e.g. by trying all possibilities) that there are no $f_0, f_1, f_2 \in \Z$ such that the above conditions are (simultaneously) fulfilled for $3$, $5$ and $7$.
+My next try was to characterize in which cases there is no $(x, y) \in E(\Z_p)$, $|y|_p = 1$.
+However it turns out that this never happens simultaneously for $p \in \{ 3, 5, 7 \}$ (which was how I understood the question at first).
+On the other hand, I also found the following strengthening of the previous statement that completely finishes the case $p \geq 11$.
+\begin{equation*}
+    n^3 + f_2 n^2 + f_1 n + f_0 \equiv a_1, ..., a_l \mod p
+\end{equation*}
+for all $n \in \Z$ is equivalent to the same condition for $n \in \{ 0, ..., p - 1 \}$.
+Further, each condition is linear
 This seems to indicate that I have indeed misunderstood the task, and we only look for Elliptic Curves $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$ such that there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ for every $p \neq 3, 5, 7$, and do not require further properties for $E(\Z_3), E(\Z_5)$ and $E(\Z_7)$.
@@
 This only case that can fail is $p = 2$, but here, the condition is fulfilled quite often, so we can just try different choices.
+Using a small brute force search then yields the following examples.
 \begin{example}
@@
 
-    Note that the usual approach to bound the size of $E_{\mathrm{tors}}(\Q)$ is use to the theorem that this embeds into $\tilde{E}(\F_p)$ whenever $\tilde{E}$ is an Elliptic Curve.
+    Note that the usual approach to bound the size of $E_{\mathrm{tors}}(\Q)$ is to use the theorem that this embeds into $\tilde{E}(\F_p)$ whenever $\tilde{E}$ is an Elliptic Curve.
     However, for this example, this was not sufficient, as we could not find a prime such that the group $\Z/4\Z \oplus \Z/2\Z$ does not embed into $\tilde{E}(\F_p)$.
@@
 \end{prop}
-\begin{prop}
+\begin{proof}
+    Consider the tangent at $P = (a, b)$.
+    Differentiating the equation of $E$ gives
+    \begin{equation*}
+        2y\frac {dy} {dx} = 3x^2 + 2a_2x + a_4
+    \end{equation*}
+    so it has slope
+    \begin{equation*}
+        \lambda = \frac {3a^2 + 2a_2a + a_4} {2b}
+    \end{equation*}
+    and the equation $y = \lambda (x - a) + b$.
+    Note that after plugging this into the equation for $E$, the quadratic term has the coefficient $a_2 - \lambda^2$, so
+    \begin{align*}
+        x([2]P) &= \lambda^2 - a_2 - 2 x(P) = \frac {(3x(P)^2 + 2a_2x(P) + a_4)^2} {4b^2} - a_2 - 2 x(P) \\
+        &= \frac {(3x(P)^2 + 2a_2x(P) + a_4)^2} {4(x(P)^3 + a_2 x(P)^2 + a_4 x(P) + a_6)} - a_2 - 2 x(P)
+    \end{align*}
+    Expanding this yields the claimed expression.
+\end{proof}
+\begin{prop}[Reductions mod $p$ are not enough]
+    \label{prop:subgroup_mod_every_p}
     Let $E: y^2 = x(x + 1)(x - 8)$ be the Elliptic Curve from the previous example.
@@
 \begin{lemma}
+    \label{prop:condition_z4_subgroup_mod_p}
     Let $E: y^2 = x(x - \alpha)(x - \beta)$ be an Elliptic Curve over a field $k$ of characteristic $\neq 2$.
-    Then there exists $P \in E(k)$ of order 4 if and only if $k$ has a root of the polynomial $F(T)$ given by
-    \begin{equation*}
-        \left(T^4 + 2(\alpha + \beta)T^2 + (\alpha - \beta)^2\right)\left(T^4 + (2\beta - 4\alpha)T^2 + \beta^2\right)\left(T^4 + (2\alpha - 4\beta)T^2 + \alpha^2\right)
-    \end{equation*}
+    Then there exists $P \in E(k)$ of order 4 if and only if at least one of the following is true
+    \begin{itemize}
+        \item there is $\gamma \in k$ with $\gamma^2 = \alpha\beta$ and $2\gamma - \alpha - \beta$ is square in $k$
+        \item there is $\gamma \in k$ with $\gamma^2 = \alpha(\alpha - \beta)$ and $2\gamma + 2\alpha - \beta$ is square in $k$
+        \item there is $\gamma \in k$ with $\gamma^2 = \beta(\beta - \alpha)$ and $2\gamma + 2\beta - \alpha$ is square in $k$
+    \end{itemize}
 \end{lemma}
@@
 
-    \paragraph{Case 1} If there is $\mu \in \F_p$ with $\mu^4 + 2(\alpha + \beta)\mu^2 + (\alpha - \beta)^2 = 0$.
-
-    Then note that there is $\gamma := \frac 1 2 (\mu^2 - \alpha - \beta)$ such that $\gamma^2 = \alpha\beta$.
+    \paragraph{Case 1} By assumption, there is $\gamma, \mu \in k$ with $\gamma^2 = \alpha\beta$ and $\mu^2 = 2\gamma + \alpha + \beta$.
     Thus
@@
     \end{equation*}
-    since $\mu^2 = 2\gamma - \alpha - \beta$.
     So there is a point $(\gamma, \gamma\mu) \in E(k)$ with $[2](\gamma, \mu) = (0, 0)$.
 
-    \paragraph{Case 2} If there is $\mu \in k$ with $\mu^4 + (2\beta - 4\alpha)\mu^2 + \beta^2 = 0$.
-
-    Then note that there is $\gamma := \frac 1 2 (\mu^2 + \beta)$ such that $\gamma^2 - 2\alpha\gamma + \alpha\beta = 0$.
+    \paragraph{Case 2} By assumption, there is $\gamma_0, \mu \in k$ with $\gamma_0^2 = \alpha(\alpha - \beta)$ and $\mu^2 = 2\gamma_0 + 2\alpha - \beta$.
+    Let $\gamma := \alpha + \gamma_0$.
+    Then note that $\gamma^2 - 2\alpha\gamma + \alpha\beta = 0$.
     Thus
@@
     \end{align*}
-    as $\mu^2 = 2\gamma - \beta$ and $(\gamma - \alpha)^2 = 2\alpha\gamma - \alpha\beta - 2\gamma\alpha + \alpha^2 = \alpha(\alpha - \beta)$.
     So there is a point $(\gamma, (\gamma - \alpha)\mu) \in E(k)$ with $[2](\gamma, (\gamma - \alpha)\mu) = (\alpha, 0)$.
 
-    \paragraph{Case 3} Similarly, if there is $\mu \in k$ with $\mu^4 + (2\alpha - 4\beta)\mu^2 + \alpha^2 = 0$, then there is a point $P \in E(k)$ with $[2]P = (\beta, 0)$
-\end{proof}
-Hence, we just have to find $\alpha, \beta \in \Q$ such that the polynomial $F$ has no root in $\Q$ and a root in every $\F_p$ (where $p$ is a prime of good reduction).
-First, note that $F(T) = G(T^2)$ where
-\begin{equation*}
-    G(T) = \left( T^2 + 2(\alpha + \beta)T + (\alpha - \beta)^2 \right)\left( T^2 + (2\beta - 4\alpha)T + \beta^2 \right)\left( T^2 + (2\alpha - \beta)T + \alpha^2 \right)
-\end{equation*}
-Since the cases where this has a root in $\Q$ are clearly a Zariski-closed condition on $(\alpha, \beta)$, we see that ``most'' value of $\alpha, \beta$ will result in no root of $F(T)$.
-Hence, we focus on finding $\alpha, \beta \in \Z$ such that $F(T)$ has a root modulo any prime $p$ (of good reduction).
-A necessary condition for that is that $G(T)$ has a root modulo any prime $p$, which in turn is equivalent that any of the discriminants (scaled by squares)
-\begin{equation*}
-    \alpha\beta, \ (\alpha - 3\beta)(\alpha - \beta), \ (\beta - 3\alpha)(\beta - \alpha)
-\end{equation*}
-is a quadratic residue modulo $p$, for any prime $p$.
+    \paragraph{Case 3} Exactly as in the previous case, by swapping $\alpha$ and $\beta$.
+
+    The direction $\Leftarrow$ follows by distinguishing the cases $[2]P = (0, 0)$, $[2]P = (\alpha, 0)$ and $[2]P = (\beta, 0)$ and then reversing the above computation.
+\end{proof}
+\begin{lemma}
+    \label{prop:condition_double_square}
+    Let $k$ be a field of characteristic $\neq 2$ and $\alpha, \beta \in k$.
+    \begin{itemize}
+        \item there is $\gamma \in k$ with $\gamma = \alpha\beta$ and $2\gamma - \alpha - \beta$ square in $k$ if $-\alpha$ and $-\beta$ are squares in $k$.
+        \item there is $\gamma \in k$ with $\gamma = \alpha(\alpha - \beta)$ and $2\gamma + 2\alpha - \beta$ square in $k$ if $\alpha$ and $\alpha - \beta$ are squares in $k$.
+        \item there is $\gamma \in k$ with $\gamma = \beta(\beta - \alpha)$ and $2\gamma + 2\beta - \alpha$ square in $k$ if $\beta$ and $\beta - \alpha$ are squares in $k$.
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    Consider $\mu, \rho \in k$ with $\mu^2 = -\alpha$ and $\rho^2 = -\beta$.
+    Then $\gamma := \mu\rho$ satisfies $\gamma^2 = \alpha\beta$ and
+    \begin{equation*}
+        (\mu + \rho)^2 = \mu^2 + 2\mu\rho + \rho^2 = 2\gamma -\alpha - \beta
+    \end{equation*}
+    Consider now $\mu, \rho \in k$ with $\mu^2 = \alpha$ and $\rho^2 = \alpha - \beta$.
+    Then $\gamma := \mu\rho$ satisfies $\gamma^2 = \alpha(\alpha - \beta)$ and
+    \begin{equation*}
+        (\mu + \rho)^2 = \mu^2 + 2\mu\rho + \rho^2 = 2\gamma + 2\alpha - \beta
+    \end{equation*}
+    The third claim follows in the same way, by swapping $\alpha$ and $\beta$.
+\end{proof}
+\begin{example}
+    Let $p$ be a prime.
+    Taking the set of ``exhaustive cases'' given by $p(-1) = -p$ similar to the proof of Proposition~\ref{prop:subgroup_mod_every_p}.
+    In other words, take $\alpha, \beta \in \Z$ such that $-\alpha, -p\beta$ and $\beta - \alpha$ are squares (in $\Z$).
+    Then we find for any prime $q$
+    \begin{itemize}
+        \item If $p$ is a quadratic residue mod $q$, then $-\alpha$ and $-\beta$ are
+        \item If $-1$ is a quadratic residue mod $q$, then $\alpha$ and $\alpha - \beta$ are
+        \item If $-p$ is a quadratic residue mod $q$, then $\beta$ and $\beta - \alpha$ are
+    \end{itemize}
+    Hence, by Lemma~\ref{prop:condition_z4_subgroup_mod_p} and Lemma~\ref{prop:condition_double_square}, we see that every reduction $\tilde{E}(\F_q)$ of the Elliptic Curve $E: y^2 = x(x - \alpha)(x - \beta)$ (where $q$ is a prime of good reduction) contains a point of order 4.
+    Thus $\Z/4\Z \times \Z/2\Z \hookrightarrow \tilde{E}(\F_q)$.
+\end{example}
+\begin{example}
+    Consider the Elliptic Curve $E: y^2 = x(x + 4)(x + 3)$.
+    Then $-(-4)$, $(-3)(-3)$ and $-3 - (-4) = 1$ are square, thus $\Z/4\Z \times \Z/2\Z \hookrightarrow \tilde{E}(\F_p)$ for every prime $p$ of good reduction.
+    Furthermore, $E(\Q)$ does not have a point of order $4$ by Lemma~\ref{prop:condition_z4_subgroup_mod_p}, since $(-3)(-4) = 12$ and $(-3)(-3 - (-4)) = 3$ are no squares and also $2\gamma + 2(-4) - (-3) = -5 \pm 2 \cdot 2$ is not a square, where $\gamma^2 = (-4)(-4 - (-3)) = 4$.
+\end{example}
 
@@
     Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
-    Suppose that $E$ has a nontrivial 5-torsion point $P = (\alpha_1, \beta_1) \in E(k)$.
-    wlog $\alpha_1 = 0$.
+    Suppose that $E$ has a nontrivial 5-torsion point\footnote{As remarked upon later, focusing on case that the $x$-coordinate is zero is not a real restriction.} $P = (0, \beta) \in E(k)$.
     Let further $(\alpha_2, \beta_2) = [2](0, \beta)$.
@@
 \begin{proof}
-    Consider the following SAGE script:
+    Note that the assumptions
+    \begin{align*}
+        (0, \beta) &\in E, \\
+        (\alpha_2, \beta_2) &\in E, \\
+        [2](0, \beta) &= (\alpha_2, \beta_2), \\
+        [2](\alpha_2, \beta_2) &= (0, -\beta)
+    \end{align*}
+    can all be expressed via roots of polynomials, and also the claimed statement is of this form.
+    Hence, the problem reduces to checking that $\alpha_2^3 + 4\beta\beta_2$ is contained in the ideal $I$ generated by the polynomials giving the assumptions (in the polynomial ring $k[a_2, a_4, a_6, \beta, \alpha_2, \beta_2]$).
+    Using Gröbner-basis methods, this can easily be done using a computer.  
+    So consider the following SAGE script:
     \lstinputlisting[language = python]{./3i_algebra.sage}
-    The output shows that $\alpha_2^3 = -4 \beta \beta_2$ already follows from the facts
-    \begin{align*}
-        &(0, \beta) \in E, \\
-        &(\alpha_2, \beta_2) \in E, \\
-        &[2](0, \beta) = (\alpha_2, \beta_2), \\
-        &[2](\alpha_2, \beta_2) = (0, -\beta)
-    \end{align*}
-    which hold by assumption that $(0, \beta)$ has order $5$.
-    The claim follows.
+    The output prints \lstinline{True} and so the statement holds for $k = \Q$.
+    Thus, there are $g_1, ..., g_n \in I$ and $s_1, ..., s_n \in \Q[a_2, a_4, a_6, \beta, \alpha_2, \beta_2]$ such that
+    \begin{equation*}
+        \alpha_2^3 + 4\beta\beta_2 = \sum_i g_i s_i
+    \end{equation*}
+    Since the generators of $I$ and $\alpha_2^3 + 4\beta\beta_2$ have coefficients in $\Z$, we can also choose $r_i, s_i$ to have coefficients in $\Z$.
+    Now note that there is a homomorphism $\Z \to k$ for every field $k$, and so the statement holds in an arbitrary field $k$.
 \end{proof}
 \begin{lemma}
-    Let
-    \begin{equation*}
-        E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2 + a_4 x + a_6    
-    \end{equation*}
-    and
-    \begin{equation*}
-        E': y^2 + a'_1 x y + a'_3 y = x^3 + a'_2 x^2 + a'_4 x + a'_6    
-    \end{equation*}
-    be Elliptic Curves.
-    If there are five distinct points $P_1, ..., P_5 \in E \cap E'$ in ``sufficiently independent position'', then $E = E'$ (meaning $a_i = a'_i$).
-
-    To be completely precise, there is a fixed 1-dimensional algebraic curve $C \subseteq \mathbb{A}^{10}$ (that does not depend on $E$, $E'$ or $P_1, ..., P_5$) of degree $6$ such that if there are five points $P_1 = (x_1, y_1), ..., P_5 = (x_5, y_5) \in E \cap E'$ with
-    \begin{equation*}
-        (x_1, ..., x_5, y_1, ..., y_5) \notin C
-    \end{equation*}
-    then $E = E'$.
+    \label{prop:share_subgroup_equal}
+    Let $E, E'$ be Elliptic Curves, and assume they share a cyclic subgroup of order $n \geq 5$\footnote{Technically, we can also allow infinite order here.}.
+    With this, we mean there is a point $P \in E \cap E'$ of order $n$ such that
+    \begin{equation*}
+        G := \langle P \rangle_E \subseteq E' \quad \text{and} \quad \restr{+_E}{G} = \restr{+_{E'}}{G}
+    \end{equation*}
+    Then $E = E'$ (in the sense that they have the same defining equation).
 \end{lemma}
 \begin{proof}
-    Consider the matrix $A = (a_{ij}) \in k[x_1, ..., x_5, y_1, ..., y_5]^{5 \times 5}$ given by
-    \begin{equation*}
-        a_{ij} = \begin{cases}
-            x_i^{j - 1} & \text{if $j \leq 3$} \\
-            -x_iy_i & \text{if $j = 4$} \\
-            -y_i & \text{if $j = 5$}
-        \end{cases}
-    \end{equation*}
-    Let $C = \V(\det(A))$ and assume there are five points $P_1 = (x_1, y_1), ..., P_5(x_5, y_5) \in E \cap E'$.
-    Then the matrix $A_P := A(x_1, ..., x_5, y_1, ..., y_5) \in k^{5 \times 5}$ is regular.
-    Since $P_1, ..., P_5 \in E \cap E'$, see that
-    \begin{equation*}
-        A_P (a_6 \ \ a_4 \ \ a_2 \ \ a_1 \ \ a_3)^T = (y_1^2 x_1^3 \ \ ... \ \ y_5^2 x_5^3)^T
-    \end{equation*}
-    and
-    \begin{equation*}
-        A_P (a'_6 \ \ a'_4 \ \ a'_2 \ \ a'_1 \ \ a'_3)^T = (y_1^2 x_1^3 \ \ ... \ \ y_5^2 x_5^3)^T
-    \end{equation*}
-    Thus by linear algebra, find that $E = E'$.
+    Consider some point $[i] P = (a, b) \in E \cap E'$.
+    With $P' = (a', b') := -[2i] P \in E \cap E'$ we see that $P + P + P' = \O$ and so $P, P, P'$ are colinear\footnote{We mean that the line through $P$ and $P'$ meets $E$ resp.
+$E'$ at $P$ with multiplicity 2.}.
+    In particular, the tangent on $E$ resp. on $E'$ at $P \in E \cap E'$ both have the slope $(b - b')/(a - a')$\footnote{Or infinity if $a = a'$, but importantly, the slopes are equal.}.
+
+    Since $P$ has order at least 5, observe that $P, [2]P, [3]P, [4]P$ and $[5]P$ are all different.
+    Furthermore, since $E$ and $E'$ have the same tangent slope at each $[i] P$, note that $E$ meets $E'$ in $[i] P$ with multiplicity 2.
+    So $E$ meets $E'$ in at least 10 points (counting multiplicity), which is greater than the product of their degrees $9 = 3 \cdot 3$.
+    By Bezout's theorem, it follows that $E$ and $E'$ share an irreducible component of dimension $\geq 1$, but since both are Elliptic Curves, they are irreducible of dimension $1$ and so $E = E'$.
 \end{proof}
@@
     \label{prop:characterization_5_torsion}
-    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
+    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over a field $k$ of characteristic $\neq 2$.
     Suppose that $E$ has a nontrivial 5-torsion point $P = (0, \beta) \in E(k)$.
@@
 \begin{proof}
+    First note that the above values are well-defined, as by assumption, $(0, \beta)$ has order 5 (in particular $\neq 2$), thus $\beta \neq 0$.
+    Furthermore, we have that $(\alpha_2, \beta_2) = [2]P \neq \pm P$ (since $P$ has order 5), and since $\pm P = \pm (0, \beta)$ are the only (affine) points on $E$ with $x$-coordinate $0$, we see that $\alpha_2 \neq 0$.
+
     Clearly $\psi$ maps $E$ to an Elliptic Curve $E''$.
@@
     \end{equation*}
-
     Under $\psi$, we now see that
     \begin{equation*}
-        (0, \ \beta) \mapsto (0, u^3 \beta + t) = \left( 0, \ \frac {\beta} {2\beta_2} - \frac {\beta} {2\beta_2} \right) = (0, 0) \in E'
+        (0, \ \beta) \mapsto (0, u^3 \beta + t) = \left( 0, \ \frac {\beta} {2\beta_2} - \frac {\beta} {2\beta_2} \right) = (0, 0)
     \end{equation*}
@@
         (\alpha_2, \ \beta_2) \mapsto (u^2 \alpha_2, \ u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(\frac {\alpha_2^3} {4\beta^2}, \ \frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
-        &= \left( -\frac {\beta_2} {\beta}, \ \frac {\beta_2^2} {\beta^2} \right) = (-v, \ v^2) \in E'
+        &= \left( -\frac {\beta_2} {\beta}, \ \frac {\beta_2^2} {\beta^2} \right) = (-v, \ v^2)
     \end{align*}
@@
     \begin{align*}
-        (\alpha_2, \beta_2) \mapsto (u^2 \alpha_2, \ -u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(\frac {\alpha_2^3} {4\beta^2}, \ -\frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
-        &= ( -\frac {\beta_2} {\beta}, \ 0) = (-v, \ 0) \in E'
+        (\alpha_2, -\beta_2) \mapsto (u^2 \alpha_2, \ -u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(\frac {\alpha_2^3} {4\beta^2}, \ -\frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
+        &= ( -\frac {\beta_2} {\beta}, \ 0) = (-v, \ 0)
     \end{align*}
@@
     \begin{align*}
-        (0, \ -\beta) \mapsto (0, -u^3 \beta + t) = \left( 0, \ -\frac {\beta_2} {2\beta} - \frac {\beta_2} {2\beta} \right) = (0, \ -v) \in E'
+        (0, \ -\beta) \mapsto (0, -u^3 \beta + t) = \left( 0, \ -\frac {\beta_2} {2\beta} - \frac {\beta_2} {2\beta} \right) = (0, \ -v)
     \end{align*}
     and of course $\O \mapsto \O$.
-    Hence we have $\#(E' \cap E'') \geq 5$ and by the previous proposition we see that $E' = E''$.
+
+    Now note that in $E'$, we have
+    \begin{equation*}
+        [2](0, 0) = (-v, v^2) = \psi(\alpha_2, \beta_2), \quad [4](0, 0) = [2](-v, v^2) = (0, -v) = \psi(0, -\beta)
+    \end{equation*}
+    and so
+    \begin{equation*}
+        [5](0, 0) = \O = \psi(\O), \quad [3](0, 0) = -[2](0, 0) = (-v, 0) = \psi(\alpha_2, -\beta_2) 
+    \end{equation*}
+    Hence $\psi(E)$ and $E'$ share the subgroup $\{ (0, 0), (-v, v^2), (-v, 0), (0, -v), \O \}$ and must be equal by Lemma~\ref{prop:share_subgroup_equal}.
 \end{proof}
@@
     \end{equation*}
-    For example by the duplication formula~\ref{prop:duplication_formula} find that
+    As above, find that
     \begin{equation*}
@@
 \end{itemize}
-Hence, we are quite limited for $N$ a similar idea can work.
+Hence, there are not many $N$ for which a similar idea can work.
 First, note that the case $N = 2$ is easy.
-\begin{prop}[3(ii)]
+\begin{prop}[3(ii) - $2$-torsion points]
     Let $E$ be an Elliptic Curve defined over $\Q$.
@@
 \end{prop}
+\begin{proof}
+    Just plug the equation of the isomorphism into the equation defining the $E'$, and check that it is zero modulo the equation of $E$.
+\end{proof}
 Now we can find a nice form for Elliptic Curves with a (nontrivial) 3-torsion point by the following step:

### 2022-03-28 Elliptic Curves/submission.tex
Found better proof for 3i

@@
 
-    Now consider any prime $p \neq 2, 3$ and $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_p), x, y \in \Z$.
+    Now consider any prime $p \neq 2, 3$ and $(\tilde{x}, \tilde{y}) \in \tilde{E}(\F_p), x, y \in \Z, \tilde{y} \neq 0$.
     Let $f(t) := t^2 - x^3 - 2x - 2$.
@@
 On the other hand, I also found the following strengthening of the previous statement that completely finishes the case $p \geq 11$.
-\begin{equation*}
-    n^3 + f_2 n^2 + f_1 n + f_0 \equiv a_1, ..., a_l \mod p
-\end{equation*}
-for all $n \in \Z$ is equivalent to the same condition for $n \in \{ 0, ..., p - 1 \}$.
-Further, each condition is linear
-This seems to indicate that I have indeed misunderstood the task, and we only look for Elliptic Curves $E: y^2 = x^3 + f_2 x^2 + f_1 x + f_0$ such that there is $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ for every $p \neq 3, 5, 7$, and do not require further properties for $E(\Z_3), E(\Z_5)$ and $E(\Z_7)$.
-
-So instead consider a strengthening of the last part of Proposition~\ref{prop:p_adic_points_techniques}.
 \begin{prop}
@@
 Using a small brute force search then yields the following examples.
-\begin{example}
+\begin{example}[1(iv)]
     Let
@@
 \end{proof}
-\begin{example}
+\begin{example}[2(ii) - Additional Examples]
     Let $p$ be a prime.
@@
 \section{Question 3}
-\begin{lemma}
-    \label{prop:relation_y_uv}
-    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
-    Suppose that $E$ has a nontrivial 5-torsion point\footnote{As remarked upon later, focusing on case that the $x$-coordinate is zero is not a real restriction.} $P = (0, \beta) \in E(k)$.
-    Let further $(\alpha_2, \beta_2) = [2](0, \beta)$.
-    Then
-    \begin{equation*}
-        \alpha_2^3 = -4\beta\beta_2
-    \end{equation*}
-\end{lemma}
-\begin{proof}
-    Note that the assumptions
-    \begin{align*}
-        (0, \beta) &\in E, \\
-        (\alpha_2, \beta_2) &\in E, \\
-        [2](0, \beta) &= (\alpha_2, \beta_2), \\
-        [2](\alpha_2, \beta_2) &= (0, -\beta)
-    \end{align*}
-    can all be expressed via roots of polynomials, and also the claimed statement is of this form.
-    Hence, the problem reduces to checking that $\alpha_2^3 + 4\beta\beta_2$ is contained in the ideal $I$ generated by the polynomials giving the assumptions (in the polynomial ring $k[a_2, a_4, a_6, \beta, \alpha_2, \beta_2]$).
-    Using Gröbner-basis methods, this can easily be done using a computer.  
-    So consider the following SAGE script:
-    \lstinputlisting[language = python]{./3i_algebra.sage}
-    The output prints \lstinline{True} and so the statement holds for $k = \Q$.
-    Thus, there are $g_1, ..., g_n \in I$ and $s_1, ..., s_n \in \Q[a_2, a_4, a_6, \beta, \alpha_2, \beta_2]$ such that
-    \begin{equation*}
-        \alpha_2^3 + 4\beta\beta_2 = \sum_i g_i s_i
-    \end{equation*}
-    Since the generators of $I$ and $\alpha_2^3 + 4\beta\beta_2$ have coefficients in $\Z$, we can also choose $r_i, s_i$ to have coefficients in $\Z$.
-    Now note that there is a homomorphism $\Z \to k$ for every field $k$, and so the statement holds in an arbitrary field $k$.
-\end{proof}
+First, we first look at some basic transformations we can do to Weierstraß equations.
+This will be our main toolkit for this exercise.
+\begin{prop}[Weierstraß transformations]
+    \label{prop:weierstrass_transformations}
+    Let $E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
+    There are three nice types of transformations
+    \begin{description}
+        \item[Translation] Let $P = (s, t) \in E(k)$ be a point. Then the isomorphism
+        \begin{equation*}
+            E \to E', \quad (x, y) \mapsto (x - s, y - t)
+        \end{equation*}
+        maps $P$ to $(0, 0)$ and the curve $E$ to an Elliptic Curve
+        \begin{equation*}
+            E': y^2 + a_1 x y + (a_3 + 2t + a_1 s) y = x^3 + (a_2 + 3 s) x^2 + (a_4 - 3 s^2 + 2 a_2 s - a_1 t) x
+        \end{equation*}
+        This is very useful to clear $a_6$ and continue working with the point $(0, 0)$.
+        \item[Shearing] Let $r \in k$. Then the isomorphism
+        \begin{equation*}
+            E \to E', \quad (x, y) \mapsto (x, y - r x)
+        \end{equation*}
+        preserves $(0, 0)$ and maps $E$ to an Elliptic Curve
+        \begin{equation*}
+            E': y^2 + (a_1 + 2r) x y + a_3 y = x^3 + (a_2 + r^2 - a_1 r) x^2 + (a_4 - r a_3) x + a_6
+        \end{equation*}
+        This is very useful, as it does not change $a_3$ and $a_6$.
+        \item[Scaling] Let $u \in k^*$. Then the isomorphism
+        \begin{equation*}
+            E \to E', \quad (x, y) \mapsto (u^2 x, y^3 y)
+        \end{equation*}
+        preserves $(0, 0)$ and maps $E$ to an Elliptic Curve
+        \begin{equation*}
+            E': y^2 + \frac {a_1} u x y + \frac {a_3} {u^3} = x^3 + \frac {a_2} {u^2} x^2 + \frac {a_4} {u^4} x + \frac {a_6} {u^6}
+        \end{equation*}
+        This is very useful, as it does not change which of the $a_1, ..., a_4, a_6$ are zero.
+    \end{description}
+\end{prop}
+\begin{proof}
+    Just plug the equation of the isomorphism into the equation defining the $E'$, and check that it is zero modulo the equation of $E$.
+\end{proof}
+\begin{corollary}
+    \label{prop:point_normalization}
+    Let $E$ be an Elliptic Curve defined over $k$ with a $k$-rational point $P$ that is not a 2-torsion point.
+    Then there is a linear isomorphism $\psi: E \to E'$ mapping $E$ to an Elliptic Curve of the form
+    \begin{equation*}
+        E': y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2
+    \end{equation*}
+    such that $\psi(P) = (0, 0)$, the tangent at $(0, 0)$ is given by $y = 0$.
+    Furthermore $[2](0, 0) = (-a_2, a_1 a_2 - a_3)$.
+\end{corollary}
+\begin{proof}
+    After a translation by $-P$, we may assume that
+    \begin{equation*}
+        E: y^2 + a'_1 x y + a'_3 y = x^3 + a'_2 x^2 + a'_4 x
+    \end{equation*}
+    and $P = (0, 0)$.
+    Now observe that if $a'_3 = 0$, the line $x = 0$ through $(0, 0)$ and $\O$ meets $E$ in $(0, 0)$ with multiplicity 2, and so $(0, 0) + \O = (0, 0)$, contradicting the assumption that $P$ is not a 2-torsion point.
+    Thus $a'_3 \neq 0$ and a shearing with $r = a'_4 / a'_3$ maps $E$ to
+    \begin{equation*}
+        E': y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2
+    \end{equation*}
+    Note that the tangent at $(0, 0)$ now has slope $0$, i.e. is given by $y = 0$.
+    Furthermore, the third point of intersection of the tangent and $E$ is $(-a_2, 0)$.
+    The line through $\O$ and $(-a_2)$ is given by $x = -a_2$ and its third point of intersection with $E$ is then $(-a_2, a_1a_2 - a_3)$. 
+\end{proof}
+I came up with the next lemma to make my first proof of 3(i) work.
+Since then, I have found a simpler proof that does not require the lemma anymore, but I found it beautiful and did not want to delete it.
 \begin{lemma}
     \label{prop:share_subgroup_equal}
-    Let $E, E'$ be Elliptic Curves, and assume they share a cyclic subgroup of order $n \geq 5$\footnote{Technically, we can also allow infinite order here.}.
+    Let $E, E'$ be Elliptic Curves defined over any field $k$, and assume they share a cyclic subgroup of order $n \geq 5$\footnote{Technically, we can also allow infinite order here.}.
     With this, we mean there is a point $P \in E \cap E'$ of order $n$ such that
@@
 \end{proof}
-\begin{prop}
-    \label{prop:characterization_5_torsion}
-    Let $E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over a field $k$ of characteristic $\neq 2$.
-    Suppose that $E$ has a nontrivial 5-torsion point $P = (0, \beta) \in E(k)$.
-    Let further $[2]P = (\alpha_2, \beta_2)$ and note that $0 \neq \alpha_2$.
-    Then there exists a birational equivalence $E \to E'$ where $E': y^2 + (1 + v) x y + v y = x^3 + v x^2$ given by
-    \begin{equation*}
-        \psi: E \to E', \quad (x, y) \mapsto (u^2 x, u^3 y + u^2 s x + t)
-    \end{equation*}
-    with
-    \begin{equation*}
-        v = \frac {\beta_2} {\beta}, \quad t = -\frac {\beta_2} {2\beta}, \quad u = -\frac {\alpha_2} {2\beta}, \quad s = \frac {u} {\alpha_2} ( \beta_2 + \beta )
-    \end{equation*}
-\end{prop}
-\begin{proof}
-    First note that the above values are well-defined, as by assumption, $(0, \beta)$ has order 5 (in particular $\neq 2$), thus $\beta \neq 0$.
-    Furthermore, we have that $(\alpha_2, \beta_2) = [2]P \neq \pm P$ (since $P$ has order 5), and since $\pm P = \pm (0, \beta)$ are the only (affine) points on $E$ with $x$-coordinate $0$, we see that $\alpha_2 \neq 0$.
-
-    Clearly $\psi$ maps $E$ to an Elliptic Curve $E''$.
-    Note that by assumption, we have
-    \begin{align*}
-        &[1](0, \beta) = (0, \beta), \quad [2](0, \beta) = (\alpha_2, \beta_2), \\
-        &[3](0, \beta) = -[2](0, \beta) = (\alpha_2, -\beta_2), \quad [4](0, \beta) = -[1](0, \beta) = (0, -\beta)
-    \end{align*}
-    By Lemma~\ref{prop:relation_y_uv} we have that $\alpha_2^3 = -4\beta\beta_2$ and so
-    \begin{equation*}
-        u^3 = \left( -\frac {\alpha_2} {2\beta} \right)^3 = -\frac {\alpha_2^3} {8\beta^3} = \frac {4\beta\beta_2} {8\beta^3} = \frac {\beta_2} {2\beta^2}
-    \end{equation*}
-    Under $\psi$, we now see that
-    \begin{equation*}
-        (0, \ \beta) \mapsto (0, u^3 \beta + t) = \left( 0, \ \frac {\beta} {2\beta_2} - \frac {\beta} {2\beta_2} \right) = (0, 0)
-    \end{equation*}
-    and
-    \begin{align*}
-        (\alpha_2, \ \beta_2) \mapsto (u^2 \alpha_2, \ u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(\frac {\alpha_2^3} {4\beta^2}, \ \frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
-        &= \left( -\frac {\beta_2} {\beta}, \ \frac {\beta_2^2} {\beta^2} \right) = (-v, \ v^2)
-    \end{align*}
-    and
-    \begin{align*}
-        (\alpha_2, -\beta_2) \mapsto (u^2 \alpha_2, \ -u^3 \beta_2 + u^2 s \alpha_2 + t) &= \left(\frac {\alpha_2^3} {4\beta^2}, \ -\frac {\beta_2^2} {2\beta^2} + \frac {\beta_2} {2\beta} \left( \frac {\beta_2} {\beta} + 1 \right) - \frac {\beta_2} {2\beta} \right) \\
-        &= ( -\frac {\beta_2} {\beta}, \ 0) = (-v, \ 0)
-    \end{align*}
-    and
-    \begin{align*}
-        (0, \ -\beta) \mapsto (0, -u^3 \beta + t) = \left( 0, \ -\frac {\beta_2} {2\beta} - \frac {\beta_2} {2\beta} \right) = (0, \ -v)
-    \end{align*}
-    and of course $\O \mapsto \O$.
-
-    Now note that in $E'$, we have
-    \begin{equation*}
-        [2](0, 0) = (-v, v^2) = \psi(\alpha_2, \beta_2), \quad [4](0, 0) = [2](-v, v^2) = (0, -v) = \psi(0, -\beta)
-    \end{equation*}
-    and so
-    \begin{equation*}
-        [5](0, 0) = \O = \psi(\O), \quad [3](0, 0) = -[2](0, 0) = (-v, 0) = \psi(\alpha_2, -\beta_2) 
-    \end{equation*}
-    Hence $\psi(E)$ and $E'$ share the subgroup $\{ (0, 0), (-v, v^2), (-v, 0), (0, -v), \O \}$ and must be equal by Lemma~\ref{prop:share_subgroup_equal}.
-\end{proof}
-\begin{corollary}[3(i)]
+\begin{prop}[3(i)]
     Let $E$ be an Elliptic Curve defined over $\Q$.
@@
     \end{equation*}
-\end{corollary}
-\begin{proof}
-    Note that $E$ is isomorphic (over $\Q$) to an Elliptic Curve defined by a Weierstraß equation, so assume wlog
-    \begin{equation*}
-        E: y^2 = x^3 + a_2 x^2 + a_4 x + a_6
-    \end{equation*}
-    Now let $P = (\alpha, \beta)$ be a nontrivial 5-torsion point.
-    Then $E$ is isomorphic via $(x, y) \mapsto (x - \alpha, \beta)$ to an Elliptic Curve
-    \begin{equation*}
-        E': y^2 = x^3 + a'_2 x^2 + a'_4 x
-    \end{equation*}
-    and $(0, \beta)$ is a nontrivial 5-torsion point of $E'$.
-    The claim follows now by Proposition~\ref{prop:characterization_5_torsion}.
-
-    Conversely, assume that
-    \begin{equation*}
-        E: y^2 + (v + 1) x y + v y = x^3 + v x^2
-    \end{equation*}
-    As above, find that
-    \begin{equation*}
-        [2](0, 0) = (-v, v^2), \quad [2](-v, v^2) = (0, -v)
-    \end{equation*}
-    and thus $[4](0, 0) + (0, 0) = \O$, hence $(0, 0)$ has order 5.
+\end{prop}
+\begin{proof}
+    By Corollary~\ref{prop:point_normalization}, we can assume that $E$ is given as
+    \begin{equation*}
+        E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2
+    \end{equation*}
+    and $(0, 0)$ is a 5-torsion point of $E$ such that the tangent at $(0, 0)$ on $E$ is given by $y = 0$.
+    Further, have $[2](0, 0) = (-a_2, a_1 a_2 - a_3)$.
+    After applying a scaling, assume further that $a_2 = a_3$.
+    Now define $\beta = a_2(a_1 - 1)$.
+    Thus $[2](0, 0) = (-a_2, \beta)$.
+    By computing the third point of intersection between $E$ and the lines $x = 0$ resp. $x = -a_2$ we see that 
+    \begin{equation*}
+        [3](0, 0) = -[2](0, 0) = (-a_2, 0), \quad [4](0, 0) = (0, -a_3)
+    \end{equation*}
+    Now consider the tangent at $[2](0, 0) = (-a_2, \beta)$.
+    It has slope
+    \begin{align*}
+        \lambda =& \frac {3 a_2^2 - 2 a_2^2 - a_1 \beta} {2\beta - a_1 a_2 + a_3} = \frac {a_2^2 - a_1\beta} \beta = \frac {a_2^2 - a_1a_2(a_1 - 1)} \beta = \frac {(a_2 - a_1(a_1 - 1))a_2} {a_2(a_1 - 1)} \\
+        =& \frac {a_2 - a_1(a_1 - 1)} {a_1 - 1} = \frac {a_2} {a_1 - 1} - a_1
+    \end{align*}
+    Since $[4](-a_2, \beta) = [4](0, 0) = -(0, 0)$, observe that $(0, 0)$ must be a point on the tangent $y = \lambda (x + a_2) + \beta$.
+    Thus $\lambda a_2 + \beta = 0$ and so
+    \begin{equation*}
+        \frac {a_2^2} {a_1 - 1} - a_1 a_2 + a_2(a_1 - 1) = 0
+    \end{equation*}
+    Clearly $a_2 \neq 0$ and thus
+    \begin{equation*}
+        0 = a_2 - a_1 (a_1 - 1) + (a_1 - 1)^2 = a_2 - a_1 - 1
+    \end{equation*}
+    So $a_1 = a_2 + 1$ and the claim follows with $v = a_2 = a_3$.
 \end{proof}
@@
 The case $N = 3$ is slightly more interesting.
-For this, we first look at some basic transformations we can do to Weierstraß equations.
-\begin{prop}
-    \label{prop:weierstrass_transformations}
-    Let $E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2 + a_4 x + a_6$ be an Elliptic Curve defined over $k$.
-    There are three nice types of transformations
-    \begin{description}
-        \item[Translation] Let $P = (s, t) \in E(k)$ be a point. Then the isomorphism
-        \begin{equation*}
-            E \to E', \quad (x, y) \mapsto (x - s, y - t)
-        \end{equation*}
-        maps $P$ to $(0, 0)$ and the curve $E$ to an Elliptic Curve
-        \begin{equation*}
-            E': y^2 + a_1 x y + (a_3 + 2t + a_1 s) y = x^3 + (a_2 + 3 s) x^2 + (a_4 - 3 s^2 + 2 a_2 s - a_1 t) x
-        \end{equation*}
-        This is very useful to clear $a_6$ and continue working with the point $(0, 0)$.
-        \item[Shearing] Let $r \in k$. Then the isomorphism
-        \begin{equation*}
-            E \to E', \quad (x, y) \mapsto (x, y - r x)
-        \end{equation*}
-        preserves $(0, 0)$ and maps $E$ to an Elliptic Curve
-        \begin{equation*}
-            E': y^2 + (a_1 + 2r) x y + a_3 y = x^3 + (a_2 + r^2 - a_1 r) x^2 + (a_4 - r a_3) x + a_6
-        \end{equation*}
-        This is very useful, as it does not change $a_3$ and $a_6$.
-        \item[Scaling] Let $u \in k^*$. Then the isomorphism
-        \begin{equation*}
-            E \to E', \quad (x, y) \mapsto (u^2 x, y^3 y)
-        \end{equation*}
-        preserves $(0, 0)$ and maps $E$ to an Elliptic Curve
-        \begin{equation*}
-            E': y^2 + \frac {a_1} u x y + \frac {a_3} {u^3} = x^3 + \frac {a_2} {u^2} x^2 + \frac {a_4} {u^4} x + \frac {a_6} {u^6}
-        \end{equation*}
-        This is very useful, as it does not change which of the $a_1, ..., a_4, a_6$ are zero.
-    \end{description}
-\end{prop}
-\begin{proof}
-    Just plug the equation of the isomorphism into the equation defining the $E'$, and check that it is zero modulo the equation of $E$.
-\end{proof}
-Now we can find a nice form for Elliptic Curves with a (nontrivial) 3-torsion point by the following step:
+Our approach is as follows:
 \begin{itemize}
-    \item Apply a translation to get an isomorphic curve whose (nontrivial) 3-torsion point is $(0, 0)$.
+    \item Apply a translation to get an isomorphic curve whose (nontrivial) 3-torsion point is $(0, 0)$ and the tangent is given by $y = 0$.
     \item Observe that $(0, 0)$ being a 3-torsion point is equivalent to the fact that the tangent at $E$ through $(0, 0)$ meets $E$ at $(0, 0)$ with multiplicity three.
-    \item Apply clever shearing and scaling to get a nice form. Note that this does not destroy the fact $a_6 = 0$.
+    \item Show that after a scaling, the resulting equation is nice.
 \end{itemize}
 Now we get
-\begin{prop}
+\begin{prop}[3(ii) - 3-torsion points]
     Let $E$ be an Elliptic Curve defined over $\Q$.
@@
 \begin{proof}
-    By Proposition~\ref{prop:weierstrass_transformations} we can assume wlog that
-    \begin{equation*}
-        E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2 + a_4 x
+    By Corollary~\ref{prop:point_normalization} we can assume wlog that
+    \begin{equation*}
+        E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2
     \end{equation*}
     and $(0, 0) \in E(\Q)$ is a nontrivial 3-torsion point.
-    Now a shearing with $r = a_4 / a_3$ transforms $E$ into an Elliptic Curve
-    \begin{equation*}
-        E': y^2 + a'_1 x y + a'_3 y = x^3 + a'_2 x^2
-    \end{equation*}
-    Observe that $(0, 0)$ is still a nontrivial 3-torsion point of $E'(\Q)$.
-
-    Now note that the tangent at $(0, 0)$ has slope $m = a'_4/a'_3 = 0$.
-    Hence, since $-[2](0, 0) = (0, 0)$ is the third point of intersection of $E'$ and the tangent, we see that the tangent meets $E'$ at $(0, 0)$ with multiplicity three.
+
+    Now note that the tangent at $(0, 0)$ has slope $m = 0/a_3 = 0$.
+    Hence, since $-[2](0, 0) = (0, 0)$ is the third point of intersection of $E$ and the tangent, we see that the tangent meets $E$ at $(0, 0)$ with multiplicity three.
     Thus
     \begin{equation*}
-        x^3 + a'_2 x^2 
-    \end{equation*}
-    must already be $x^3$ and thus have $a'_2 = 0$.
-    Finally, apply a scaling with $u = a'_1$ (note that $a'_1 \neq 0$, otherwise the curve would be singular) and find that $E$ is isomorphic to the curve
-    \begin{equation*}
-        E'': y^2 + x y + v y = x^3
-    \end{equation*}
-    where $v = a'_3 / (a'_1)^3$.
+        x^3 + a_2 x^2 
+    \end{equation*}
+    must already be $x^3$ and thus have $a_2 = 0$.
+    Finally, apply a scaling with $u = a_1$ (note that $a_1 \neq 0$, otherwise the curve would be singular) and find that $E$ is isomorphic to the curve
+    \begin{equation*}
+        E': y^2 + x y + v y = x^3
+    \end{equation*}
+    where $v = a_3 / (a_1)^3$.
 

### 2022-03-28 Elliptic Curves/submission.tex
Added new possibly unnecessary proposition

@@
     Let $E$ be an Elliptic Curve defined over $k$ with a $k$-rational point $P$ that is not a 2-torsion point.
-    Then there is a linear isomorphism $\psi: E \to E'$ mapping $E$ to an Elliptic Curve of the form
+    Then there is an Elliptic Curve $E'$ and a linear isomorphism $\psi: E \to E'$ such that $P \mapsto (0, 0)$ and the tangent at $(0, 0)$ on $E'$ is given by the equation $y = 0$.
+
+    Furthermore $E'$ is given by an equation of the form
     \begin{equation*}
@@
     \end{equation*}
-    such that $\psi(P) = (0, 0)$, the tangent at $(0, 0)$ is given by $y = 0$.
-    Furthermore $[2](0, 0) = (-a_2, a_1 a_2 - a_3)$.
+    and $[2](0, 0) = (-a_2, a_1 a_2 - a_3)$.
 \end{corollary}
@@
 \end{proof}
+A similar approach works also for 4-torsion points.
+\begin{prop}(3(ii) - 4-torsion points)
+    Let $E$ be an Elliptic Curve defined over $\Q$.
+    Then $E(\Q)$ has a nontrivial 4-torsion point if and only if $E$ is isomorphic (over $\Q$) to an Elliptic Curve given by an equation of the form
+    \begin{equation*}
+        y^2 + x y + v y = x^3 + v x^2
+    \end{equation*}
+\end{prop}
+\begin{proof}
+    Again, by Corollary~\ref{prop:point_normalization}, assume wlog that
+    \begin{equation*}
+        E: y^2 + a_1 x y + a_3 y = x^3 + a_2 x^2
+    \end{equation*}
+    and $(0, 0) \in E(\Q)$ is a nontrivial 4-torsion point.
+    Find that $[2](0, 0) = (-a_2, \beta)$ where $\beta = a_1 a_2 - a_3$.
+    The tangent at $(-a_2, \beta)$ must have the equation $x = -a_2$ since $(-a_2, \beta)$ is 2-torsion by assumption.
+    Thus
+    \begin{equation*}
+        0 = 2\beta - a_1a_2 + a_3 = \beta
+    \end{equation*}
+    and so $a_1a_2 = a_3$.
+    By scaling with $a_1$ (which is nonzero, otherwise $a_3 = 0$ and the curve is singular), observe that $E$ is isomorphic to the curve
+    \begin{equation*}
+        E': y^2 + x y + v y = x^3 + v x^2
+    \end{equation*}
+    where $v = a_3 / a_1^3 = a_2 / a_1^2$.
+
+    Conversely, assume that $E$ is isomorphic to an Elliptic Curve of the above form, so wlog
+    \begin{equation*}
+        E: y^2 + x y + v y = x^3 + v x^2
+    \end{equation*}
+    We show that $(0, 0) \in E(\Q)$ has order $4$.
+    The tangent has slope $0$, so is given by the line $y = 0$.
+    The third point of intersection with $E$ is now $(-v, 0)$.
+    Note that the line through $(-v, 0)$ and $\O$ has the equation $x = -v$ and meets $E$ at $(-v, 0)$ with multiplicity 2.
+    It follows that $(-v, 0)$ is a 2-torsion point, and so $E(\Q)$ has the point $(0, 0)$ of order 4.
+\end{proof}
+Now we strengthen Corollary~\ref{prop:point_normalization} somewhat more.
+\begin{lemma}
+    Let $E$ be an Elliptic Curve defined over $\Q$ with a $\Q$-rational point $P$ that is not a 2-torsion point.
+    Then there exists a unique Elliptic Curve $E'$ and a linear isomorphism\footnote{the isomorphism is only unique up to composition with an automorphism of $E'$.} $\psi: E \to E'$ such that $P \mapsto (0, 0)$ and $E'$ is given by an equation of the form
+    \begin{equation*}
+        E': y^2 + x y + a_3 y = x^3 + a_2 x^2
+    \end{equation*}
+
+    In this case have that the tangent at $(0, 0)$ is given by $y = 0$ and $[2](0, 0) = (-a_2, a_1 a_2 - a_3)$.
+\end{lemma}
+\begin{proof}
+    Existence holds by Corollary~\ref{prop:point_normalization} and applying a scaling by $u = a_1$ (note that this is $\neq 0$, otherwise the curve would be singular).
+
+    So we have to show uniqueness.
+    Assume there is a second curve
+    \begin{equation*}
+        E'': y^2 + x y + a'_3 = x^3 + a'_2 x^2
+    \end{equation*}
+    and a linear isomorphism $\psi': E \to E''$ mapping $P \to (0, 0)$.
+    Then we find a linear isomorphism
+    \begin{equation*}
+        E' \to E'', \quad (x, y) \mapsto (u^2 x + r, u^3 y + u^2 s x + t)
+    \end{equation*}
+    Note that it must map $(0, 0) \mapsto (0, 0)$, thus $r = t = 0$.
+    Plugging this into the equation of $E''$, we get
+    \begin{equation*}
+        G := -u^6 x^3 + u^4 s^2 x^2 + 2 u^5 s x y + u^6 y^2 + u^4 s x^2 - u^4 a'_2 x^2 + u^5 x y + u^2 a'_3 s x + u^3 a'_3 y
+    \end{equation*}
+    This must be zero modulo $F = y^2 + x y + a_3 y - x^3 - a_2 x^2$.
+    By a simple degree argument, observe that $G - u^6F$ must already be zero in $\Q[x, y]$.
+    Grouping coefficients of $G - u^6F$, we see that
+    \begin{align*}
+        &u^2 a'_3 s = 0 \\
+        &u^6 a_2 + u^4 s^2 + u^4 s - u^4 a'_2 = 0 \\
+        -&u^6 a_3 + u^3 a'_3 = 0 \\
+        -&u^6 + 2 u^5 s + u^5 = 0
+    \end{align*}
+    Note that $u \neq 0$, so $a'_3 s = 0$.
+    Note that $s \neq 0$, otherwise the isomorphism is just a scaling, and in this case, it must already be the identity.
+    Thus $s = 0$ and we find
+    \begin{align*}
+        &u^2 a_2 - a'_2 = 0 \\
+        -&u^3 a_3 + a'_3 = 0 \\
+        -&u + 1 = 0
+    \end{align*}
+    So $u = 1$ and $a_2 = a'_2$, $a_3 = a'_3$.
+    This shows that $E' = E''$ and then the isomorphisms $\psi, \psi'$ must be equal up to composition with an automorphism in $E'$.
+\end{proof}
 
 \section{Question 4}
-
 Let $S = \{ x^2 \ | \ x \in \Q^* \}$.

### 2022-03-29 Elliptic Curves/submission.tex
Added references

@@
     \begin{equation*}
-        |162^2 + 6|_5 = |26250|_5 = |5^4 \cdot 7 \cdot 2 \cdot 3|_5 = 5^{-4} < 5^{-3}
-    \end{equation*}
+        |463^2 + 6|_5 = |214375|_5 = |5^4 \cdot 7^3|_5 = 5^{-4} < 5^{-3}
+    \end{equation*}
+    To find it, note that $|2^2 + 6|_5 < 1$ and use Newton's method.
+    Set $x_0 = 2$ and have
+    \begin{align*}
+        x_1 = x_0 - \frac {x_0^2 + 6} {2x_0} = 2 - \frac {10} {4} = -\frac 1 2  \\
+        x_2 = -\frac 1 2 - \frac {1/4 + 6} {-1} = \frac {25} 4 - \frac 1 2 = \frac {23} 4
+    \end{align*}
+    and indeed, $|(23/4)^2 + 6|_5 = |625/16|_5 = 5^{-4}$.
+    Since the valuation $|\cdot|_5$ is non-Archimedian, observe that $|x^2 + 6|_5 < 5^{-3}$ holds for all $x \in \Q$ with $|x - 32/4|_5 = |4x - 32|_5 < 5^{-3}$.
+    Hence, we look for $x \in \Z$ such that $5^4 \divides 4x + 23$.
+    In other words, find $k \in \Z$ with $4 \divides k 5^4 - 23$, i.e. $k - 3 \equiv 0 \mod 4$.
+    We find $k = 3$ and so $x = 463$.
 \end{example}
@@
     If $p \equiv 1, 5 \mod 8$, then $-1$ is a square in $\F_p$, thus there is $\alpha \in \F_p$ with $\alpha^2 = -1$ and so $(-1, \alpha) \in \tilde{E}(\F_p)$.
-    If $p \equiv 7 \mod 8$, then (by Quadratic Reciprocity) it follows that $2$ is a square in $\F_p$.
+    If $p \equiv 7 \mod 8$, then (the law of Quadratic Reciprocity, e.g. \cite[Prop. I.8.6]{neukirch}) it follows that $2$ is a square in $\F_p$.
     Thus there is $\alpha \in \F_p$ with $\alpha^2 = 2$ and so $(0, \alpha) \in \tilde{E}(\F_p)$.
@@
     Hence we see that $p \notdivides \Delta(E)$ and so $\tilde{E}$ is an Elliptic Curve defined over $\F_p$.
-    Now the Hasse bound shows that
+    Now the Hasse bound \cite[Thm 1.15]{lecture} shows that
     \begin{equation*}
@@
     \end{equation*}
-    and so Hensel's Lemma yields a point $(5, \gamma) \in E(\Z_2)$.
+    and so Hensel's Lemma \cite[Thm 2.14]{lecture} yields a point $(5, \gamma) \in E(\Z_2)$.
 
@@
     \end{equation*}
-    Hensel's Lemma now shows that there is $\gamma \in \Z_p$ such that $\gamma^2 = x^3 + a_2 x^2 + a_4 x + a_6$ and so $(x, \gamma) \in E(\Z_p)$.
+    Hensel's Lemma now \cite[Thm 2.14]{lecture} shows that there is $\gamma \in \Z_p$ such that $\gamma^2 = x^3 + a_2 x^2 + a_4 x + a_6$ and so $(x, \gamma) \in E(\Z_p)$.
     Since $|y|_p = 1$ clearly also $|\gamma|_p = 1$.
@@
 
-    For the fourth part, note that as above, $p > 9$ implies $\sqrt{p} < p/3$ and so the Hasse bound yields (since $\tilde{E}$ is an Elliptic Curve by assumption, as $p \notdivides \Delta(E)$)
+    For the fourth part, note that as above, $p > 9$ implies $\sqrt{p} < p/3$ and so the Hasse bound \cite[Thm 1.15]{lecture} yields (since $\tilde{E}$ is an Elliptic Curve by assumption, as $p \notdivides \Delta(E)$)
     \begin{equation*}
@@
     \end{align*}
-    so Hensel's Lemma yields points $(x, y) \in E_i(\Z_2)$ with $|y|_2 = 1$ for $i \in \{1, 2, 3\}$.
+    so Hensel's Lemma yields \cite[Thm 1.15]{lecture} points $(x, y) \in E_i(\Z_2)$ with $|y|_2 = 1$ for $i \in \{1, 2, 3\}$.
     By Proposition~\ref{prop:points_in_EZp}, we have points $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ for all $p \geq 11$.
@@
     Consider the Elliptic Curve $E: y^2 = x(x + 1)(x + 4)$ defined over $\Q$.
-    Have
-    \begin{equation*}
-        x(x + 1)(x + 4) = x^3 + 5x^2 + 4x = \left( x + \frac 5 3 \right)^3 - \frac {13} 3 \left( x + \frac 5 3 \right) + \frac {70} {27}
-    \end{equation*}
-    So $E$ is isomorphic to $E': y^2 = x^3 - \frac {13} 3 x + \frac {70} {27}$ via
-    \begin{equation*}
-        \psi: E \to E', \quad (x, y) \mapsto \left( x + \frac 5 3, y \right)
-    \end{equation*}
-    This isomorphism preserves the group structure\footnote{It is a general result that all isogenies are group homomorphisms, but in this case, it is also directly obvious as the isomorphism is linear, hence maps lines to lines.}, and so $E'_{\mathrm{tors}} \cong E_{\mathrm{tors}}$.
-    Have
-    \begin{equation*}
-        \Delta(E') = 4 \left( -\frac {13} 3 \right)^3 + 27 \left( \frac {70} {27} \right)^2 = -144 = \Delta(E)
-    \end{equation*}
-    Consider now any prime $p \neq 2, 3$.
-    Then the isomorphism $\psi: E \to E'$ induces an isomorphism $\tilde{\psi}: \tilde{E} \to \tilde{E}'$ between the reductions modulo $p$.
-    Note that $\tilde{E}, \tilde{E}'$ are still Elliptic Curves.
-
-    Hence, we can use results from the lecture on the reduction modulo $p \neq 2, 3$ for the curve $E$, even though it is not given by an equation of the form $y^2 = x^3 + Ax + B$, as all these statements are preserved under isomorphism.
-    In particular, we see that the kernel of reduction $E_1(\Q_5)$ has no torsion and so there is an embedding
+    Note that the reduction $\tilde{E}$ modulo 5 is still an Elliptic Curve, as the roots $0, 1, 4$ are distinct modulo 5.
+    By \cite[Lemma 5.1]{lecture}, there is an embedding
     \begin{equation*}
@@
     Unlike the previous example however, this time the former is the case.
-    To see this, we use the Nagell-Lutz theorem.
+    To see this, we use the Nagell-Lutz theorem \cite[5.4]{lecture}.
     Assume $(x, y) \in E_{\mathrm{tors}}(\Q)$ with $y \neq 0$.
@@
 \end{proof}
-\begin{example}[2(ii) - Additional Examples]
+\begin{example}
     Let $p$ be a prime.
@@
 \end{example}
-\begin{example}
+\begin{example}[2(ii) - Additional Examples]
     Consider the Elliptic Curve $E: y^2 = x(x + 4)(x + 3)$.
@@
     \begin{equation*}
-        G := \langle P \rangle_E \subseteq E' \quad \text{and} \quad \restr{+_E}{G} = \restr{+_{E'}}{G}
+        G := \langle P \rangle_E \subseteq E' \quad \text{and} \quad \restr{+_E}{G \times G} = \restr{+_{E'}}{G \times G}
     \end{equation*}
@@
     So $E$ meets $E'$ in at least 10 points (counting multiplicity), which is greater than the product of their degrees $9 = 3 \cdot 3$.
-    By Bezout's theorem, it follows that $E$ and $E'$ share an irreducible component of dimension $\geq 1$, but since both are Elliptic Curves, they are irreducible of dimension $1$ and so $E = E'$.
+    By Bezout's theorem \cite[Corollary I.7.8]{hartshorne}, it follows that $E$ and $E'$ share an irreducible component of dimension $\geq 1$, but since both are Elliptic Curves, they are irreducible of dimension $1$ and so $E = E'$.
 \end{proof}
@@
 A similar approach works also for 4-torsion points.
-\begin{prop}(3(ii) - 4-torsion points)
+\begin{prop}[3(ii) - 4-torsion points]
     Let $E$ be an Elliptic Curve defined over $\Q$.
@@
 \end{proof}
-Now we strengthen Corollary~\ref{prop:point_normalization} somewhat more.
-\begin{lemma}
-    Let $E$ be an Elliptic Curve defined over $\Q$ with a $\Q$-rational point $P$ that is not a 2-torsion point.
-    Then there exists a unique Elliptic Curve $E'$ and a linear isomorphism\footnote{the isomorphism is only unique up to composition with an automorphism of $E'$.} $\psi: E \to E'$ such that $P \mapsto (0, 0)$ and $E'$ is given by an equation of the form
-    \begin{equation*}
-        E': y^2 + x y + a_3 y = x^3 + a_2 x^2
-    \end{equation*}
-
-    In this case have that the tangent at $(0, 0)$ is given by $y = 0$ and $[2](0, 0) = (-a_2, a_1 a_2 - a_3)$.
-\end{lemma}
-\begin{proof}
-    Existence holds by Corollary~\ref{prop:point_normalization} and applying a scaling by $u = a_1$ (note that this is $\neq 0$, otherwise the curve would be singular).
-
-    So we have to show uniqueness.
-    Assume there is a second curve
-    \begin{equation*}
-        E'': y^2 + x y + a'_3 = x^3 + a'_2 x^2
-    \end{equation*}
-    and a linear isomorphism $\psi': E \to E''$ mapping $P \to (0, 0)$.
-    Then we find a linear isomorphism
-    \begin{equation*}
-        E' \to E'', \quad (x, y) \mapsto (u^2 x + r, u^3 y + u^2 s x + t)
-    \end{equation*}
-    Note that it must map $(0, 0) \mapsto (0, 0)$, thus $r = t = 0$.
-    Plugging this into the equation of $E''$, we get
-    \begin{equation*}
-        G := -u^6 x^3 + u^4 s^2 x^2 + 2 u^5 s x y + u^6 y^2 + u^4 s x^2 - u^4 a'_2 x^2 + u^5 x y + u^2 a'_3 s x + u^3 a'_3 y
-    \end{equation*}
-    This must be zero modulo $F = y^2 + x y + a_3 y - x^3 - a_2 x^2$.
-    By a simple degree argument, observe that $G - u^6F$ must already be zero in $\Q[x, y]$.
-    Grouping coefficients of $G - u^6F$, we see that
-    \begin{align*}
-        &u^2 a'_3 s = 0 \\
-        &u^6 a_2 + u^4 s^2 + u^4 s - u^4 a'_2 = 0 \\
-        -&u^6 a_3 + u^3 a'_3 = 0 \\
-        -&u^6 + 2 u^5 s + u^5 = 0
-    \end{align*}
-    Note that $u \neq 0$, so $a'_3 s = 0$.
-    Note that $s \neq 0$, otherwise the isomorphism is just a scaling, and in this case, it must already be the identity.
-    Thus $s = 0$ and we find
-    \begin{align*}
-        &u^2 a_2 - a'_2 = 0 \\
-        -&u^3 a_3 + a'_3 = 0 \\
-        -&u + 1 = 0
-    \end{align*}
-    So $u = 1$ and $a_2 = a'_2$, $a_3 = a'_3$.
-    This shows that $E' = E''$ and then the isomorphisms $\psi, \psi'$ must be equal up to composition with an automorphism in $E'$.
-\end{proof}
+\begin{example}[3(ii) - Additional Examples]
+    Consider the Elliptic Curve
+    \begin{equation*}
+        E: y^2 + x y + y = x^3
+    \end{equation*}
+    defined over $\Q$.
+    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve (If $3x^2 + y = 2y + 1 + x = 0$ then $y^2 - y - 1 = 0$, so $y = -1$ and $x = 1$.
+However $(1, -1) \notin \tilde{E}(\F_3)$).
+    Trying all values in $\F_3^2$, we find
+    \begin{equation*}
+        \tilde{E}(\F_3) = \{ (0, 0), (0, 2), \O \} 
+    \end{equation*}
+    Clearly $E(\Q)$ has the 3-torsion point $(0, 0)$, and since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_3)$ we see that
+    \begin{equation*}
+        E_{\mathrm{tors}}(\Q) = \{ (0, 0), (0, -1), \O \}
+    \end{equation*}
+\end{example}
 
@@
     \end{align*}
-    \paragraph{Find $E'(\Q)/\phi(E(\Q))$} As in the lecture, consider $r \divides 32$ square-free, i.e. $r \in \{ \pm 1, \pm 2 \}$.
+    To find the rank, we proceed as in the lecture (technically, use \cite[Lemma 6.6]{lecture}).
+
+    \paragraph{Find $E'(\Q)/\phi(E(\Q))$} Consider $r \divides 32$ square-free, i.e. $r \in \{ \pm 1, \pm 2 \}$.
 
@@
 Further requiring those points to be non-integral increases our chance, as that way, they cannot be torsion points.
-
-For rank one, this is very easy: If we find a curve with integral coefficients and at least one non-integral point, its rank must be $\geq 1$.
-Such a curve is easy to find by guessing a point and using linear algebra.
-Furthermore, if we have two points $P, Q$ whose $x$-coordinates are linearly independent in $\Q^*/S$ (as $\Z/2\Z$-module), then we already see that $\overline{P} \neq \overline{Q} \in E(\Q)/\hat{q}(E'(\Q))$ and since both are non-torsion (they have non-integral coordinates), it follows that the rank is at least 2.
-\begin{example}
-    Guess the points
-    \begin{equation*}
-        P_1 = \left(-1, \frac 1 2\right), \quad P_2 = \left(-2, \frac 1 2\right)
-    \end{equation*}
-    and consider an Elliptic Curve given by
-    \begin{equation*}
-        y^2 = x^3 + a_2 x^2 + a_4 x
-    \end{equation*}
-    If $P_1, P_2, P_3 \in E$, we must have
-    \begin{align*}
-        &-1 + a_2 - a_4 = \frac 1 4 \\
-        &-8 + 4a_2 - 2a_4 = \frac 1 4
-    \end{align*}
-    This has the solution $(a_2, a_4) = (23/8, 13/8)$.
-    Hence, we consider the curve given by
-    \begin{equation*}
-        y^2 = x^3 + \frac {23} 8 x^2 + \frac {13} 8 x
-    \end{equation*}
-    Putting it into standard form yields
-    \begin{equation*}
-        E: y^2 = x(x^2 + 46 x + 104)
-    \end{equation*}
-    Now we would like to compute the rank of this curve, however the standard method fails here.
-    The reason is that some of the equations, like
-    \begin{equation*}
-        13 l^4 + 65 l^2 m^2 + 8 m^4 = n^2
-    \end{equation*}
-    (resulting from $r = 13 \divides 104$) seem to have no integer solutions, but seem have one modulo any prime.
-
-    Note however that we find
-    \begin{equation*}
-        -l^4 + 46 l^2 m^2 - 104 m^4 = n^2 \quad \text{has solution $(l, m, n) = (2, 1, 8)$}
-    \end{equation*}
-    and
-    \begin{equation*}
-        104 l^4 + 46 l^2 m^2 + 1 m^4 = n^2 \quad \text{has solution $(l, m, n) = (0, 1, 1)$}
-    \end{equation*}
-    and
-    \begin{equation*}
-        2 l^4 + 46 l^2 m^2 + 52 m^4 = n^2 \quad \text{has solution $(l, m, n) = (1, 1, 10)$}
-    \end{equation*}
-    corresponding to the points $P_1, P_2$ and $(0, 0)$.
-
-    So we find that $(\Z/2\Z)^3 \hookrightarrow E(\Q)/[2]E(\Q)$ and since $x^2 + 46 x + 104$ has no rational roots (the discriminant $1700$ is not a perfect square), observe that $E_{\mathrm{tors}}(\Q) / [2]E(\Q) \cong \Z/2\Z$.
-    Thus
-    \begin{equation*}
-        (\Z/2\Z)^2 \hookrightarrow E_{\mathrm{torsion-free}}(\Q)/[2]E(\Q)
-    \end{equation*}
-    and $E$ has rank at least 2.
-\end{example}
-A lot of trying around shows that most curves that are generated in a ``clever'' way to satisfy nice properties (like high rank, or only few square-free $r \divides b$ resp.
-$r \divides b_1$) cause problems when computing the rank, due to resulting in hard-to-solve equations as above.
-So it would be good to find a method that generates ``nice'' curves, i.e. curves where each of the equations
-\begin{equation*}
-    r l^4 + a l^2 m^2 + \frac b r m^4 = n^4 \quad \text{resp} \quad r l^4 + a_1 l^2 m^2 + \frac {b_1} r m^4 = n^4
-\end{equation*}
-obviously has or hasn't a nontrivial solution.
-At the moment, I fail to see any elegant method to generate ``nice'' curves with desired properties.
+However, playing around with this method did not yield a nice curve where we can compute the rank.
 So lets fall back to brute force, which works quite well here as this condition is very easy to test via a computer.
@@
     \end{itemize}
-    Note that if one of the additional conditions is fulfilled for $a_1, b_1$, then we get the corresponding bound for $\mathrm{rank}(E') = \mathrm{rank}(E)$ (isogenous curves have the same rank, as isogenies have finite kernel).
+    Note that if one of the additional conditions is fulfilled for $a_1, b_1$, then we get the corresponding bound for $\mathrm{rank}(E') = \mathrm{rank}(E)$ 
+    (isogenous curves have the same rank, as isogenies are group homomorphisms with finite kernel, see \cite[Thm III.4.8]{silverman} and \cite[Corollary III.4.9]{silverman}).
 \end{prop}
@@
     we see that
-    \begin{equation*}
-        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^{m + 1} = 2^{l + m + 1}
-    \end{equation*}
+    \begin{equation}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^{m + 1} = 2^{l + m + 1} \label{eq:general_bound}
+    \end{equation}
     Finally, note that
     \begin{equation*}
-        E(\Q)[2]E(\Q) \cong E_{\mathrm{tors}}(\Q)/[2]E(\Q) \oplus (\Z/2\Z)^{\mathrm{rank}(E)}
+        E(\Q)/[2]E(\Q) \cong E_{\mathrm{tors}}(\Q)/[2]E(\Q) \oplus (\Z/2\Z)^{\mathrm{rank}(E)}
     \end{equation*}
@@
     \end{equation*}
-    Hence as before find
-    \begin{equation*}
-        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^m
-    \end{equation*}
-    and as before
+    As before find then (since $\hat{\phi}$ has a kernel of size 2)
+    \begin{equation}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^m \label{eq:sign_bound}
+    \end{equation}
+    and again as before
     \begin{equation*}
@@
     \paragraph{Assume $a \perp b$} Then have that $b_1 = (a^2 - 4b) \perp b$ and thus we find that $l + m = k$.
-    Now have again
-    \begin{equation*}
-        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^{m + 1}
-    \end{equation*}
-    and so
+    Equation~\ref{eq:general_bound} is
+    \begin{equation*}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^{m + 1} = 2^{l + m + 1}
+    \end{equation*}
+    and so it follows
     \begin{equation*}
@@
 
-    \paragraph{Assume $a \perp b$ and $a \leq 0, b \geq 0$} Now have both
-    \begin{equation*}
-        \#(E(\Q)/\hat{\phi}(E'(\Q))) \leq 2^m
+    \paragraph{Assume $a \perp b$ and $a \leq 0, b \geq 0$} Now have both Equation~\ref{eq:sign_bound}
+    \begin{equation*}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^m = 2^{m + l}
     \end{equation*}
@@
     \end{equation*}
-    Note that the square of the $y$-coordinate $3^2 = 9$ does not divide $\Delta(E) = 4 \cdot 8^3 = 2^{11}$ and so $(1, 3)$ is not torsion by the Nagell-Lutz theorem.
+    Note that the square of the $y$-coordinate $3^2 = 9$ does not divide $\Delta(E) = 4 \cdot 8^3 = 2^{11}$ and so $(1, 3)$ is not torsion by the Nagell-Lutz theorem \cite[Thm 5.4]{lecture}.
     So it is of infinite order, and we have indeed that $\mathrm{rank}(E) = 1$.
@@
 
+\printbibliography
+
 \end{document}

### 2022-03-29 Elliptic Curves/submission.tex
Finished Elliptic Curves

@@
 \title{Miniproject - Elliptic Curves}
-\author{Simon Pohmann}
+\author{Candidate Number: 1059926}
 
@@
     and indeed, $|(23/4)^2 + 6|_5 = |625/16|_5 = 5^{-4}$.
-    Since the valuation $|\cdot|_5$ is non-Archimedian, observe that $|x^2 + 6|_5 < 5^{-3}$ holds for all $x \in \Q$ with $|x - 32/4|_5 = |4x - 32|_5 < 5^{-3}$.
+    Since the valuation $|\cdot|_5$ is non-Archimedean, observe that $|x^2 + 6|_5 < 5^{-3}$ holds for all $x \in \Q$ with $|x - 32/4|_5 = |4x - 32|_5 < 5^{-3}$.
     Hence, we look for $x \in \Z$ such that $5^4 \divides 4x + 23$.
@@
 \end{example}
-
 \begin{example}[1(ii)]
@@
 for an Elliptic Curve $E$ defined over $k$ and any ring $R$ contained in the algebraic closure $\bar{k}$.
-Note that this is usually not a group anymore, and does not have a lot of nice structure.
+Note that this is in general not a group.
+However, it gives us a way to nicely phrase the next statements.
 \begin{prop}[1(iii)]
+    \label{prop:1iii}
     Consider the Elliptic Curve $E: y^2 = x^3 + 2x + 2$ defined over $\Z$.
@@
 \end{proof}
-For the next exercise, we first summarize the techniques we have used above.
+Note that the Hasse bound already yields the statement for all but finitely many primes $p$.
+So instead of arguing with Quadratic Reciprocity, we could just explicitly compute $\tilde{E}(\F_p)$ for the remaining $p$.
+For general Elliptic Curves, exactly this approach is summarized in the next proposition.
 \begin{prop}[Existence of points over $\Z_p$]
@@
 This only case that can fail is $p = 2$, but here, the condition is fulfilled quite often, so we can just try different choices.
-Using a small brute force search then yields the following examples.
-\begin{example}[1(iv)]
-    Let
-    \begin{align*}
-        E_1: \ &y^2 = x^3 + 2 x \\
-        E_2: \ &y^2 = x^3 + 2 x^2 + 6 x + 5\\
-        E_3: \ &y^2 = x^3 + 6x + 1
-    \end{align*}
-    Note that
+If we additionally want no points $(x, y) \in \tilde{E}(\F_p)$ with $y \neq 0$, then we can for example use a little bit of linear algebra.
+\begin{example}[1(iv) - first example]
+    Assume we want to find a curve $E: y^2 = f(x) := x^3 + A x + B$ such that $\tilde{E}(\F_3)$ contains no point $(x, y)$ with $y \neq 0$.
+    Then have
+    \begin{equation*}
+        f(0) = B \equiv 0, 2  \quad \text{and} \quad f(1) = 1 + A + B \equiv 0, 2
+    \end{equation*}
+    since $1$ is the only square in $\F_3^*$.
+    For example the case $B \equiv 0$ and $1 + A + B \equiv 0$ yields the solution $B = 0$, $A = 2$ which indeed does yield a curve $E$ with $\tilde{E}(\F_3) = \{ \O \}$.
+    Indeed, have that
+    \begin{equation*}
+        \tilde{E}(\F_3) = \{ (0, 0), (1, 0), (2, 0), \O \}
+    \end{equation*}
+    Furthermore, we see that
+    \begin{equation*}
+        \tilde{E}(\F_5) = \{ (0, 0), \O \}
+    \end{equation*}
+    On the other hand, note that
     \begin{align*}
         1^2 &\equiv 3^3 + 2 \cdot 3 = 33 \mod 8 \\
+        3^2 &\equiv 4^3 + 2 \cdot 4 = 72 \mod 7
+    \end{align*}
+    so Hensel's Lemma yields \cite[Thm 1.15]{lecture} points $(x, y) \in E(\Z_2)$ with $|y|_2 = 1$ and $(x', y') \in E(\Z_7)$ with $|y'|_7 = 1$.
+
+    Interestingly, if we want a curve $E$ such that $\tilde{E}(\F_3) = \{ \O \}$, then we require
+    \begin{equation*}
+        f(0) = B \equiv 2  \quad \text{and} \quad f(1) = 1 + A + B \equiv 2
+    \end{equation*}
+    and this has the only solution $A \equiv B \equiv 2$, which indeed works out (this is the curve from Proposition~\ref{prop:1iii}).
+\end{example}
+This also works for $p = 7$, as the next example shows.
+\begin{example}[1(iv) - second example]
+    Assume we want to find a curve $E: y^2 = f(x) := x^3 + a_2 x^2 + a_4 x + a_6$ such that $\tilde{E}(\F_7)$ contains no point $(x, y)$ with $y \neq 0$.
+    By considering a scaling isomorphism of the form
+    \begin{equation*}
+        E \to E', \quad (x, y) \mapsto (u^2 x, u^3 y)
+    \end{equation*}
+    we can assume wlog that $a_2 \equiv 0, 1, 2 \mod 7$ (as each element in $\F_7$ is congruent to $0, 1$ or $2$ modulo the squares $\{ x^2 \ | \ x \in \F_7 \}$).
+    Furthermore have
+    \begin{equation*}
+        f(0) = a_6 \equiv 0, 3, 5, 6, \quad f(1) = 1 + a_2 + a_4 + a_6 \equiv 0, 3, 5, 6
+    \end{equation*}
+    since $1, 4, 2$ are the squares in $\F_7^*$.
+    We find 48 possible solutions, and for example $a_2 \equiv 2, a_4 \equiv 6, a_6 \equiv 5$ works.
+    Indeed, have that
+    \begin{equation*}
+        \tilde{E}(\F_7) = \{ (1, 0), (5, 0), (6, 0), \O \}
+    \end{equation*}
+    Furthermore, note that
+    \begin{align*}
         1^2 &\equiv 2^3 + 2 \cdot 2^2 + 6 \cdot 2 + 5 = 33 \mod 8 \\
-        1^2 &\equiv 4^3 + 6 \cdot 4 + 1 = 89 \mod 8
+        1^2 &\equiv 2^3 + 2 \cdot 2^2 + 6 \cdot 2 + 5 = 33 \mod 3 \\
+        2^2 &\equiv 1^3 + 2 \cdot 1^2 + 6 \cdot 1 + 5 = 14 \mod 5
     \end{align*}
-    so Hensel's Lemma yields \cite[Thm 1.15]{lecture} points $(x, y) \in E_i(\Z_2)$ with $|y|_2 = 1$ for $i \in \{1, 2, 3\}$.
-    By Proposition~\ref{prop:points_in_EZp}, we have points $(x, y) \in E(\Z_p)$ with $|y|_p = 1$ for all $p \geq 11$.
-
-    Finally, note that trying all points shows
+    so Hensel's Lemma yields \cite[Thm 1.15]{lecture} points $(x, y) \in E(\Z_2)$ with $|y|_2 = 1$ and $(x', y') \in E(\Z_3)$ with $|y'|_3 = 1$ and $(x'', y'') \in E(\Z_5)$ with $|y''|_5 = 1$.
+\end{example}
+\begin{example}[(iv) - third example]
+    The cubic polynomial $f = x^3 + x$ has roots $0$ and $1$ modulo 2.
+    Thus the Elliptic Curve $E: y^2 = x^3 + x$ clearly has no points $(x, y) \in E(\Z_2)$ with $|y|_2 = 1$, as all points $(x, y) \in \tilde{E}(\F_2)$ satisfy $y = 0$.
+    Furthermore, see that
+    \begin{equation*}
+        \tilde{E}(\F_5) = \{ (0, 0), (2, 0), (3, 0), \O \}
+    \end{equation*}
+    and
     \begin{align*}
-        \tilde{E}_1(\F_3) &= \{ (0, 0), (1, 0), (2, 0), \O \} \\
-        \tilde{E}_1(\F_5) &= \{ (0, 0), \O \} \\
-        \tilde{E}_2(\F_7) &= \{ (1, 0), (5, 0), (6, 0), \O \}
+        1^2 &\equiv 2^3 + 2 = 10 \mod 3 \\
+        3^2 &\equiv 1^3 + 1 = 2 \mod 7
     \end{align*}
-    so there is no point $(x, y) \in E_i(\Z_p)$ with $|y|_p = 1$ for $p \in \{3, 5, 7\}$ and a suitable $i$. 
-\end{example}
+    so Hensel's Lemma yields \cite[Thm 1.15]{lecture} points $(x, y) \in E(\Z_3)$ with $|y|_3 = 1$ and $(x', y') \in E(\Z_7)$ with $|y'|_7 = 1$.
+\end{example}
+Note also that those three examples show that the bound $p \geq 11$ in Proposition~\ref{prop:points_in_EZp} is sharp.
 
@@
     The only factors of $81$ are $\pm 1, \pm 3, \pm 9, \pm 27, \pm 81$ and none solves $81 = x^3 - 7x^2 - 8x$.
-
+\end{example}
 Note that the usual approach to bound the size of $E_{\mathrm{tors}}(\Q)$ is to use the theorem that this embeds into $\tilde{E}(\F_p)$ whenever $\tilde{E}$ is an Elliptic Curve.
@@
 it is impossible to show that $\#E_{\mathrm{tors}}(\Q) \neq 8$ by just considering the reductions modulo $p$.
-\end{example}
+
 First, it is convenient to have a closed formula for the $x$-coordinate of $[2]P$ for a point $P$ on an Elliptic Curve.
@@
 \end{proof}
+Here now comes the promised statement.
 \begin{prop}[Reductions mod $p$ are not enough]
@@
 \end{proof}
+As it turns out, we can phrase each of those nested square condition by a condition that two fixed values are squares, which is much nicer to work with.
 \begin{lemma}
@@
 \end{proof}
+Combining these two lemmas, it is quite easy to generate more examples.
 \begin{example}
@@
 \end{proof}
+The next corollary will give us a ``base form'' for equations of Elliptic Curves with special torsion points. 
 \begin{corollary}
@@
 \end{proof}
+Finally we can proof the statement on 5-torsion points.
 \begin{prop}[3(i)]
@@
 \end{proof}
-In the lecture, it was mentioned that a theorem of Mazur states that the torsion group of an Elliptic Curve $E$ defined over $\Q$ has one of the following forms
-\begin{itemize}
-    \item $\Z/n\Z$ for $n \in \{ 1, ..., 10, 12 \}$
-    \item $\Z/n\Z \oplus \Z/2\Z$ for $n \in \{ 2, 4, 6, 8 \}$
-\end{itemize}
-Hence, there are not many $N$ for which a similar idea can work.
-First, note that the case $N = 2$ is easy.
+More or less the same approach works for other $n \neq 5$.
+However, the case of 2-torsion points is special (but nevertheless quite easy).
+The following is IMO the nicest form for curves with a nontrivial 2-torsion point, even though there are still 2 parameters (and not just one).
 \begin{prop}[3(ii) - $2$-torsion points]
@@
     Assume $E: y^2 = x^3 + a_2 x^2 + a_4 x$ is an Elliptic Curve.
-    Then clearly $(0, 0) \in E(\Q)$ and $(0, 0) = -(0, 0)$, so $(0, 0)$ is nontrival 2-torsion point.
+    Then clearly $(0, 0) \in E(\Q)$ and $(0, 0) = -(0, 0)$, so $(0, 0)$ is nontrivial 2-torsion point.
     Hence, there is a nontrivial 2-torsion point in $E'(\Q)$ for all Elliptic Curves $E'$ that are isomorphic (over $\Q$) to $E$.
@@
     as this holds for every Elliptic Curve.
-    Now let $(\alpha, \beta) \in E'(\Q)$ be a nontrival 2-torsion point.
+    Now let $(\alpha, \beta) \in E'(\Q)$ be a nontrivial 2-torsion point.
     Thus $-(\alpha, \beta) = (\alpha, \beta)$, so $\beta = 0$ and $\alpha^3 + a_2 \alpha^2 + a_4 \alpha + a_6 = 0$.
@@
 \end{proof}
-\begin{example}[3(ii) - Additional Examples]
+It looks like we could continue in a similar way for e.g. 6-or 7-torsion points, but the algebra becomes more and more convoluted. 
+\begin{example}[3(ii) - first example]
     Consider the Elliptic Curve
@@
     defined over $\Q$.
-    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve (If $3x^2 + y = 2y + 1 + x = 0$ then $y^2 - y - 1 = 0$, so $y = -1$ and $x = 1$.
+    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve (If $3x^2 - y = 2y + 1 + x \equiv 0$ then $y \equiv 0$ and $x \equiv -1$, but $(-1, 0) \notin \tilde{E}(\F_3)$).
+    Trying all values in $\F_3^2$, we find
+    \begin{equation*}
+        \tilde{E}(\F_3) = \{ (0, 0), (0, 2), \O \} 
+    \end{equation*}
+    Clearly $E(\Q)$ has the 3-torsion point $(0, 0)$, and since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_3)$ we see that
+    \begin{equation*}
+        E_{\mathrm{tors}}(\Q) = \{ (0, 0), (0, -1), \O \}
+    \end{equation*}
+\end{example}
+\begin{example}[3(ii) - second example]
+    Consider the Elliptic Curve
+    \begin{equation*}
+        E: y^2 + x y + 2 y = x^3 + 2 x^2
+    \end{equation*}
+    defined over $\Q$.
+    Note that the reduction $\tilde{E}$ modulo $5$ is still an Elliptic Curve (If $3x^2 + y = 2y + 1 + x = 0$ then $y^2 - y - 1 = 0$, so $y = -1$ and $x = 1$.
 However $(1, -1) \notin \tilde{E}(\F_3)$).
@@
 Further requiring those points to be non-integral increases our chance, as that way, they cannot be torsion points.
-However, playing around with this method did not yield a nice curve where we can compute the rank.
+However, playing around with this method did not yield a nice curve for which we can easily compute the rank.
 So lets fall back to brute force, which works quite well here as this condition is very easy to test via a computer.

### 2022-03-29 Elliptic Curves/4ii_computations.py

@@ -17,7 +17,7 @@ def can_prove_has_sol(r, a, b):
     return False
 
 def can_prove_has_no_sol(r, a, b):
-    for q in [90, 82, 110]:
+    for q in [64, 81, 25, 49]:
         squares = { x**2 % q for x in range(q) }
         sol_count_mod_q =  len([(l, m) 
             for l in range(q) 
@@ -54,10 +54,8 @@ def is_curve_nice(a, b):
             return False
     return True
 
-exit()
-
 for a in range(100):
     for b in range(100):
         if a**2 - 4 * b != 0 and len(sqrfree_factors(b)) >= 14:
             if is_curve_nice(a, b):
-                print(a, b, len(squarefree_factors(b)))
+                print(a, b, len(sqrfree_factors(b)))

### 2022-03-30 Schemes/submission.tex
Proofread schemes

@@
     So assume $\D{f} \subseteq \bigcup_i \D{f_i}$.
-    If no $f^n$ is in $\a := \langle f_i \ | \ i \rangle$, then $f$ is not nilpotent in $S/\a$ and so $S/\a$ is not the zero ring.
+    If no $f^n$ is in $\a := \langle f_i \ | \ i \rangle$, then $f$ is not nilpotent in $S/\a$ and so $(S/\a)_f$ is not the zero ring.
     Hence, $(S/\a)_f$ has a prime ideal, and its preimage under $S \to S/\a \to (S/\a)_f$ yields a prime ideal $\p'$ containing $\a$ and not containing $f$.
@@
     \end{equation*}
-
+    We show that the $s_i$ glue to a unique $s \in \mathcal{F}(\D{f})$.
     To show uniqueness, assume there are $\alpha/f^N, \beta/f^N \in \D{f}$ with
@@
     \begin{equation*}
-        s_i = s := \frac {\sum_l r_l a_l} {fn} \in S_f
+        s_i = s := \frac {\sum_l r_l a_l} {f^n} \in S_f
     \end{equation*}
@@
 \end{proof}
-Now we the B-sheaf extension theorem from the lecture (from Section 1.11) yields the following corollary.
+Now the B-sheaf extension theorem from the lecture (from Section 1.11) yields the following corollary.
 \begin{corollary}
@@
 
-    Now assume there is any ideal $\a$ such that $\a \setminus \m \neq \emptyset$, i.e. there is $f/g \in \a \setminus \m$.
-    Then $f \in T$ as $f$ homogeneous and $f \notin \p$.
+    Now consider an ideal $\a$ such that $\a \setminus \m \neq \emptyset$, i.e. there is $f/g \in \a \setminus \m$.
+    Then $f \in T$ as $f$ homogeneous (since $f/g \in (T^{-1}S)_0$ is homogeneous of degree 0) and $f \notin \p$.
     Thus $g/f \in (T^{-1}S)_0$ and so $f/g \in (T^{-1}S)_0^*$, which implies $\a = \langle 1 \rangle$.
@@
     \end{equation*}
-    which is also continuous, as the preimage of some basic open set $\D{fg}$ is $D_{g^n/f^m}$ where $n\deg(g) = m\deg(f)$.
-    Note that $\phi \circ \phi' = \mathrm{id}_{\Spec(R)}$ because $\p \subseteq (\p S_f \cap S) S_f \cap R$ and
+    which is also continuous, as the preimage of some basic open set $\D{fg}$ is $D_{g^n/f^m}$ where $n\deg(g) = m\deg(f), (n, m) \neq (0, 0)$.
+    Note that $\phi \circ \phi' = \mathrm{id}_{\Spec(R)}$ because for $\p \leq R$ have $\p \subseteq (\p S_f \cap S) S_f \cap R$ and
     \begin{equation*}
@@
     \begin{equation*}
-        \eta_{\D{g/f^n}}: R_{g/f^n} \to (S_{f g})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
+        \eta_{D_{g/f^n}}: R_{g/f^n} \to (S_{f g})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
     \end{equation*}
@@
 \end{corollary}
+
+\section{Projective space}
+For this section, let $R$ be a ring and assume $S$ is a graded $R$-algebra, i.e. $S$ is a graded ring with $R \subseteq S_0$.
 \begin{definition}
-    For any ring $R$ and $n \in \N$, define the \emph{projective $n$-space} as\footnote{Endow $R[x_0, ..., x_n]$ with the standard natural grading, i.e.
-$\deg(x_i) = 1$.
-Note that this makes $R[x_0, ..., x_n]_0 = R$, so all $r \in R$ are homogeneous of degree $0$.}
-    \begin{equation*}
-        \P_R^n := \Proj(R[x_0, ..., x_n])
-    \end{equation*}
-    which naturally becomes a scheme over $\Spec(R)$ via the morphism given by
+    The scheme $\Proj(S)$ naturally becomes a scheme over $\Spec(R)$ via
     \begin{align*}
-        &f: \Proj(R[x_0, ..., x_n]) \to \Spec(R), \quad \p \mapsto \p \cap R \\
-        &f^\#_{D_f}: R_f \to \O_{\Proj(R[x_0, ..., x_n])}(\D{f}) = R_f[x_0, ..., x_n], \quad r \mapsto r
+        &f: \Proj(S) \to \Spec(R), \quad \p \mapsto \p \cap R \\
+        &f^\#_{D_f}: R_f \to \O_{\Proj(S)}(\D{f}) = (S_f)_0, \quad r \mapsto r
     \end{align*}
+    This is well-defined, as $R \subseteq S_0$ implies $R_f \subseteq (S_0)_f = (S_f)_0$ since $\deg(f) = 0$.
 \end{definition}
-
-\section{Projective space as a variety}
-For this section, let $R$ be a ring and $n \in \N$.
 \begin{prop}
     \label{prop:projective_space_separated}
-    The morphism $\P_R^n \to \Spec(R)$ is separated.
+    The morphism $\Proj(S) \to \Spec(R)$ is separated.
 \end{prop}
@@
     This is the same proof as for \citestacks{01MC}.
-    By Lemma~\ref{prop:Df_affine} we find a cover $\Proj(S) = \bigcup_i \D{x_i}$ of affine opens.
-    We use the characterization from the lecture and show that $\D{x_i} \cap \D{x_j}$ is an affine open and the canonical multiplication map
+    By Lemma~\ref{prop:Df_affine} we find a cover $\Proj(S) = \bigcup_i \D{f_i}$ of affine opens.
+    We use the characterization from the lecture and show that $\D{f_i} \cap \D{f_j}$ is an affine open and the canonical multiplication map
     \begin{equation*}
-        \O_{\P_R^n}(\D{x_i}) \times \O_{\P_R^n}(\D{x_j}) \to \O_{\P_R^n}(\D{x_i} \cap \D{x_j})
+        \O_{\Proj(S)}(\D{f_i}) \times \O_{\Proj(S)}(\D{f_j}) \to \O_{\Proj(S)}(\D{f_i} \cap \D{f_j})
     \end{equation*}
@@
 
-    First note that $\D{x_i} \cap \D{x_j} = \D{x_ix_j}$ which is affine open by Lemma~\ref{prop:Df_affine}.
-    By definition, we have $\O_{\P_R^n}(\D{f}) = (R[x_0, ..., x_n]_f)_0$ and so we have to show that
+    First note that $\D{f_i} \cap \D{f_j} = \D{f_if_j}$ which is affine open by Lemma~\ref{prop:Df_affine}.
+    By definition, we have $\O_{\Proj(S)}(\D{f}) = (S)_0$ and so we have to show that
     \begin{equation*}
-        (R[x_0, ..., x_n]_{x_i})_0 \times (R[x_0, ..., x_n]_{x_j})_0 \to (R[x_0, ..., x_n]_{x_ix_j})_0, \quad (a, b) \mapsto ab
+        (S_{f_i})_0 \times (S_{f_j})_0 \to (S_{f_if_j})_0, \quad (a, b) \mapsto ab
     \end{equation*}
@@
 
-    However, for $f/(x_ix_j)^n \in (R[x_0, ..., x_n]_{x_ix_j})_0$ we have that
+    For $g/(f_if_j)^n \in (S_{f_if_j})_0$ we now have that
     \begin{equation*}
-        \frac f {x_i^{2n}} \cdot \frac {x_i^n} {x_j^n} = \frac f {(x_ix_j)^n}
+        \frac {gf_j^r} {f_i^{n + t}} \cdot \frac {f_i^t} {f_j^{n + r}} = \frac g {(f_if_j)^n}
     \end{equation*}
-    and clearly $f/x_i^{2n} \in (R[x_0, ..., x_n]_{x_i})_0$ as $\deg(f) = \deg(x_i) n + \deg(x_j) n = 2n$ and $x_i^n/x_j^n \in (R[x_0, ..., x_n]_{x_j})_0$.
-    The claim follows.
+    where $r, t \in \N$ such that\footnote{This exists, since $\gcd(\deg(f_i), \deg(f_j)) \ \mid \ \deg(f_j) \ | \ \deg(f_j)n$.} $\deg(f_j) n = \deg(f_i) t - \deg(f_j) r$.
+
+    Since $\deg(g) = (\deg(f_i) + \deg(f_j)) n$ it follows that $\deg(g) + \deg(f_j)r = \deg(f_i) (n + t)$ and so both $gf_j^r/g_i^{n + t}$ and $f_i^t/f_j^{n + r}$ have degree 0.
+    Hence they are elements of $(S_{f_i})_0$ resp. $(S_{f_j})_0$ and the claim follows.
 \end{proof}
-To study integrality, it is useful to have the next small lemma on the nilradical.
+Now we want to define projective space, which is the object we study during the rest of this project.
+From now on, let $n \in \N$ and equip $R[x_0, ..., x_n]$ with the standard grading.
+\begin{definition}
+    \emph{Projective $n$-space} is the scheme $\P_R^n := \Proj(R[x_0, ..., x_n])$ over $\Spec(R)$.
+\end{definition}
 \begin{lemma}
@@
     \end{equation*}
-    Now note that $\Nil(R[x_0, ..., x_n]) \subseteq \a$ for all prime ideals $\a$, and the claim follows since $\Nil(R)$ is prime by assumption that $\Spec(R)$ is irreducible.
+    Now note that $\Nil(R[x_0, ..., x_n]) \subseteq \a$ for all prime ideals $\a$, and the claim follows since $\Nil(R)$ and thus $\Nil(R)R[x_0, ..., x_n]$ is prime by assumption that $\Spec(R)$ is irreducible.
 \end{proof}
@@
     Since the $V_i$ cover $Y$, there is $i$ such that $x \in V_i$.
-    As $\pi = \restr{\pi}{f^{-1}(V_i)}$ is closed, we see that
+    As $\pi_i = \restr{\pi}{f^{-1}(V_i)}$ is closed, we see that
     \begin{equation*}
-        \pi(C) \cap V_i = \pi_i(C) \quad \text{is closed in $V_i$}
+        \pi(C) \cap V_i = \pi_i(C \cap \pi^{-1}(V_i)) \quad \text{is closed in $V_i$}
     \end{equation*}
@@
     for all homogeneous $f \in R[x_0, ..., x_n]$.
-    By Lemma~\ref{prop:Df_affine}, we see that $\D{f}$ for $f \in S[x_0, ..., x_n]$ homogeneous form an affine open cover of $\P_S^n$.
-    Furthermore, we have a cover by affine opens $\D{f} \times_{\Spec(R)} \Spec(S)$ of $\P_R^n \times_{\Spec(R)} \Spec(S)$ for $f \in R[x_0, ..., x_n]$ homogeneous.
-    Together, we see that it suffices to show that the isomorphisms (induced by $\iota_f$)
+    By Lemma~\ref{prop:Df_affine}, we see that the basic open sets $\D{x_i}$ form an affine open cover of $\P_S^n$.
+    Furthermore, we have a cover by affine opens $\D{x_i} \times_{\Spec(R)} \Spec(S)$ of $\P_R^n \times_{\Spec(R)} \Spec(S)$.
+    Note that $\alpha(x_i) = x_i$.
+    Together, we see that it suffices to show that the isomorphisms (induced by $\iota_{x_i}$)
     \begin{equation*}
-        \phi_f: \D{\alpha(f)} = \Spec((S[x_0, ..., x_n]_{\alpha(f)})_0) \to \D{f} \times_{\Spec(R)} \Spec(S)
+        \phi_i: \D{x_i} = \Spec(S[x_0, ..., x_n]_{x_i})_0 \to \D{x_i} \times_{\Spec(R)} \Spec(S)
     \end{equation*}
     glue to an isomorphism $\Proj(S[x_0, ..., x_n]) \to \P_R^n \times_{\Spec(R)} \Spec(S)$.
-    By the gluing lemma, it suffices that the compatibility conditions are satisfied, i.e. that for all $f, g \in R[x_0, ..., x_n]$ homogeneous the diagram
+    By the gluing lemma, it suffices that the compatibility conditions are satisfied, i.e. for all $i, j$ the diagram
     \begin{center}
         \begin{tikzpicture}
-            \node (Sfg) at (1, 0) {$\D{\alpha(f)} \cap \D{\alpha(g)} = \D{\alpha(fg)}$};
-            \node (Sf) at (3, 1.5) {$\D{\alpha(f)}$};
-            \node (Sg) at (3, -1.5) {$\D{\alpha(g)}$};
-            \node (f) at (7, 1.5) {$\D{f} \times_{\Spec(R)} \Spec(S)$};
-            \node (g) at (7, -1.5) {$\D{g} \times_{\Spec(R)} \Spec(S)$};
+            \node (Sfg) at (1, 0) {$\D{x_i} \cap \D{x_j} = \D{x_ix_j}$};
+            \node (Sf) at (2, 1.5) {$\D{x_i}$};
+            \node (Sg) at (2, -1.5) {$\D{x_j}$};
+            \node (f) at (7, 1.5) {$\D{x_i} \times_{\Spec(R)} \Spec(S)$};
+            \node (g) at (7, -1.5) {$\D{x_j} \times_{\Spec(R)} \Spec(S)$};
             \node (all) at (9, 0) {$\P_R^n \times_{\Spec(R)} \Spec(S)$};
@@
             \draw [->] (Sfg) -- (Sg);
-            \draw [->] (Sf) -- (f) node [midway, above] {$\phi_f$};
-            \draw [->] (Sg) -- (g) node [midway, above] {$\phi_g$};
+            \draw [->] (Sf) -- (f) node [midway, above] {$\phi_i$};
+            \draw [->] (Sg) -- (g) node [midway, above] {$\phi_j$};
             \draw [->] (f) -- (all);
@@
 
-    For a prime ideal $\p \in \D{\alpha(fg)}$ have that
+    For a prime ideal $\p \in \D{x_ix_j}$ have that
     \begin{equation*}
-        \phi_f(\p) = \iota_f^{-1}(\p \cap (S[x_0, ..., x_n]_f)_0) \in \D{f} \times_{\Spec(R)} \Spec(S)
+        \phi_i(\p) = \iota_{x_i}^{-1}\bigl( \p \cap (S[x_0, ..., x_n]_{x_i})_0 \bigr) \in \D{x_i} \times_{\Spec(R)} \Spec(S)
     \end{equation*}
-    and so $g \notin \phi_f(\p)$, i.e. $\phi_f(\p) \in \D{fg} \times_{\Spec(R)} \Spec(S)$.
-    Hence, we have that both restrictions
+    and so $x_j \notin \phi_i(\p)$, i.e. $\phi_i(\p) \in \D{x_ix_j} \times_{\Spec(R)} \Spec(S)$.
+    Hence, both restrictions
     \begin{equation*}
-        \restr{\phi_f}{\D{\alpha(fg)}}, \ \restr{\phi_g}{\D{\alpha(fg)}}: \D{\alpha(fg)} \to \D{fg} \times_{\Spec(R)} \Spec(S)
+        \restr{\phi_i}{\D{x_ix_j}}, \ \restr{\phi_j}{\D{x_ix_j}}: \D{x_ix_j} \to \D{x_ix_j} \times_{\Spec(R)} \Spec(S)
     \end{equation*}
-    map into $\D{fg} \times_{\Spec(R)} \Spec(S)$.
+    map into $\D{x_ix_j} \times_{\Spec(R)} \Spec(S)$.
     Now note that the diagram
@@
         \begin{tikzpicture}
-            \node (Rf) at (-3, 0) {$S \otimes_R (R[x_0, ..., x_n]_f)_0$};
-            \node (Rg) at (0, -1.5) {$S \otimes_R (R[x_0, ..., x_n]_g)_0$};
-            \node (Rfg) at (-3, -3) {$S \otimes_R (R[x_0, ..., x_n]_{fg})_0$};
+            \node (Rf) at (-3, 0) {$S \otimes_R (R[x_0, ..., x_n]_{x_i})_0$};
+            \node (Rg) at (0.5, -1.5) {$S \otimes_R (R[x_0, ..., x_n]_{x_j})_0$};
+            \node (Rfg) at (-3, -3) {$S \otimes_R (R[x_0, ..., x_n]_{x_ix_j})_0$};
 
-            \node (Sf) at (8, 0) {$(S[x_0, ..., x_n]_f)_0$};
-            \node (Sg) at (5, -1.5) {$(S[x_0, ..., x_n]_g)_0$};
-            \node (Sfg) at (8, -3) {$(S[x_0, ..., x_n]_{fg})_0$};
+            \node (Sf) at (8.5, 0) {$(S[x_0, ..., x_n]_{x_i})_0$};
+            \node (Sg) at (5, -1.5) {$(S[x_0, ..., x_n]_{x_j})_0$};
+            \node (Sfg) at (8.5, -3) {$(S[x_0, ..., x_n]_{x_ix_j})_0$};
 
-            \draw [->] (Rf) -- (Sf) node [midway, above] {$\iota_f$};
-            \draw [->] (Rg) -- (Sg) node [midway, above] {$\iota_g$};
-            \draw [->] (Rfg) -- (Sfg) node [midway, above] {$\iota_{fg}$};
+            \draw [->] (Rf) -- (Sf) node [midway, above] {$\iota_{x_i}$};
+            \draw [->] (Rg) -- (Sg) node [midway, above] {$\iota_{x_j}$};
+            \draw [->] (Rfg) -- (Sfg) node [midway, above] {$\iota_{x_ix_j}$};
 
@@
     \end{center}
-    commutes, and so the restrictions of $\phi_f$ resp. $\phi_g$ to $\D{\alpha(fg)}$ are both induced by the homomorphism $\iota_{fg}$, hence they are equal.
+    commutes, and so the restrictions of $\phi_i$ resp. $\phi_j$ to $\D{x_ix_j}$ are both induced by the homomorphism $\iota_{x_ix_j}$, hence they are equal.
     The claim follows.
 \end{proof}
-Before we come to the proof now, there is one last notion to present.
+This lemma also justifies the usual definition of projective $n$-space over a scheme $B$ as
+\begin{equation*}
+    \P_B^n := B \times_{\Spec(\Z)} \P_\Z^n
+\end{equation*}
+
+Before we come to the proof of properness now, there is one last notion to present.
 \begin{definition}
@@
     Let $f: X \to Y$ be a quasi-compact morphism.
-    Then $f(|X|)$ is closed if and only if it is stable under specialization.
+    Then $f(X)$ is closed if and only if it is stable under specialization.
 \end{lemma}
@@
     The implication $\Leftarrow$ is clear.
-    It suffices to show that $f(|X|) \cap V \subseteq V$ is closed for all affine opens $V \subseteq Y$.
+    It suffices to show that $f(X) \cap V \subseteq V$ is closed for all affine opens $V \subseteq Y$.
 
     Note that the preimage $f^{-1}(V)$ is quasi-compact, hence has a finite cover of affine opens $U_i \subseteq X$.
-    Now let $V_i = \overline{f(|U_i|)}$ be the closed subscheme of $V$ with the canonical (reduced) scheme structure\footnote{As in the Lecture Notes, Section 5.6.}.
+    Now let $V_i = \overline{f(U_i)}$ be the closed subscheme of $V$ with the canonical (reduced) scheme structure\footnote{As in the Lecture Notes, Section 5.6.}.
     Since $V$ is affine, also $V_i$ is affine.
-    Note that now it suffices to show that $f(|U_i|) \subseteq V_i$ is closed.
+    Note that now it suffices to show that $f(U_i) \subseteq V_i$ is closed.
 
@@
     is a morphism between affine schemes with dense image.
-    We want to show that $f'(|U_i|)$ is already $V_i$.
+    We want to show that $f'(U_i)$ is already $V_i$, i.e. $V_i \subseteq f(U_i)$.
 
@@
     Note that $\p$ is a specialization of $\p'$.
-    Hence, it suffices to show that $\p' \in f'(|U_i|)$.
+    Hence, it suffices to show that $\p' \in f'(U_i)$.
     Note that $B_{\p'}$ must be a field, otherwise we could take a proper nonzero prime ideal of $B_{\p'}$ and its preimage under $B \to B_{\p'}$ would be a smaller prime ideal in $B$.
@@
     Since $\q \cap B_{\p'} = \{ 0 \}$ (here we use that $B_{\p'}$ is a field), find $\q' \cap B = \p'$, thus $\q'$ maps to $\p'$ under $\Spec(A) \to \Spec(B)$.
-    This shows $\p' \in f'(|U_i|)$ and the claim follows.
+    This shows $\p' \in f'(U_i)$ and the claim follows.
 \end{proof}
@@
     By assumption, all\footnote{Since a monomial of degree $(n + 1)m$ in $n + 1$ variables is divisible by $x_i^m$ for at least one $i$, by the pigeonhole principle.} $\alpha w_i \in \b$.
-    Since $\p$ is homogeneous, observe that now there are $r_{ij} \in \q$ such that
+    Since $\p$ is homogeneous, observe that by definition of $\b$, there are $r_{ij} \in \q$ such that
     \begin{equation*}
@@
     Now we continue in $S$, replacing $w$ and $A/\alpha$ by their images under $R \to S$.
-    So $w \in S^n$ and $A/\alpha \in \mathfrak{l}^{n \times n}$.
+    So $w \in S^N$ and $A/\alpha \in \mathfrak{l}^{N \times N}$.
     Note that we still have $(A/\alpha) w = w$.
@@
 
-    Now equip $S_{\mathfrak{l}}$ with the $\mathfrak{l}$-adic topology.
+    Now equip $S$ with the $\mathfrak{l}$-adic topology.
     Note that $S$ is Noetherian and local, thus the Krull intersection theorem \cite[8.41]{comalg_notes} shows that the $\mathfrak{l}$-adic topology is Hausdorff and we find
@@
     Denote $\P_R^n \to \Spec(R)$ by $\phi$.
-    Consider a closed set $\V{\a} = \P_R^n \setminus \D{\a}$ given by a homogeneous ideal $\a \leq R[x_0, ..., x_n]$.
+    Consider a closed set $\V{\a} := \P_R^n \setminus \D{\a}$ given by a homogeneous ideal $\a \leq R[x_0, ..., x_n]$.
     By Lemma~\ref{prop:im_closed_iff_stable_specialization}, it suffices to show that $\phi(\V{\a})$ is closed under specialization (note that $\P_R^n \to \Spec(R)$ is quasi-compact, e.g.
@@
     As $R$ is a valuation ring, we find $k$ such that $g_{k0}$ is the smallest element (w.r.t. divisibility by $R$) among $g_{00}, ..., g_{n0}$.
-    So we see that $g_{ik} = g_{i0} / g_{k0} \in R$ for all $i$.
+    So we see that $g_{jk} = g_{j0} / g_{k0} \in R$ for all $i$.
     In particular, we find a ring homomorphism
@@
     \begin{equation*}
-        \Spec(R) \to \Spec(\Z\Bigl[ \frac {x_0} {x_k}, ..., \frac {x_n} {x_k} \Bigr]) = \D{x_j} \subseteq X
+        \Spec(R) \to \Spec(\Z\Bigl[ \frac {x_0} {x_k}, ..., \frac {x_n} {x_k} \Bigr]) = \D{x_k} \subseteq X
     \end{equation*}

### 2022-03-30 Elliptic Curves/submission.tex
Fixed an example for Elliptic Curves

@@
     defined over $\Q$.
-    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve (If $3x^2 - y = 2y + 1 + x \equiv 0$ then $y \equiv 0$ and $x \equiv -1$, but $(-1, 0) \notin \tilde{E}(\F_3)$).
+    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve 
+    (if $3x^2 - y \equiv 2y + 1 + x \equiv 0$ then $y \equiv 0$ and $x \equiv -1$, but $(-1, 0) \notin \tilde{E}(\F_3)$).
     Trying all values in $\F_3^2$, we find
@@
     defined over $\Q$.
-    Note that the reduction $\tilde{E}$ modulo $5$ is still an Elliptic Curve (If $3x^2 + y = 2y + 1 + x = 0$ then $y^2 - y - 1 = 0$, so $y = -1$ and $x = 1$.
-However $(1, -1) \notin \tilde{E}(\F_3)$).
+    Note that the reduction $\tilde{E}$ modulo $3$ is still an Elliptic Curve
+    (if $3x^2 + 4x - y \equiv 2y + x + 2 \equiv 0$ then $x - y \equiv x - y - 1 \equiv 0$, a contradiction).
     Trying all values in $\F_3^2$, we find
     \begin{equation*}
-        \tilde{E}(\F_3) = \{ (0, 0), (0, 2), \O \} 
-    \end{equation*}
-    Clearly $E(\Q)$ has the 3-torsion point $(0, 0)$, and since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_3)$ we see that
-    \begin{equation*}
-        E_{\mathrm{tors}}(\Q) = \{ (0, 0), (0, -1), \O \}
+        \tilde{E}(\F_3) = \{ (0, 0), (0, 1), (1, 0), \O \} 
+    \end{equation*}
+    Now note that $E(\Q)$ has the 4-torsion point $(0, 0)$ and since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_5)$ we already see that
+    \begin{equation*}
+        E_{\mathrm{tors}}(\Q) = \{ (0, 0), (-2, 0), (0, -2), \O \}
     \end{equation*}

### 2022-03-30 Elliptic Curves/submission.tex
Added trivial example for 4(ii)

@@
 \end{proof}
+First of all, note that it is trivial to find an example where $b$ has at least 3 different prime factors and the rank of $E$ is easy to compute.
+\begin{example}[4(ii) - trivial example]
+    Consider the Elliptic Curve $E: y^2 = x(x^2 + 6 \cdot 30^2 x + 30^4)$.
+    Clearly $30^4 = 2^4 \cdot 3^4 \cdot 5^4$ has at least three different prime factors.
+    To compute the rank of $E$, note that $E$ is isomorphic to $E': y^2 = x(x^2 + 6x + 1)$ (over $\Q$), and so $\mathrm{rank}(E) = \mathrm{rank}(E')$.
+    By Example~\ref{ex:4i}, we thus see that $E$ has rank 0.
+\end{example}
 To find an example with rank two, it seems like a good way to take a curve with many rational points.
@@
 So lets fall back to brute force, which works quite well here as this condition is very easy to test via a computer.
-\begin{example}[4(ii)]
+\begin{example}[4(ii) - main example]
     \label{ex:special_curve}
@@
     \end{equation*}
-    Clearly $30 = 2 \cdot 3 \cdot 5$ has at least 3 different prime factors.
+    Note that $30 = 2 \cdot 3 \cdot 5$ has at least 3 different prime factors.
     We want to compute the rank of $E$.
@@
     \end{equation*}
-    and thus $\Z/2\Z \hookrightarrow E_{\mathrm{tors}}(\Q)/[2]E(\Z)$ (there is the nontrivial 2-torsion point $(0, 0)$)
+    and $\Z/2\Z \hookrightarrow E_{\mathrm{tors}}(\Q)/[2]E(\Z)$ (there is the nontrivial 2-torsion point $(0, 0)$)
     This yields

### 2022-03-31 Elliptic Curves/submission.tex
Remade example 1.7

@@
 for an Elliptic Curve $E$ defined over $k$ and any ring $R$ contained in the algebraic closure $\bar{k}$.
-Note that this is in general not a group.
+Note that in general this is not a group.
 However, it gives us a way to nicely phrase the next statements.
@@
     \end{equation*}
-    Thus $|f(y)|_p < |f'(y)|_p^2$ and Hensel's Lemma yields a root $\gamma \in \Z_p$ with $(x, \gamma) \in E(\Z_p)$.
+    Thus $|f(y)|_p < |f'(y)|_p^2$ and Hensel's Lemma \cite[Thm 2.14]{lecture} yields a root $\gamma \in \Z_p$ with $(x, \gamma) \in E(\Z_p)$.
 
@@
     \end{equation*}
-    Hensel's Lemma now \cite[Thm 2.14]{lecture} shows that there is $\gamma \in \Z_p$ such that $\gamma^2 = x^3 + a_2 x^2 + a_4 x + a_6$ and so $(x, \gamma) \in E(\Z_p)$.
+    Hensel's Lemma \cite[Thm 2.14]{lecture} now shows that there is $\gamma \in \Z_p$ such that $\gamma^2 = x^3 + a_2 x^2 + a_4 x + a_6$ and so $(x, \gamma) \in E(\Z_p)$.
     Since $|y|_p = 1$ clearly also $|\gamma|_p = 1$.
@@
     with $\alpha, \beta \in \bar{\F}_p$.
-    However, note that $\F_p$ is perfect, so $(x - \alpha)^2(x - \beta)$ cannot be irreducible over $\F_p$, otherwise $\F_p[x] / \langle(x - \alpha)^2(x - \beta)\rangle$ would be a non-separable field extension of $\F_p$.
+    However, note that $\F_p$ is perfect, so $(x - \alpha)^2(x - \beta)$ cannot be irreducible over $\F_p$, otherwise $\F_p[x] / \langle(x - \alpha)^2(x - \beta)\rangle$ would be a non-separable finite field extension of $\F_p$.
     Thus, either $\alpha \in \F_p$ or $\beta \in \F_p$.
-    If $\alpha \in \F_p$, then clearly also $\beta = -2\alpha - \tilde{f}_2 \in \F_p$.
+    If $\alpha \in \F_p$, then clearly also $\beta = 2\alpha - \tilde{f}_2 \in \F_p$.
     If $\beta \in \F_p$, then also $(x - \alpha)^2 \in \F_p[x]$ and again by perfectness of $\F_p$, note that $\alpha \in \F_p$.
@@
 \begin{example}[1(iv) - second example]
-    Assume we want to find a curve $E: y^2 = f(x) := x^3 + a_2 x^2 + a_4 x + a_6$ such that $\tilde{E}(\F_7)$ contains no point $(x, y)$ with $y \neq 0$.
+    Assume we want to find a curve $E: y^2 = f(x) := x^3 + A x + B$ such that $\tilde{E}(\F_7)$ contains no point $(x, y)$ with $y \neq 0$.
     By considering a scaling isomorphism of the form
@@
     \end{equation*}
-    we can assume wlog that $a_2 \equiv 0, 1, 2 \mod 7$ (as each element in $\F_7$ is congruent to $0, 1$ or $2$ modulo the squares $\{ x^2 \ | \ x \in \F_7 \}$).
+    we can assume wlog that $A \equiv 0, 1, 3 \mod 7$ (as the fourth powers in $\F_7^*$ are $1, 4, 2$).
     Furthermore have
     \begin{equation*}
-        f(0) = a_6 \equiv 0, 3, 5, 6, \quad f(1) = 1 + a_2 + a_4 + a_6 \equiv 0, 3, 5, 6
+        f(0) = B \equiv 0, 3, 5, 6, \quad f(1) = 1 + A + B \equiv 0, 3, 5, 6
     \end{equation*}
     since $1, 4, 2$ are the squares in $\F_7^*$.
-    We find 48 possible solutions, and for example $a_2 \equiv 2, a_4 \equiv 6, a_6 \equiv 5$ works.
+    So we have the possibilities
+    \begin{equation*}
+        A \equiv 0, \quad B \equiv 5, 6
+    \end{equation*}
+    and
+    \begin{equation*}
+        A \equiv 1, \quad B \equiv 3, 5
+    \end{equation*}
+    and
+    \begin{equation*}
+        A \equiv 3, \quad B \equiv 3, 6
+    \end{equation*}
+    Trying all of them, we find that the only solution such that there is no $(x, y) \in \tilde{E}(\F_7)$ with $y \neq 0$ is $A \equiv 0, B \equiv 6$.
     Indeed, have that
     \begin{equation*}
-        \tilde{E}(\F_7) = \{ (1, 0), (5, 0), (6, 0), \O \}
+        \tilde{E}(\F_7) = \{ (1, 0), (2, 0), (4, 0), \O \}
     \end{equation*}
@@
     \begin{align*}
-        1^2 &\equiv 2^3 + 2 \cdot 2^2 + 6 \cdot 2 + 5 = 33 \mod 8 \\
-        1^2 &\equiv 2^3 + 2 \cdot 2^2 + 6 \cdot 2 + 5 = 33 \mod 3 \\
-        2^2 &\equiv 1^3 + 2 \cdot 1^2 + 6 \cdot 1 + 5 = 14 \mod 5
+        2^2 &\equiv 3^3 + 6 = 28 \mod 8 \\
+        1^2 &\equiv 1^3 + 6 = 7 \mod 3 \\
+        2^2 &\equiv 2^3 + 6 = 14 \mod 5
     \end{align*}
-    so Hensel's Lemma yields \cite[Thm 1.15]{lecture} points $(x, y) \in E(\Z_2)$ with $|y|_2 = 1$ and $(x', y') \in E(\Z_3)$ with $|y'|_3 = 1$ and $(x'', y'') \in E(\Z_5)$ with $|y''|_5 = 1$.
+    so Hensel's Lemma \cite[Thm 1.15]{lecture} yields points $(x, y) \in E(\Z_2)$ with $|y|_2 = 1$ and $(x', y') \in E(\Z_3)$ with $|y'|_3 = 1$ and $(x'', y'') \in E(\Z_5)$ with $|y''|_5 = 1$.
 \end{example}

### 2022-03-31 Elliptic Curves/submission.tex
Finalized Elliptic Curves

@@
     \begin{align*}
-        2^2 &\equiv 3^3 + 6 = 28 \mod 8 \\
+        1^2 &\equiv 3^3 + 6 = 33 \mod 8 \\
         1^2 &\equiv 1^3 + 6 = 7 \mod 3 \\
@@
     Consider the Elliptic Curve $E: y^2 = x(x + 1)(x - 8)$.
-    Note that we have an isomorphism
-    \begin{equation*}
-        \psi: E \to E', \quad (x, y) \mapsto \left( x - \frac 7 3, y \right)
-    \end{equation*}
-    to the Elliptic Curve $E': y^2 = x^3 - \frac {73} 3 x - \frac {1190} {27}$ defined over $\Q$.
     Have that
     \begin{equation*}
-        \Delta(E) = -72^2 = -5184 = \Delta(E')
+        \Delta(E) = -(-1 - 0)^2(8 - 0)^2(8 - (-1))^2 = -72^2 = -5184
     \end{equation*}
     Note that this has only the prime factors $2$ and $3$.
-    As before, this shows that all the results from the lecture on the reduction modulo $p \neq 2, 3$ are also valid for the curve $E$, even though it is not defined by an equation of the form $y^2 = x^3 + Ax + B$.
-    We see that
+    So the reduction $\tilde{E}$ modulo 7 is an Elliptic Curve with
     \begin{equation*}
@@
     \end{equation*}
-    and thus has order 8.
-    As before, we this only leaves two possible cases, either the obvious 2-torsion points are all torsion points (i.e.
-$\#E_{\mathrm{tors}}(\Q) = 4$) or each of the points $\tilde{E}(\F_5)$ lifts to a torsion point (i.e.
+    Since $E_{\mathrm{tors}}(\Q) \hookrightarrow \tilde{E}(\F_7)$, this leaves only two cases.
+    Either the obvious 2-torsion points are all torsion points (i.e.
+$\#E_{\mathrm{tors}}(\Q) = 4$) or each of the points $\tilde{E}(\F_7)$ lifts to a torsion point (i.e.
 $\#E_{\mathrm{tors}}(\Q) = 8$).
@@
     Unlike the previous example however, this time the former is the case.
-    To see this, we use the Nagell-Lutz theorem \cite[5.4]{lecture}.
+    To see this, we use the Nagell-Lutz theorem \cite[Thm 5.4]{lecture}.
     Assume $(x, y) \in E_{\mathrm{tors}}(\Q)$ with $y \neq 0$.
@@
     \end{equation*}
-
+    First consider the direction $\Leftarrow$.
     \paragraph{Case 1} By assumption, there is $\gamma, \mu \in k$ with $\gamma^2 = \alpha\beta$ and $\mu^2 = 2\gamma + \alpha + \beta$.
@@
     Let $p$ be a prime.
-    Taking the set of ``exhaustive cases'' given by $p(-1) = -p$ similar to the proof of Proposition~\ref{prop:subgroup_mod_every_p}.
+    We can find an example by taking the set of ``exhaustive cases'' given by $p(-1) = -p$, similar to the proof of Proposition~\ref{prop:subgroup_mod_every_p}.
     In other words, take $\alpha, \beta \in \Z$ such that $-\alpha, -p\beta$ and $\beta - \alpha$ are squares (in $\Z$).
@@
     Furthermore, the third point of intersection of the tangent and $E$ is $(-a_2, 0)$.
-    The line through $\O$ and $(-a_2)$ is given by $x = -a_2$ and its third point of intersection with $E$ is then $(-a_2, a_1a_2 - a_3)$. 
+    The line through $\O$ and $(-a_2, 0)$ is given by $x = -a_2$ and its third point of intersection with $E$ is then $(-a_2, a_1a_2 - a_3)$. 
 \end{proof}
@@
     So $E$ meets $E'$ in at least 10 points (counting multiplicity), which is greater than the product of their degrees $9 = 3 \cdot 3$.
-    By Bezout's theorem \cite[Corollary I.7.8]{hartshorne}, it follows that $E$ and $E'$ share an irreducible component of dimension $\geq 1$, but since both are Elliptic Curves, they are irreducible of dimension $1$ and so $E = E'$.
+    By Bezout's theorem \cite[Corollary I.7.8]{hartshorne}, it follows that $E$ and $E'$ share an irreducible component of dimension $\geq 1$, but since both are Elliptic Curves, they are irreducible of dimension $1$, so we find $E = E'$.
 \end{proof}
@@
 \begin{itemize}
-    \item Apply a translation to get an isomorphic curve whose (nontrivial) 3-torsion point is $(0, 0)$ and the tangent is given by $y = 0$.
+    \item Apply Corollary~\ref{prop:point_normalization} to get an isomorphic curve whose (nontrivial) 3-torsion point is $(0, 0)$ and the tangent is given by $y = 0$.
     \item Observe that $(0, 0)$ being a 3-torsion point is equivalent to the fact that the tangent at $E$ through $(0, 0)$ meets $E$ at $(0, 0)$ with multiplicity three.
@@
 However, playing around with this method did not yield a nice curve for which we can easily compute the rank.
-So lets fall back to brute force, which works quite well here as this condition is very easy to test via a computer.
+In other words, we want to find curves $E: y^2 = x(x^2 + ax + b)$ such that the equations
+\begin{equation*}
+    r l^4 + a l^2 m^2 + \frac b r m^4 = n^2 \quad \text{and} \quad r l^4 + a_1 l^2 m^2 + \frac {b_1} r m^4 = n^2
+\end{equation*}
+obviously have or have no solution.
+This condition is quite easy to check with a computer, so let's just use a brute-force approach to find nice curves.
 \begin{example}[4(ii) - main example]
@@
     \begin{itemize}
-        \item If $a \leq 0, b \geq 0$, then $\mathrm{rank}(E) \leq 2k - 1$
+        \item If $a \leq 0 \leq b$, then $\mathrm{rank}(E) \leq 2k - 1$
         \item If $a \perp b$ are coprime, then $\mathrm{rank}(E) \leq k$
-        \item If $a \perp b$ and $a \leq 0, b \geq 0$, then $\mathrm{rank}(E) \leq k - 1$
+        \item If $a \perp b$ and $a \leq 0 \leq b$, then $\mathrm{rank}(E) \leq k - 1$
     \end{itemize}
@@
     Use $a_1, b_1, E', \phi, \hat{\phi}, q, \hat{q}$ as in the lecture.
-    Let $l$ denote the number of distinct prime factors of $a^2 - 4b = b_1$ and $m$ denote the number of distinct prime factors of $b$.
+    Let $v$ denote the number of distinct prime factors of $a^2 - 4b = b_1$ and $w$ denote the number of distinct prime factors of $b$.
     As shown in the lecture, have that $E'(\Q)/\phi(E(\Q)) \cong \im(q)$ and if $\overline{r} \in \im(q)$ with $r \in \Z$ square-free, then $r \divides b_1$.
@@
     \begin{equation*}
-        \#(E'(\Q)/\phi(E(\Q))) \leq 2^{l + 1}
+        \#(E'(\Q)/\phi(E(\Q))) \leq 2^{v + 1}
     \end{equation*}
@@
     \begin{equation*}
-        \#(\hat{\phi}(E'(\Q))/[2]E(\Q)) \leq 2^l
+        \#(\hat{\phi}(E'(\Q))/[2]E(\Q)) \leq 2^v
     \end{equation*}
@@
     \begin{equation*}
-        \#(E(\Q)/\hat{\phi}(E'(\Q))) \leq 2^{m + 1}
+        \#(E(\Q)/\hat{\phi}(E'(\Q))) \leq 2^{w + 1}
     \end{equation*}
@@
     \begin{equation}
-        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^{m + 1} = 2^{l + m + 1} \label{eq:general_bound}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^v \cdot 2^{w + 1} = 2^{v + w + 1} \label{eq:general_bound}
     \end{equation}
@@
     \begin{equation*}
-        \mathrm{rank}(E) \leq \log_2(\#(E(\Z)/[2]E(\Q)) / 2) \leq \log_2(2^{l + m}) = l + m \leq 2k
-    \end{equation*}
-
-    \paragraph{Assume $a \leq 0, b \geq 0$} Then the equation
+        \mathrm{rank}(E) \leq \log_2(\#(E(\Z)/[2]E(\Q)) / 2) \leq \log_2(2^{v + w}) = v + w \leq 2k
+    \end{equation*}
+
+    \paragraph{Assume $a \leq 0 \leq b$} Then the equation
     \begin{equation*}
@@
     \begin{equation*}
-        \#(E(\Q)/\hat{\phi}(E'(\Q))) \leq 2^m
+        \#(E(\Q)/\hat{\phi}(E'(\Q))) \leq 2^w
     \end{equation*}
@@
     \begin{equation}
-        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^m \label{eq:sign_bound}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^v \cdot 2^w \label{eq:sign_bound}
     \end{equation}
@@
     \begin{equation*}
-        \mathrm{rank}(E) \leq \log_2(2^l \cdot 2^m / 2) = l + m - 1 \leq 2k - 1
-    \end{equation*}
-
-    \paragraph{Assume $a \perp b$} Then have that $b_1 = (a^2 - 4b) \perp b$ and thus we find that $l + m = k$.
+        \mathrm{rank}(E) \leq \log_2(2^v \cdot 2^w / 2) = v + w - 1 \leq 2k - 1
+    \end{equation*}
+
+    \paragraph{Assume $a \perp b$} Then have that $b_1 = (a^2 - 4b) \perp b$ and thus we find that $v + w = k$.
     Equation~\ref{eq:general_bound} is
     \begin{equation*}
-        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^{m + 1} = 2^{l + m + 1}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^v \cdot 2^{w + 1} = 2^{v + w + 1}
     \end{equation*}
@@
     \begin{equation*}
-        \mathrm{rank}(E) \leq \log_2(2^{l + m + 1} / 2) = l + m = k
-    \end{equation*}
-
-    \paragraph{Assume $a \perp b$ and $a \leq 0, b \geq 0$} Now have both Equation~\ref{eq:sign_bound}
-    \begin{equation*}
-        \#(E(\Q)/[2]E(\Q)) \leq 2^l \cdot 2^m = 2^{m + l}
-    \end{equation*}
-    and $m + l = k$.
+        \mathrm{rank}(E) \leq \log_2(2^{v + w + 1} / 2) = v + w = k
+    \end{equation*}
+
+    \paragraph{Assume $a \perp b$ and $a \leq 0 \leq b$} Now have both Equation~\ref{eq:sign_bound}
+    \begin{equation*}
+        \#(E(\Q)/[2]E(\Q)) \leq 2^v \cdot 2^w = 2^{v + w}
+    \end{equation*}
+    and $v + w = k$.
     As before, it follows
     \begin{equation*}
-        \mathrm{rank}(E) \leq \log_2(2^{m + l} / 2) = m + l - 1 = k - 1
+        \mathrm{rank}(E) \leq \log_2(2^{v + w} / 2) = v + w - 1 = k - 1
     \end{equation*}
@@
 \begin{example}
-    Consider the curve $E: y^2 = x(x^2 - 6x + 1)$, which satisfies $a \leq 0, b \geq 0$ and $a \perp b$.
+    Consider the curve $E: y^2 = x(x^2 - 6x + 1)$, which satisfies $a \leq 0 \leq b$ and $a \perp b$.
     Furthermore, $b_1 = 6^2 - 4 = 32 = 2^5$ has only one prime factor.
@@
 \end{equation*}
-satisfies $a \leq 0, b \geq 0$ and $a \perp b$, and indeed its rank is $\mathrm{rank}(E') = 3 = 4 - 1$ (note that $2089 \cdot 30$ has exactly $4$ prime factors).
+satisfies $a \leq 0 \leq b$ and $a \perp b$, and indeed its rank is $\mathrm{rank}(E') = 3 = 4 - 1$ (note that $2089 \cdot 30$ has exactly $4$ prime factors).
 

### 2022-03-31 Elliptic Curves/submission.tex
Removed unused lemma

@@
 \end{proof}
-I came up with the next lemma to make my first proof of 3(i) work.
-Since then, I have found a simpler proof that does not require the lemma anymore, but I found it beautiful and did not want to delete it.
-\begin{lemma}
-    \label{prop:share_subgroup_equal}
-    Let $E, E'$ be Elliptic Curves defined over any field $k$, and assume they share a cyclic subgroup of order $n \geq 5$\footnote{Technically, we can also allow infinite order here.}.
-    With this, we mean there is a point $P \in E \cap E'$ of order $n$ such that
-    \begin{equation*}
-        G := \langle P \rangle_E \subseteq E' \quad \text{and} \quad \restr{+_E}{G \times G} = \restr{+_{E'}}{G \times G}
-    \end{equation*}
-    Then $E = E'$ (in the sense that they have the same defining equation).
-\end{lemma}
-\begin{proof}
-    Consider some point $[i] P = (a, b) \in E \cap E'$.
-    With $P' = (a', b') := -[2i] P \in E \cap E'$ we see that $P + P + P' = \O$ and so $P, P, P'$ are colinear\footnote{We mean that the line through $P$ and $P'$ meets $E$ resp.
-$E'$ at $P$ with multiplicity 2.}.
-    In particular, the tangent on $E$ resp. on $E'$ at $P \in E \cap E'$ both have the slope $(b - b')/(a - a')$\footnote{Or infinity if $a = a'$, but importantly, the slopes are equal.}.
-
-    Since $P$ has order at least 5, observe that $P, [2]P, [3]P, [4]P$ and $[5]P$ are all different.
-    Furthermore, since $E$ and $E'$ have the same tangent slope at each $[i] P$, note that $E$ meets $E'$ in $[i] P$ with multiplicity 2.
-    So $E$ meets $E'$ in at least 10 points (counting multiplicity), which is greater than the product of their degrees $9 = 3 \cdot 3$.
-    By Bezout's theorem \cite[Corollary I.7.8]{hartshorne}, it follows that $E$ and $E'$ share an irreducible component of dimension $\geq 1$, but since both are Elliptic Curves, they are irreducible of dimension $1$, so we find $E = E'$.
-\end{proof}
-Finally we can proof the statement on 5-torsion points.
+Now we can proof the statement on 5-torsion points.
 \begin{prop}[3(i)]

### 2022-03-31 Elliptic Curves/submission.tex
Added introduction and conclusion to elliptic curves

@@
 
+\section*{Introduction}
+In this Miniproject, we study several phenomena that can occur when computing the group of rational points $E(\Q)$ of an Elliptic Curve $E$.
+In particular, we look at the two most important tools for studying this group that were introduced in the lecture. 
+Firstly, this is the fact that the reduction modulo a prime is injective on torsion points, and thus provides a good way to find the torsion part of $E(\Q)$.
+The second tool is the 2-descent method, which can be used to find the rank (i.e. the dimension of the free part of $E(\Q)$).
+
+When applying these methods, there are some exceptional (and therefore interesting) situations that can occur.
+We want to present some of these phenomena by giving examples, and analyze what conditions must be satisfied for them to occur.
+
 \section{Question 1}
@@
 
+\section*{Conclusion}
+In this work, we have seen a lot of examples of Elliptic Curves with interesting behavior.
+The first question dealt with cases in which there are (almost) no points with coordinates in $\Z_p$ on the curve, for certain $p$.
+By Hensel's Lemma, this is very closely related to the $\F_p$-rational points of the reduction of $E$ modulo $p$, and we have seen that this only exhibits special behavior for small primes.
+
+In the second question, we continued to study the reduction modulo $p$ and looked for situations where the group of $\F_p$ rational points in the reduction is strictly larger than the torsion group of $E(\Q)$.
+These cases are interesting, as they complicate the computation of the torsion group using the standard techniques.
+
+The third question continued to deal with rational torsion points, but now we wanted to find Elliptic Curves with torsion points of specified order.
+As it turns out, in some cases we have found a family of defining equations that completely characterize these Elliptic Curves.
+Together, we note that when it comes to the torsion group, we find a lot of nice connections and can make definite statements about its structure.
+All in all, we understand the torsion part of $E(\Q)$ quite well.
+
+The last question however deals with the free part of $E(\Q)$ (in particular the rank of $E$), which is much more mysterious.
+Our main obstacle is that the naive 2-descent method from the lecture only works in a few cases, and in other cases, it is extremely difficult to compute the rank.
+We also could not find nice characterizations of whenever the method works.
+However, working around this obstacle, we still could find some interesting examples and find their rank.
+Furthermore, we present a sharp bound on the rank, which only depends on the coefficients of the Elliptic Curve in a simple way.
+
+Of course, when it comes to the rank, there are still a lot of open questions, and we just touched the topic on the surface.
+For example, I would find it interesting to study whether the fact that isogenies preserve the rank allows to prove more statements or compute the rank in more cases.
+Finally, this line of thought also leads into current research, and is even connected to one of the Millenium Problems, namely the Birch and Swinnerton-Dyer Conjecture.
+
 \section{Appendix}

### 2022-03-31 Schemes/submission.tex
Shrunk diagram to make it fit the page
Added introduction and conlusion to schemes

@@
 
-\tableofcontents
+In this miniproject, we want to study the $\Proj$-construction in the theory of schemes, that can be used to associate a scheme given a graded ring.
+In particular, it is very closely related to projective space (hence the name).
+
+We begin the work by defining the scheme $\Proj(S)$ for a graded ring $S$, and showing that it is well-defined.
+Furthermore, we study some very basic properties.
+Then we focus on the case that our graded ring $S$ is an $R$-algebra, in particular, we are interested in the case of the polynomial ring $R[x_0, ..., x_n]$.
+This case is important, since it yields the projective space $\P_R^n$.
+
+Finally, we use the theory developed in the work to prove the main result, namely that projective space is a proper scheme.
+We present two proofs of this, one relatively short and concrete (but complicated) one, relying on commutative algebra.
+The other proof is the standard proof, as presented in works like \cite{hartshorne}.
+For the sake of brevity, we will only present parts of this proof, but try to give a little bit of intuition.
 
@@
 \end{corollary}
-\begin{proof}
-    By assumption, $\D{f}$ covers $\D{g}$, thus by the Covering Trick (Lemma~\ref{prop:covering_trick}), observe that $g^n \in \langle f \rangle$ for some $n \in \N$.
-    The claim follows.
-\end{proof}
 \begin{prop}
@@
 \end{prop}
-\begin{proof}\footnote{I guess I have included the proof mostly for the sake of completeness - apart from presentational issues, it is just copied from the lecture notes.}
-    Clearly, $\mathcal{F}$ is a functor and thus a presheaf.
-    Hence, we have to show the local-to-global property.
-
-    Let $\D{f} = \bigcup_{i \in I} \D{g_if}$ be a cover and $s_i \in \mathcal{F}(\D{g_if})$ such that
-    \begin{equation*}
-        \forall x \in \D{g_if} \cap \D{g_jf} \ \exists V \in B: \ V \subseteq \D{g_if} \cap \D{g_jf}, \ x \in V, \ \frac {s_i} 1 = \frac {s_j} 1 \in \mathcal{F}(V)
-    \end{equation*}
-    We show that the $s_i$ glue to a unique $s \in \mathcal{F}(\D{f})$.
-    To show uniqueness, assume there are $\alpha/f^N, \beta/f^N \in \D{f}$ with
-    \begin{equation*}
-        \restr{\frac {\alpha} {f^N}}{\D{g_if}} = \restr{\frac {\beta} {f^N}}{\D{g_if}} \quad \text{for all $i$}
-    \end{equation*}
-    Therefore there is $n_i \in \N$ such that
-    \begin{equation*}
-        (f g_i)^{n_i} (\alpha f^N + \beta f^N) = 0
-    \end{equation*}
-
-    wlog there are only finitely many $i$ (by the Covering Trick, Lemma~\ref{prop:covering_trick}).
-
-    wlog $N$ is sufficiently large (we can always increase $N$), and so $(fg_i)^N(\alpha - \beta) = 0$.
-
-    Since $\bigcup_i \D{(fg_i)^N} = \bigcup_i \D{fg_i} = \D{f}$ it follows that $f^n \in \langle (fg_i)^N \ | \ i \rangle$ for some $n \in \N$ (again the Covering Trick, Lemma~\ref{prop:covering_trick}).
-    Therefore we find
-    \begin{equation*}
-        f^n(\alpha - \beta) \in \langle (f g_i)^N \ | \ i \rangle (\alpha - \beta) = \langle (f g_i)^N (\alpha - \beta) \ | \ i \rangle = \{ 0 \}
-    \end{equation*}
-    and so $\alpha = \beta \in S_f$.
-
-    Now we show existence.
-    By the uniqueness above, it follows that
-    \begin{equation*}
-        \restr{s_i}{\D{fg_ig_j}} = \restr{s_i}{\D{fg_i} \cap \D{fg_j}} = \restr{s_j}{\D{fg_i} \cap \D{fg_j}} = \restr{s_j}{\D{fg_ig_j}}
-    \end{equation*}
-    wlog have again a finite cover, i.e. only finitely many $g_i$.
-    Hence find an $N \in \N$ such that each $s_i = s'_i / (fg_i)^N$ with $s'_i \in S$ homogeneous.
-    By possibly replacing $N$ with a bigger $N$, we can now assume that
-    \begin{equation*}
-        (f^2g_ig_j)^N \left( s'_i (f g_j)^N - s'_j (f g_i)^N \right) = 0 \quad \text{as $\restr{s_i}{\D{fg_ig_j}} = \restr{s_j}{\D{fg_ig_j}}$}
-    \end{equation*}
-    Now note that
-    \begin{equation*}
-        s_i = \frac {a_i} {b_i} \quad \text{with}\ a_i = s'_i(f g_i)^N, \ b_i = (f g_i)^{2N}
-    \end{equation*}
-    and
-    \begin{equation*}
-        a_i b_j - a_j b_i = s'_i (f g_i)^N (f g_j)^{2N} - s'_j (f g_j)^N (f g_i)^{2N} = \underbrace{(f^2g_ig_j)^N \left(s'_i (fg_j)^N - s'_j (fg_i)^N \right)}_{= 0}
-    \end{equation*}
-    Now observe that $\D{b_i} = \D{fg_i}$ and so $f^n \in \langle b_i \ | \ i \rangle$ for some $n$ (once again the Covering Trick, Lemma~\ref{prop:covering_trick}).
-    Let $f^n = \sum_i r_i b_i$ and get
-    \begin{equation*}
-        a_i f^n = \sum_l r_l b_l a_i = \sum_l r_l a_l b_i = b_i \sum_l r_l a_l
-    \end{equation*}
-    Note that $a_i, b_i, f$ are homogeneous, and so we can also choose $r_i$ to be homogeneous.
-    Then find that $0 = \deg(s_i) = \deg(a_i) - \deg(b_i) = \deg(\sum r_l a_l) - n\deg(f)$.
-
-    Thus
-    \begin{equation*}
-        s_i = s := \frac {\sum_l r_l a_l} {f^n} \in S_f
-    \end{equation*}
-    and since $\deg(\sum r_l a_l) = n\deg(f)$ we find that $s \in (S_f)_0 = \mathcal{F}(\D{f})$.
-    Clearly $\restr{s}{\D{fg_i}} = s_i$ and the claim follows.
+\begin{proof}
+    This is exactly the proof from the lecture, Section 1.12.
+    Note that we have all necessary ingredients, in particular the Covering Trick~\ref{prop:covering_trick}.
+    Hence, the only thing to note is that the gluing produces a homogeneous global section if one starts with homogeneous local sections.
+    It is easy to check that this is indeed the case.
 \end{proof}
@@
 
-            \node (Sf) at (8.5, 0) {$(S[x_0, ..., x_n]_{x_i})_0$};
+            \node (Sf) at (7.5, 0) {$(S[x_0, ..., x_n]_{x_i})_0$};
             \node (Sg) at (5, -1.5) {$(S[x_0, ..., x_n]_{x_j})_0$};
-            \node (Sfg) at (8.5, -3) {$(S[x_0, ..., x_n]_{x_ix_j})_0$};
+            \node (Sfg) at (7.5, -3) {$(S[x_0, ..., x_n]_{x_ix_j})_0$};
 
@@
 \end{proof}
-This lemma also justifies the usual definition of projective $n$-space over a scheme $B$ as
+This lemma also justifies the usual definition of \emph{projective $n$-space over a scheme $B$} as
 \begin{equation*}
@@
 divisibility by $R$) - more or less achieves the same effect as the more complicated ideal argument from Lemma~\ref{prop:adding_coeff_ideal_does_not_introduce_irrelevant_ideal}.
+
+\section*{Conclusion}
+In this work, we have seen how to construct the scheme $\Proj(S)$ given a graded ring $S$.
+Furthermore, we have peeked into its properties, and used it to prove an important statement about projective space.
+Additionally, we have tried to explain a little bit what is going on in the proof, and compared two different versions of proof.
+The first proof is my own work\footnote{Meaning I could find it nowhere online.
+However, I do not believe that it is original, and in some sense, it relies on the same idea as the standard proof.}, while the second proof is the standard proof found in many textbooks.
+
+If one continues that line of thought, the next step would probably be to study \emph{projective morphisms}, i.e.
+morphisms that factor through projective space via a closed immersion, and show that they are always proper.
+After that, it seems like an interesting idea to examine the phenomenon of properness closer.
+For example \cite{hartshorne} mentioned that not all proper morphisms are projective, so it might be instructive to find examples for that and study in which other situations one gets a projective morphism.
+
+Finally, another line of continuing the work would be to study the cohomology of $\Proj(S)$, and how it relates to the ring $S$.
+From the lecture, we already know that projective space $\P_\Z^n$ has a first \v{C}ech-cohomology group isomorphic to $\Z$.
+Starting from that, it would be interesting to see what the cohomology group of $\Proj(S)$ for other graded rings $S$ is.
+A natural first step would be to consider $S = R[x_0, ..., x_n]/\a$ for a homogeneous ideal $\a$, i.e. study the cohomology of closed subschemes of $\P_R^n$.
+This can already become quite complicated, as for example the case of Elliptic Curves shows.
+In the end, it will be interesting if the representation of a scheme as $\Proj(S)$ gives us better access to computing cohomology as the standard way to cover it by affine opens.
+
 \printbibliography

### 2022-03-31 Elliptic Curves/submission.tex
Made the remarks on isogenies and rank more precise

@@
     Note that if one of the additional conditions is fulfilled for $a_1, b_1$, then we get the corresponding bound for $\mathrm{rank}(E') = \mathrm{rank}(E)$ 
-    (isogenous curves have the same rank, as isogenies are group homomorphisms with finite kernel, see \cite[Thm III.4.8]{silverman} and \cite[Corollary III.4.9]{silverman}).
+    ($\Q$-isogenous curves have the same rank, as isogenies are group homomorphisms with finite kernel and there is the ``dual isogeny'', see \cite[Thm III.4.8]{silverman}, \cite[Corollary III.4.9]{silverman} and \cite[Thm III.6.1]{silverman}).
 \end{prop}
@@
 Of course, when it comes to the rank, there are still a lot of open questions, and we just touched the topic on the surface.
-For example, I would find it interesting to study whether the fact that isogenies preserve the rank allows to prove more statements or compute the rank in more cases.
+For example, I would find it interesting to study whether the fact that $\Q$-isogenies preserve the rank allows to prove more statements or compute the rank in more cases.
 Finally, this line of thought also leads into current research, and is even connected to one of the Millenium Problems, namely the Birch and Swinnerton-Dyer Conjecture.
